### 2019-03-05 src/manuscript/pandoc-frontiers-template/demo-manuscript.Rmd
Set up Frontiers template and created demo manuscript

---
title: 'Demo Manuscript'
author: "An author"
date: "October 30th 2018"
abstract: "Hello, this is the abstract."
keywords: "keyword1, kw2, kw3... have to have at least 5, max 8"
language: en-US
output:
  pdf_document:
    dev: pdf
    keep_tex: true
    template: ./pandoc-frontiers-template.tex
---

Hello, world!

# Introduction
Here are some things to consider:

1. We don't know what's happening
2. Neither does anyone else

Also important:

- this creates an unordered list
- and this is the second item.

This is how links work: [link text](https://example.com/)

We can also include code snippets:
```python
# Examplary python code
print("Hello World!")
print("2 + 5 = " + (2+5))
with open('testfile.fa', 'w') as file:
  file.write("Hello, world")
print("Done")
```

# Rmarkdown
Now for some really kewl stuff: We load a file in R:

```{r loadSomething}
annotation_quantities = 
  read.csv('../../../data/mocks/processed/annotation_quantities.csv', header=T)
rice = subset(annotation_quantities, genome=='rice' & source=='GOMAP')
```

And now we can actually use it:
```{r demo1}
head(annotation_quantities)
summary(annotation_quantities$n_c)
```

The annotation set for rice had a total of `r rice$n_c + rice$n_p + rice$n_f` annotations.

## Plots
We can even plot the data:
```{r plot}
a = annotation_quantities
pie(a$n_c+a$n_f+a$n_p, labels=paste(a$genome, a$source))
```

```{r plot2}
barplot(a$n_c+a$n_f+a$n_p, las=2)
```

### 2019-03-06 src/manuscript/pandoc-frontiers-template/demo-manuscript.Rmd
Added quantity figure to demo manuscript
Created rudimentary and buggy Makefile

@@
 
-The annotation set for rice had a total of `r rice$n_c + rice$n_p + rice$n_f` annotations.
+The annotation set for rice had a total of `r rice$n_c` annotations for cellular component.
 
@@
 ```
+
+Now here is an actual figure I've been working on:
+
+![Quantitiative lalala](../../../reports/figures/annotation_quantities.pdf)

### 2019-03-06 src/figures/quantity_barcharts.R
Added axis and labels to quantity barchart script

@@ -7,23 +7,24 @@ n_genomes = length(unique(annotation_quantities$genome))
 row_counter = 0
 
 pdf("reports/figures/annotation_quantities.pdf", 18, 6)
-par(family='serif', mar=c(0.5,5,0.5,0.5))
 library(pBrackets)
+
+axis_drawn = F
 
 # Make a new barplot for each genome
 for(current_genome in unique(annotation_quantities$genome)) {
   par(fig=c(
-    0, 0.1, row_counter * (1/n_genomes),
-    (row_counter + 1) * (1/n_genomes)
+    0, 0.1, row_counter * (1/n_genomes)  * 0.90 + 0.05,
+    (row_counter + 1) * (1/n_genomes) * 0.90  + 0.05
   ), new=T, mar=c(0,0,0,0))
   plot(c(0, 1), c(0, 1), ann = F, bty = 'n', type = 'n', xaxt = 'n', yaxt = 'n', xpd=F)
   brackets(1, 0.1, 1, 0.9, lwd=2)
   text(0.95,0.5, current_genome, cex = 2, pos=2)
   
   par(fig=c(
-    0.1, 1, row_counter * (1/n_genomes),
-    (row_counter + 1) * (1/n_genomes)
-  ), new=T, mar=c(0.5,5,0.5,0.5))
+    0.1, 1, row_counter * (1/n_genomes) * 0.90 + 0.05,
+    (row_counter + 1) * (1/n_genomes) * 0.90  + 0.05
+  ), new=T, mar=c(0.5,5,0.5,1.5))
   
   current_data = subset(annotation_quantities, genome == current_genome)
   # Now sort in ascending order by number of total annotations
@@ -42,11 +43,27 @@ for(current_genome in unique(annotation_quantities$genome)) {
          formatC(bar$n_f, format='d', big.mark=','))
     text(bar$n_c/2, y_coordinates[bar_index],
          formatC(bar$n_c, format='d', big.mark=','))
+    #mtext(text=formatC(bar$n_c + bar$n_f + bar$n_p, format='d', big.mark=','), side=4, at=y_coordinates[bar_index], las=1)
+    #text(bar$n_c+bar$n_f+bar$n_p, y_coordinates[bar_index], formatC(bar$n_p+bar$n_c+bar$n_f, format='d', big.mark=','), pos = 4)
+  }
+  
+  if(!axis_drawn) {
[…]

### 2019-03-08 docs/conf.py
Restructured project layout

@@ -1,244 +1,0 @@
-# -*- coding: utf-8 -*-
-#
-# GOMAP-Paper documentation build configuration file, created by
-# sphinx-quickstart.
-#
-# This file is execfile()d with the current directory set to its containing dir.
-#
-# Note that not all possible configuration values are present in this
-# autogenerated file.
-#
-# All configuration values have a default; values that are commented out
-# serve to show the default.
-
-import os
-import sys
-
-# If extensions (or modules to document with autodoc) are in another directory,
-# add these directories to sys.path here. If the directory is relative to the
-# documentation root, use os.path.abspath to make it absolute, like shown here.
-# sys.path.insert(0, os.path.abspath('.'))
-
-# -- General configuration -----------------------------------------------------
-
-# If your documentation needs a minimal Sphinx version, state it here.
-# needs_sphinx = '1.0'
-
-# Add any Sphinx extension module names here, as strings. They can be extensions
-# coming with Sphinx (named 'sphinx.ext.*') or your custom ones.
-extensions = []
-
-# Add any paths that contain templates here, relative to this directory.
-templates_path = ['_templates']
-
-# The suffix of source filenames.
-source_suffix = '.rst'
-
-# The encoding of source files.
-# source_encoding = 'utf-8-sig'
-
-# The master toctree document.
-master_doc = 'index'
-
-# General information about the project.
-project = u'GOMAP-Paper'
-
-# The version info for the project you're documenting, acts as replacement for
-# |version| and |release|, also used in various other places throughout the
-# built documents.
-#
-# The short X.Y version.
-version = '0.1'
-# The full version, including alpha/beta/rc tags.
-release = '0.1'
-
-# The language for content autogenerated by Sphinx. Refer to documentation
-# for a list of supported languages.
-# language = None
-
-# There are two options for replacing |today|: either, you set today to some
-# non-false value, then it is used:
-# today = ''
-# Else, today_fmt is used as the format for a strftime call.
-# today_fmt = '%B %d, %Y'
-
-# List of patterns, relative to source directory, that match files and
-# directories to ignore when looking for source files.
-exclude_patterns = ['_build']
-
-# The reST default role (used for this markup: `text`) to use for all documents.
-# default_role = None
-
-# If true, '()' will be appended to :func: etc. cross-reference text.
-# add_function_parentheses = True
-
[…]

### 2019-03-08 setup.py
Restructured project layout

@@ -1,10 +1,0 @@
-from setuptools import find_packages, setup
-
-setup(
-    name='src',
-    packages=find_packages(),
-    version='0.1.0',
-    description='Publication in the works',
-    author='Dill-PICL',
-    license='MIT',
-)

### 2019-03-08 src/data/create_quantity_table.R
Started writing new quantity table script

@@ -1,0 +1,78 @@
+# Creates the file `data/mocks/results/quantity_table.csv` by evaluating GAF file quantities and information from `data/mocks/raw/n_genes_per_genome.csv`
+library(tools)
+
+# Helper function for the functions below: Checks if the argument passed is a data frame (which would indicate
+# that the GAF file has already been read and the function was passed the GAF data) or a string (which would
+# indicate that it's the path to the file to be opened) and does the appropriate thing, returns the GAF data frame.
+possibly_read_gaf <- function(gaf_file) {
+  if(is.data.frame(gaf_file))
+    return(gaf_file)
+  if(is.character(gaf_file))
+    return(read.csv(gaf_file, skip=1, header=T, sep="\t"))
+  # If neither dataframe nor string: something is wrong:
+  stop("Passed argument is neither data frame nor path to GAF file!")
+}
+
+# Pass the path to a GAF file and it will return a table of the aspect occurences
+count_aspects <- function(gaf_file) {
+  gaf_file = possibly_read_gaf(gaf_file)
+  return(table(gaf_file$aspect))
+}
+
+# Pass the path to a GAF file and it will return how many genes have at least one annotation in each aspect (C,F,P) or any (A)
+count_genes_annotated <- function(gaf_file) {
+  gaf_file = possibly_read_gaf(gaf_file)
+  return(c(
+    "C" = length(unique(subset(gaf_file, aspect == "C")$db_object_id)),
+    "F" = length(unique(subset(gaf_file, aspect == "F")$db_object_id)),
+    "P" = length(unique(subset(gaf_file, aspect == "P")$db_object_id)),
+    "A" = length(unique(gaf_file$db_object_id))
+    ))
+}
+
+# @TODO This way of creating the dataframe and building it row by row is supposed to be very inefficient -- make it more efficient?
+csv = data.frame(
+  genome = "",
+  n_genes = 0,
+  dataset = "",
+  annotations_c = 0,
+  annotations_f = 0,
+  annotations_p = 0,
+  annotations_a = 0,
+  genes_annotated_c = 0,
+  genes_annotated_f = 0,
+  genes_annotated_p = 0,
+  genes_annotated_a = 0
+)
+
+n_genes_per_genome = read.csv("data/mocks/raw/n_genes_per_genome.csv", header = T)
[…]

### 2019-03-08 manuscript/Manuscript.Rmd
Finished first implementation of quantity table

---
title: 'TBD'
author: "The Pickles"
date: "Febcember 32nd 3023"
abstract: "Hello, this is the abstract."
keywords: "keyword1, kw2, kw3... have to have at least 5, max 8"
language: en-US
output:
  pdf_document:
    dev: pdf
    keep_tex: true
    template: ./pandoc-frontiers-template.tex
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
---
```{r load_libs, include=F}
library(knitr)
library(kableExtra)
knitr::opts_chunk$set(echo=FALSE)
```

# Results
... a quantitative comparison of the datasets in Table \ref{tab:t_annotation_quantities}.

```{r t_annotation_quantities}
dt2 <- read.csv("../data/results/quantity_table.csv", header=T)
headers_above = c(a = 3, b = 4, c = 4, d =4)
names(headers_above) <- c(" ", 
  paste0("Annotations", footnote_marker_alphabet(1, double_escape=T)),
  paste0("Annotated Genes", footnote_marker_alphabet(2, double_escape=T)), 
  paste0("Median Ann. per G.", footnote_marker_alphabet(3, double_escape=T)))
kable(dt2, booktabs=T, caption = "Quantitative metrics of the generated and existing functional annotation sets. C, F, P, and A refer to the aspects of the GO: Cellular Component, Biological Function, Molecular Process, and Any/All.", col.names=c("Genome", "Genes", "Dataset", "C", "F", "P", "A","C", "F", "P", "A","C", "F", "P", "A")) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  add_header_above(headers_above, escape=F)%>%
  column_spec(c(15), bold = T) %>%
  column_spec(c(7,11), bold=T, border_right = T) %>%
  collapse_rows(columns = 1:2, latex_hline="major") %>%
  footnote(alphabet=c(
    "How many annotations in the C, F, and P aspect does this dataset contain? A = How many in total? $A = C + F + P$",
    "How many genes in the genome have at least one GO term from the C, F, P aspect annotated to them? A = How many at least one from any aspect? ($A = C \\\\cup F \\\\cup P$)",
    "Take a typical gene that is present in the annotation set. How many annotations does it have in each aspect? A = How many in total? Ask your favorite statistician why $A \\\\neq C + F +P$"
  ), threeparttable=T, escape=F)
```

### 2019-03-08 manuscript/Manuscript.tex
Finished first implementation of quantity table

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is just an example/guide for you to refer to when submitting manuscripts to Frontiers, it is not mandatory to use Frontiers .cls files nor frontiers.tex  %
% This will only generate the Manuscript, the final article will be typeset by Frontiers after acceptance.   
%                                              %
%                                                                                                                                                         %
% When submitting your files, remember to upload this *tex file, the pdf generated with it, the *bib file (if bibliography is not within the *tex) and all the figures.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% Version 3.4 Generated 2018/06/15 %%%
%%% You will need to have the following packages installed: datetime, fmtcount, etoolbox, fcprefix, which are normally inlcuded in WinEdt. %%%
%%% In http://www.ctan.org/ you can find the packages and how to install them, if necessary. %%%
%%%  NB logo1.jpg is required in the path in order to correctly compile front page header %%%

\documentclass[utf8,]{frontiersSCNS} % for Science, Engineering and Humanities and Social Sciences articles
%\documentclass[utf8]{frontiersHLTH} % for Health articles
%\documentclass[utf8]{frontiersFPHY} % for Physics and Applied Mathematics and Statistics articles

%\setcitestyle{square} % for Physics and Applied Mathematics and Statistics articles
\usepackage{url,hyperref,lineno,microtype,subcaption}
\usepackage[onehalfspacing]{setspace}

\linenumbers

% Leave a blank line between paragraphs instead of using \\

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Sample {et~al.}} %use et al only if is more than 1 author
\def\Authors{First Author}
% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
\def\Address{Address}
% The Corresponding Author should be marked with an asterisk
% Provide the exact contact address (this time including street name and city zip code) and email of the corresponding author
\def\corrAuthor{Corresponding Author}

\def\corrEmail{email@uni.edu}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\begin{document}
\onecolumn
\firstpage{1}

\title[Running Title]{TBD}

\author[\firstAuthorLast ]{\Authors} %This field will be automatically populated
\address{} %This field will be automatically populated
\correspondance{} %This field will be automatically populated

\extraAuth{}% If there are more than 1 corresponding author, comment this line and uncomment the next one.
%\extraAuth{corresponding Author2 \\ Laboratory X2, Institute X2, Department X2, Organization X2, Street X2, City X2 , State XX2 (only USA, Canada and Australia), Zip Code2, X2 Country X2, email2@uni2.edu}

\maketitle

\begin{abstract}

Hello, this is the abstract.

  \tiny
   \keyFont{ \section{Keywords:} keyword1, kw2, kw3\ldots{} have to have at least 5, max 8} %All article types: you may provide up to 8 keywords; at least 5 are mandatory.

\end{abstract}

\section{Results}\label{results}

\ldots{} a quantitative comparison of the datasets in Table
\ref{tab:t_annotation_quantities}.

\begin{table}[t]

\caption{\label{tab:t_annotation_quantities}Quantitative metrics of the generated and existing functional annotation sets. C, F, P, and A refer to the aspects of the GO: Cellular Component, Biological Function, Molecular Process, and Any/All.}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}{lrlrrr>{\bfseries}r|rrr>{\bfseries}r|rrr>{\bfseries}r}
\toprule
\multicolumn{3}{c}{ } & \multicolumn{4}{c}{Annotations\textsuperscript{a}} & \multicolumn{4}{c}{Annotated Genes\textsuperscript{b}} & \multicolumn{4}{c}{Median Ann. per G.\textsuperscript{c}} \\
\cmidrule(l{3pt}r{3pt}){4-7} \cmidrule(l{3pt}r{3pt}){8-11} \cmidrule(l{3pt}r{3pt}){12-15}
Genome & Genes & Dataset & C & F & P & A & C & F & P & A & C & F & P & A\\
\midrule
\rowcolor{gray!6}   &  & GOMAP & 135251 & 87953 & 291855 & 515059 & 34867 & 38099 & 39469 & 39469 & 3 & 2 & 6 & 11\\

 &  & Gramene49 & 20072 & 31139 & 30102 & 81313 & 11834 & 18033 & 15800 & 21926 & 1 & 1 & 1 & 3\\

\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash maize\_v3} & \multirow{-3}{*}{\raggedleft\arraybackslash 300} & Phytozome & 4787 & 19098 & 13100 & 36985 & 4524 & 13775 & 11365 & 16132 & 0 & 1 & 1 & 2\\
\cmidrule{1-15}
maize\_v4 & 320 & GOMAP & 88831 & 82849 & 278952 & 450632 & 36717 & 37431 & 39324 & 39324 & 2 & 2 & 6 & 10\\
\cmidrule{1-15}
\rowcolor{gray!6}  rice & 200 & GOMAP & 72782 & 64783 & 248713 & 386278 & 28619 & 29876 & 35824 & 35825 & 2 & 2 & 6 & 9\\
\cmidrule{1-15}
wheat & 500 & GOMAP & 267742 & 218839 & 786028 & 1272609 & 95604 & 98224 & 107890 & 107891 & 2 & 2 & 6 & 10\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item[a] How many annotations in the C, F, and P aspect does this dataset contain? A = How many in total? $A = C + F + P$
\item[b] How many genes in the genome have at least one GO term from the C, F, P aspect annotated to them? A = How many at least one from any aspect? ($A = C \cup F \cup P$)
\item[c] Take a typical gene that is present in the annotation set. How many annotations does it have in each aspect? A = How many in total? Ask your favorite statistician why $A \neq C + F +P$
\end{tablenotes}
\end{threeparttable}}
\end{table}

\end{document}

### 2019-03-08 src/data/create_quantity_table.R

@@ -1,4 +1,4 @@
-# Creates the file `data/mocks/results/quantity_table.csv` by evaluating GAF file quantities and information from `data/mocks/raw/n_genes_per_genome.csv`
+# Creates the file `data/results/quantity_table.csv` by evaluating GAF file quantities and information from `data/raw/n_genes_per_genome.csv`
 library(tools)
 
 # Helper function for the functions below: Checks if the argument passed is a data frame (which would indicate
@@ -13,13 +13,13 @@ possibly_read_gaf <- function(gaf_file) {
   stop("Passed argument is neither data frame nor path to GAF file!")
 }
 
-# Pass the path to a GAF file and it will return a table of the aspect occurences
+# Pass the path/df of a GAF file and it will return a table of the aspect occurences
 count_aspects <- function(gaf_file) {
   gaf_file = possibly_read_gaf(gaf_file)
   return(table(gaf_file$aspect))
 }
 
-# Pass the path to a GAF file and it will return how many genes have at least one annotation in each aspect (C,F,P) or any (A)
+# Pass the path/df of a GAF file and it will return how many genes have at least one annotation in each aspect (C,F,P) or any (A)
 count_genes_annotated <- function(gaf_file) {
   gaf_file = possibly_read_gaf(gaf_file)
   return(c(
@@ -29,6 +29,20 @@ count_genes_annotated <- function(gaf_file) {
     "A" = length(unique(gaf_file$db_object_id))
     ))
 }
+
+# Pass the path/df of a GAF file and get back the median number of annotations for each gene in the GAF
+# in the C,F,P aspect and total median across all aspects (A)
+count_median_annotations <- function(gaf_file) {
+  gaf_file = possibly_read_gaf(gaf_file)
+  t = table(gaf_file$db_object_id, gaf_file$aspect)
+  return(c(
+    "C" = median(t[,"C"]),
+    "F" = median(t[,"F"]),
+    "P" = median(t[,"P"]),
+    "A" = median(t[,"C"]+t[,"F"]+t[,"P"])
+  ))
+}
+
 
 # @TODO This way of creating the dataframe and building it row by row is supposed to be very inefficient -- make it more efficient?
 csv = data.frame(
@@ -42,11 +56,15 @@ csv = data.frame(
   genes_annotated_c = 0,
   genes_annotated_f = 0,
[…]

### 2019-04-11 src/data/phylogenetics/merge_gene_annotations.R
Created script for merging GO annotations over genes for phylogeny

@@ -1,0 +1,39 @@
+# This script takes each GOMAP annotation GAF file and creates a new one where all GO terms for all genes are merged onto
+# a single made-up gene and duplicates removed. So it is a GAF file that describes what GO terms are assigned to the genome
+# in general, irrespectively of what gene they are annotated to.
+# This is needed to compare the GO terms genome-wide to build the phylogenetic tree.
+
+# Helper function for the functions below: Checks if the argument passed is a data frame (which would indicate
+# that the GAF file has already been read and the function was passed the GAF data) or a string (which would
+# indicate that it's the path to the file to be opened) and does the appropriate thing, returns the GAF data frame.
+possibly_read_gaf <- function(gaf_file) {
+  if(is.data.frame(gaf_file))
+    return(gaf_file)
+  if(is.character(gaf_file))
+    return(read.csv(gaf_file, skip=1, header=T, sep="\t"))
+  # If neither dataframe nor string: something is wrong:
+  stop("Passed argument is neither data frame nor path to GAF file!")
+}
+
+# Create directory for output GAF files if it doesn't exist yet:
+dir.create("data/interim/phylogenetics/merged_go_annotations", recursive=T, showWarnings=F)
+
+# Loop through all genomes and see if there's a GOMAP file.
+genomes = list.dirs("data/raw/go_annotation_sets", recursive = F)
+for(genome_path in genomes) {
+  genome_name = basename(genome_path)
+  print(genome_name)
+  if(file.exists(paste(genome_path,"/GOMAP.gaf.gz", sep=""))) {
+    gaf = possibly_read_gaf(paste(genome_path,"/GOMAP.gaf.gz", sep=""))
+    merged_gaf = gaf[!duplicated(gaf[,c('qualifier','term_accession')]),] # Choose first row of each duplicate with same qualifier and GO term
+    merged_gaf$db_object_id = "organism"
+    merged_gaf$db_object_symbol = "organism"
+    merged_gaf$taxon = "taxon:0000"
+    merged_gaf$gene_product_form_id = "organism"
+    
+    outfile = paste("data/interim/phylogenetics/merged_go_annotations/", genome_name, ".gaf", sep="")
[…]

### 2019-04-12 src/data/phylogenetics/dev/create_slim_ontology.py
Tested and explored functions for phylo-crystal scripts

@@ -1,0 +1,39 @@
+# This script reads an OBO file using the obo_parser and outputs a JSON file that is then used by the crystal scripts.
+# The JSON file looks like this:
+# {
+#   "parents": {
+#     "GO:122335": ["GO:4433", "GO:5432"],
+#     "GO:122341": ["GO:1243", "GO:1532"],
+#     ...
+#   },
+#   "obsolete": ["GO:1432", "GO:4322", ...]
+# }
+
+from cleanup_resources import obo_parser
+import json
+
+parents = {}
+obsolete = []
+with open("go.obo") as obofile:
+  parser = obo_parser.Parser(obofile)
+  for stanza in parser:
+    if not stanza.name == "Term":
+      continue
+
+    go_id = stanza.tags["id"][0]
+
+    if 'is_a' in stanza.tags:
+      parents[go_id] = stanza.tags['is_a']
+    else:
+      parents[go_id] = []
+
+    if 'alt_id' in stanza.tags:
+      for alt_id in stanza.tags['alt_id']:
+        pass
+
+    if 'is_obsolete' in stanza.tags and stanza.tags['is_obsolete'][0] == "true":
+      obsolete.append(go_id)
+
+with open('slimGO.json', 'w') as f:
+  f.write(json.dumps({"parents":parents,"obsolete":obsolete},indent=2))
+

### 2019-08-01 analyses/quantity/quantity.R
Added quantity analysis

@@ -1,0 +1,99 @@
+# Creates the file `results/quantity_table.csv` by evaluating GAF file quantities and information from `data/n_genes_per_genome.csv`
+library(tools)
+
+# Helper function for the functions below: Checks if the argument passed is a data frame (which would indicate
+# that the GAF file has already been read and the function was passed the GAF data) or a string (which would
+# indicate that it's the path to the file to be opened) and does the appropriate thing, returns the GAF data frame.
+possibly_read_gaf <- function(gaf_file) {
+  if(is.data.frame(gaf_file))
+    return(gaf_file)
+  if(is.character(gaf_file))
+    return(read.csv(gaf_file, skip=1, header=T, sep="\t"))
+  # If neither dataframe nor string: something is wrong:
+  stop("Passed argument is neither data frame nor path to GAF file!")
+}
+
+# Pass the path/df of a GAF file and it will return a table of the aspect occurences
+count_aspects <- function(gaf_file) {
+  gaf_file = possibly_read_gaf(gaf_file)
+  return(table(gaf_file$aspect))
+}
+
+# Pass the path/df of a GAF file and it will return how many genes have at least one annotation in each aspect (C,F,P) or any (A)
+count_genes_annotated <- function(gaf_file) {
+  gaf_file = possibly_read_gaf(gaf_file)
+  return(c(
+    "C" = length(unique(subset(gaf_file, aspect == "C")$db_object_id)),
+    "F" = length(unique(subset(gaf_file, aspect == "F")$db_object_id)),
+    "P" = length(unique(subset(gaf_file, aspect == "P")$db_object_id)),
+    "A" = length(unique(gaf_file$db_object_id))
+    ))
+}
+
+# Pass the path/df of a GAF file and get back the median number of annotations for each gene in the GAF
+# in the C,F,P aspect and total median across all aspects (A)
+count_median_annotations <- function(gaf_file) {
+  gaf_file = possibly_read_gaf(gaf_file)
+  t = table(gaf_file$db_object_id, gaf_file$aspect)
+  return(c(
+    "C" = median(t[,"C"]),
+    "F" = median(t[,"F"]),
+    "P" = median(t[,"P"]),
+    "A" = median(t[,"C"]+t[,"F"]+t[,"P"])
+  ))
+}
+
+
[…]

### 2019-08-03 text/Paper.Rmd
Added Rmarkdown and included quantity table

--- 2019-03-08 manuscript/Manuscript.Rmd
@@
 date: "Febcember 32nd 3023"
-abstract: "Hello, this is the abstract."
-keywords: "keyword1, kw2, kw3... have to have at least 5, max 8"
 language: en-US
-output:
-  pdf_document:
-    dev: pdf
-    keep_tex: true
-    template: ./pandoc-frontiers-template.tex
-header-includes:
-- \usepackage{booktabs}
-- \usepackage{longtable}
-- \usepackage{array}
-- \usepackage{multirow}
-- \usepackage{wrapfig}
-- \usepackage{float}
-- \usepackage{colortbl}
-- \usepackage{pdflscape}
-- \usepackage{tabu}
-- \usepackage{threeparttable}
-- \usepackage{threeparttablex}
-- \usepackage[normalem]{ulem}
-- \usepackage{makecell}
-- \usepackage{xcolor}
+output: pdf_document
 ---
+
 ```{r load_libs, include=F}
@@
 # Results
-... a quantitative comparison of the datasets in Table \ref{tab:t_annotation_quantities}.
+... a quantitative comparison of the datasets in Table.
 
 ```{r t_annotation_quantities}
-dt2 <- read.csv("../data/results/quantity_table.csv", header=T)
+dt2 <- read.csv("../analyses/quantity/results/quantity_table.csv", header=T)
 headers_above = c(a = 3, b = 4, c = 4, d =4)

### 2019-08-04 Paper.tex
Set up rake system and install biopython

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={TBD},
            pdfauthor={The Pickles},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\providecommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}

  \title{TBD}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{The Pickles}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{Febcember 32nd 3023}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\begin{document}
\maketitle

\hypertarget{results}{%
\section{Results}\label{results}}

\ldots{} a quantitative comparison of the datasets in Table.

\begin{table}[t]

\caption{\label{tab:t_annotation_quantities}Quantitative metrics of the generated and existing functional annotation sets. C, F, P, and A refer to the aspects of the GO: Cellular Component, Biological Function, Molecular Process, and Any/All.}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}{lrlrrr>{\bfseries}r|rrr>{\bfseries}r|rrr>{\bfseries}r}
\toprule
\multicolumn{3}{c}{ } & \multicolumn{4}{c}{Annotations\textsuperscript{a}} & \multicolumn{4}{c}{Annotated Genes\textsuperscript{b}} & \multicolumn{4}{c}{Median Ann. per G.\textsuperscript{c}} \\
\cmidrule(l{3pt}r{3pt}){4-7} \cmidrule(l{3pt}r{3pt}){8-11} \cmidrule(l{3pt}r{3pt}){12-15}
Genome & Genes & Dataset & C & F & P & A & C & F & P & A & C & F & P & A\\
\midrule
\rowcolor{gray!6}  Arachis\_hypogaea &  & GOMAP & 153433 & 132944 & 493799 & 780176 & 57667 & 56855 & 67123 & 67124 & 2 & 2 & 6 & 10\\

Glycine\_max &  & GOMAP & 129215 & 114010 & 417575 & 660800 & 46020 & 47087 & 52871 & 52872 & 2 & 2 & 6 & 11\\

\rowcolor{gray!6}  Hordeum\_vulgarum &  & GOMAP & 88130 & 80371 & 272835 & 441336 & 35237 & 36487 & 39733 & 39734 & 2 & 2 & 5 & 10\\

Medicago\_truncatula.A17 &  & GOMAP & 107362 & 99719 & 364065 & 571146 & 42325 & 43736 & 50443 & 50444 & 2 & 2 & 6 & 10\\

\rowcolor{gray!6}  Medicago\_truncatula.R108 &  & GOMAP & 112343 & 108031 & 382322 & 602696 & 40332 & 50220 & 55706 & 55706 & 1 & 2 & 5 & 9\\

Oryza\_sativa &  & GOMAP & 72782 & 64783 & 248713 & 386278 & 28619 & 29876 & 35824 & 35825 & 2 & 2 & 6 & 9\\

\rowcolor{gray!6}  Phaseolus\_vulgaris &  & GOMAP & 72005 & 64583 & 229630 & 366218 & 25934 & 25539 & 27432 & 27433 & 2 & 2 & 6 & 11\\

Triticum\_aestivum &  & GOMAP & 267742 & 218839 & 786028 & 1272609 & 95604 & 98224 & 107890 & 107891 & 2 & 2 & 6 & 10\\

\rowcolor{gray!6}  Vigna\_unguiculata &  & GOMAP & 75867 & 68313 & 243278 & 387458 & 27173 & 27124 & 29772 & 29773 & 2 & 2 & 6 & 11\\

Zea\_mays.B73.v3 &  & GOMAP & 135251 & 87953 & 291855 & 515059 & 34867 & 38099 & 39469 & 39469 & 3 & 2 & 6 & 11\\

\rowcolor{gray!6}  Zea\_mays.B73.v4 &  & GOMAP & 88831 & 82849 & 278952 & 450632 & 36717 & 37431 & 39324 & 39324 & 2 & 2 & 6 & 10\\

Zea\_mays.Mo17 &  & GOMAP & 87573 & 79755 & 278043 & 445371 & 33618 & 35177 & 38620 & 38620 & 2 & 2 & 6 & 10\\

\rowcolor{gray!6}  Zea\_mays.PH207 &  & GOMAP & 90625 & 86106 & 288937 & 465668 & 35170 & 36843 & 40557 & 40557 & 2 & 2 & 6 & 10\\

Zea\_mays.W22 & \multirow{-14}{*}{\raggedleft\arraybackslash 100} & GOMAP & 95397 & 85616 & 290032 & 471045 & 36987 & 37764 & 40690 & 40690 & 2 & 2 & 6 & 10\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item[a] How many annotations in the C, F, and P aspect does this dataset contain? A = How many in total? $A = C + F + P$
\item[b] How many genes in the genome have at least one GO term from the C, F, P aspect annotated to them? A = How many at least one from any aspect? ($A = C \cup F \cup P$)
\item[c] Take a typical gene that is present in the annotation set. How many annotations does it have in each aspect? A = How many in total? Ask your favorite statistician why $A \neq C + F +P$
\end{tablenotes}
\end{threeparttable}}
\end{table}

\end{document}

### 2019-08-04 text/Paper.Rmd
Set up rake system and install biopython

@@
 ```{r t_annotation_quantities}
-dt2 <- read.csv("../analyses/quantity/results/quantity_table.csv", header=T)
+dt2 <- read.csv("analyses/quantity/results/quantity_table.csv", header=T)
 headers_above = c(a = 3, b = 4, c = 4, d =4)

### 2019-08-04 Rakefile.rb

@@ -1,0 +1,11 @@
+task :default => 'Paper.pdf'
+
+desc 'Typeset the Paper'
+file 'Paper.pdf' => ['analyses/quantity/results/quantity_table.csv', 'text/Paper.Rmd'] do
+  sh %q(R -e 'library("rmarkdown"); render("text/Paper.Rmd", output_file="../Paper.pdf", knit_root_dir="../", clean=T)')
+end
+
+desc 'Quantity analysis'
+file 'analyses/quantity/results/quantity_table.csv' => FileList['data/go_annotation_sets/*/*.gaf.gz'] + ['data/n_genes_per_genome.csv', 'analyses/quantity/quantity.R'] do
+  sh "Rscript analyses/quantity/quantity.R"
+end

### 2019-08-04 analyses/quantity/quantity.R

@@ -63,8 +63,8 @@ csv = data.frame(
   median_annotations_per_gene_a = 0
 )
 
-n_genes_per_genome = read.csv("../../data/n_genes_per_genome.csv", header = T)
-genomes = list.dirs("../../data/go_annotation_sets", recursive = F)
+n_genes_per_genome = read.csv("data/n_genes_per_genome.csv", header = T)
+genomes = list.dirs("data/go_annotation_sets", recursive = F)
 for(genome_path in genomes) {
   genome_name = basename(genome_path)
   print(genome_name)
@@ -96,4 +96,4 @@ for(genome_path in genomes) {
 }
 csv <- csv[2:nrow(csv),] # Drop empty dummy row
 
-write.csv(csv, 'results/quantity_table.csv', row.names = F)
+write.csv(csv, 'analyses/quantity/results/quantity_table.csv', row.names = F)

### 2019-08-05 Rakefile.rb
Started implementing cleanup step

@@ -6,6 +6,29 @@ file 'Paper.pdf' => ['analyses/quantity/results/quantity_table.csv', 'text/Paper
 end
 
 desc 'Quantity analysis'
-file 'analyses/quantity/results/quantity_table.csv' => FileList['data/go_annotation_sets/*/*.gaf.gz'] + ['data/n_genes_per_genome.csv', 'analyses/quantity/quantity.R'] do
+file 'analyses/quantity/results/quantity_table.csv' => [:cleanup, 'data/n_genes_per_genome.csv', 'analyses/quantity/quantity.R'] do
   sh "Rscript analyses/quantity/quantity.R"
 end
+
+# Cleanup
+def cleanup
+  rm_rf 'analyses/cleanup/results/*'
+  sh 'python analyses/cleanup/cleanup.py'
+end
+
+# Each individual cleaned up file depends on its non-cleaned source
+cleanup_targets = ['analyses/cleanup/results/cleanup_table.csv']
+file cleanup_targets.first do
+  cleanup
+end
+FileList.new("data/go_annotation_sets/*/*.gaf.gz").to_a.each do |f|
+  target = "analyses/cleanup/results/" + ((f.split(".")[0..-3] + ["mgaf.gz"]).join(".").split("/")[2..-1]).join("/")
+  file target => f do
+    cleanup
+  end
+  cleanup_targets << target
+end
+
+desc 'Clean up datasets'
+# Cleanup depends on all cleanup target files
+task :cleanup => cleanup_targets

### 2019-08-05 analyses/cleanup/cleanup.py

@@ -1,0 +1,96 @@
+# Cleans aggregated GAF file:
+# 1. Removes obsolete Annotations
+# 2. Merges GO terms to main term (alt_id->id)
+# 3. (optional) Adds transcript variant to column 17
+# 4. Changes assigned by and db columns to the following values:
+keep_columns = [1,3,4,8]
+# 5. Removes duplicates
+# 
+# Usage:
+#   python 2_cleanup.py [input-gaf-file] [OBO-file] [gene-to-transcript-map (optional)]
+#    - OBO-file: Gene ontology in obo format. Most recent version can be obtained from http://www.geneontology.org/page/download-ontology which might be good when using this script on your own results.
+#    - gene-to-transcript-map: headerless space separated file of gene_name transcript_name , used to add correct transcript_name to column 17. See 2_cleanup_resources/gene_to_used_transcript_map.csv for an example
+#  GAF output will be sent to STDOUT, status messages to STDERR. So if you want to save the cleaned up GAF you can redirect STDOUT
+#   python 2_cleanup.py [input-gaf-file] [OBO-file] [gene-to-transcript-map (optional)] > [output-gaf-file]
+# See README.md in this directory to see how to reproduce our results
+
+# This script uses the obo_parser.py taken from https://github.com/mschubert/python-obo/blob/master/obo/parser.py
+
+import obo_parser
+import sys
+import csv
+import gzip
+import os
+import glob
+from sets import Set
+
+### Preparation ###
+## Build list of obsolete ids and alt_ids
+
+merge_to = {} # merge_to[goterm] == id to be merged to.
+obsolete_ids = []
+
+print >> sys.stderr, 'Parsing go.obo...'
+with gzip.open('analyses/cleanup/go.obo.gz') as obofile:
+  parser = obo_parser.Parser(obofile)
+  for stanza in parser:
+    if not stanza.name == "Term":
+      continue
+
+    go_id = stanza.tags["id"][0]
+
+    if 'alt_id' in stanza.tags:
+      for alt_id in stanza.tags['alt_id']:
+        merge_to[alt_id] = go_id
+
+    if 'is_obsolete' in stanza.tags and stanza.tags['is_obsolete'][0] == "true":
+      obsolete_ids.append(go_id)
+
+
+def process_gaf(genome, dataset):
+  print("Processing " + genome + "/" + dataset)
+  printed_tuples = Set()
+  n_obsolete = 0
[…]

### 2019-08-05 analyses/cleanup/obo_parser.py

@@ -1,0 +1,264 @@
+#!/usr/bin/env python2
+"""
+A very simple and not 100% compliant parser for the OBO file format
+
+This parser is supplied "as is"; it is not an official parser, it
+might puke on perfectly valid OBO files, it might parse perfectly
+invalid OBO files, it might steal your kitten or set your garden shed
+on fire. Apart from that, it should be working, or at least
+it should be in a suitable condition to parse the Gene Ontology,
+which is my only test case anyway.
+
+Usage example::
+
+    import gene_ontology.obo as obo
+    parser = obo.Parser(open("gene_ontology.1_2.obo"))
+    gene_ontology = {}
+    for stanza in parser:
+        gene_ontology[stanza.tags["id"][0]] = stanza.tags
+"""
+
+__author__  = "Tamas Nepusz"
+__email__   = "tamas@cs.rhul.ac.uk"
+__copyright__ = "Copyright (c) 2009, Tamas Nepusz"
+__license__ = "MIT"
+__version__ = "0.1"
+
+
+__all__ = ["ParseError", "Stanza", "Parser", "Value"]
+
+
+from cStringIO import StringIO
+import re
+import tokenize
+
+
+class ParseError(Exception):
+    """Exception thrown when a parsing error occurred"""
+
+    def __init__(self, msg, lineno = 1):
+        Exception.__init__("%s near line %d" % (msg, lineno))
+        self.lineno = lineno
+
+
+#class Value(object):
+#    """Class representing a value and its modifiers in the OBO file
+#
+#    This class has two member variables. `value` is the value itself,
+#    `modifiers` are the corresponding modifiers in a tuple. Currently
+#    the modifiers are not parsed in any way, but this might change in
+#    the future.
+#    """
+#
+#    __slots__ = ["value", "modifiers"]
+#
+#    def __init__(self, value, modifiers=()):
+#        """Creates a new value"""
+#        self.value = str(value)
+#        if modifiers:
+#            self.modifiers = tuple(modifiers)
+#        else:
+#            self.modifiers = None
+#
+#    def __str__(self):
+#        """Returns the value itself (without modifiers)"""
+#        return str(self.value)
+#
+#    def __repr__(self):
+#        """Returns a Python representation of this object"""
+#        return "%s(%r, %r)" % (self.__class__.__name__, \
+#                self.value, self.modifiers)
+
+
+class Stanza(object):
+    """Class representing an OBO stanza.
+
+    An OBO stanza looks like this::
+
+      [name]
+      tag: value
[…]

### 2019-08-05 analyses/quantity/quantity.R

@@ -8,7 +8,7 @@ possibly_read_gaf <- function(gaf_file) {
   if(is.data.frame(gaf_file))
     return(gaf_file)
   if(is.character(gaf_file))
-    return(read.csv(gaf_file, skip=1, header=T, sep="\t"))
+    return(read.csv(gaf_file, header=T, sep="\t"))
   # If neither dataframe nor string: something is wrong:
   stop("Passed argument is neither data frame nor path to GAF file!")
 }
@@ -64,11 +64,11 @@ csv = data.frame(
 )
 
 n_genes_per_genome = read.csv("data/n_genes_per_genome.csv", header = T)
-genomes = list.dirs("data/go_annotation_sets", recursive = F)
+genomes = list.dirs("analyses/cleanup/results", recursive = F)
 for(genome_path in genomes) {
   genome_name = basename(genome_path)
   print(genome_name)
-  for(gaf_file in list.files(genome_path, pattern = ".gaf", full.names = T)) {
+  for(gaf_file in list.files(genome_path, pattern = ".mgaf", full.names = T)) {
     print(gaf_file)
     gaf_df = possibly_read_gaf(gaf_file)
     aspect_counts = count_aspects(gaf_df)

### 2019-08-06 Paper.tex
Started implementing cleanup step
Finish implementing cleanup

@@
 
+\hypertarget{methods}{%
+\section{Methods}\label{methods}}
+
+\hypertarget{clean-up}{%
+\subsection{Clean up}\label{clean-up}}
+
+All functional annotation sets were cleaned up the following way (using
+definitions from the Gene Ontology version 2019-07-01):
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Any annotations where the GO accession was marked as obsolete were
+  removed.
+\item
+  Some terms in the GO have `alternative ids'. When naively removing
+  duplicates, two entries will not be recognized as duplicates if they
+  have different accessions pointing to the same GO term. Therefore, all
+  GO accessions were changed to their respecitve `main id' and the
+  dataset was again scanned for duplicates.
+\end{enumerate}
+
+Table 1 provides information on the number of annotations that were
+removed this way from each dataset. All further analyses were performed
+on the cleaned datasets since we assume the user will only be interested
+in still valid and non-redundant functional annotations.
+
 \hypertarget{results}{%
@@
 
-\caption{\label{tab:t_annotation_quantities}Quantitative metrics of the generated and existing functional annotation sets.
+\caption{\label{tab:cleanup_table}Number of removed annotations during cleanup.}
+\centering
+\begin{tabular}{llrr}
+\toprule
+Genome & Dataset & Obsolete Annotations & Duplicates\\
+\midrule
+\rowcolor{gray!6}  Triticum\_aestivum & GOMAP & 285 & 0\\
+\cmidrule{1-4}
+Hordeum\_vulgarum & GOMAP & 101 & 0\\
+\cmidrule{1-4}
+\rowcolor{gray!6}  Glycine\_max & GOMAP & 203 & 0\\
+\cmidrule{1-4}
+Arachis\_hypogaea & GOMAP & 0 & 0\\
+\cmidrule{1-4}
+\rowcolor{gray!6}  Zea\_mays.PH207 & GOMAP & 798 & 76\\
+\cmidrule{1-4}
+Zea\_mays.Mo17 & GOMAP & 726 & 77\\
+\cmidrule{1-4}
+\rowcolor{gray!6}  Phaseolus\_vulgaris & GOMAP & 0 & 0\\
+\cmidrule{1-4}
+Vigna\_unguiculata & GOMAP & 0 & 0\\
+\cmidrule{1-4}
+\rowcolor{gray!6}  Medicago\_truncatula.R108 & GOMAP & 0 & 0\\
+\cmidrule{1-4}
+Zea\_mays.B73.v3 & GOMAP & 1107 & 70\\
+\cmidrule{1-4}
+\rowcolor{gray!6}  Zea\_mays.W22 & GOMAP & 754 & 82\\
+\cmidrule{1-4}
+Medicago\_truncatula.A17 & GOMAP & 0 & 0\\
+\cmidrule{1-4}
+\rowcolor{gray!6}  Zea\_mays.B73.v4 & GOMAP & 752 & 83\\
+\cmidrule{1-4}
+Oryza\_sativa & GOMAP & 111 & 2\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{table}[t]
+
+\caption{\label{tab:t_annotation_quantities}Quantitative metrics of the cleaned functional annotation sets.
 C, F, P, and A refer to the aspects of the GO: Cellular Component, Biological Function, Molecular Process, and Any/All.}
@@
 
-Glycine\_max &  & GOMAP & 129215 & 114010 & 417575 & 660800 & 46020 & 47087 & 52871 & 52872 & 2 & 2 & 6 & 11\\
+Glycine\_max &  & GOMAP & 129215 & 113827 & 417555 & 660597 & 46020 & 47034 & 52871 & 52872 & 2 & 2 & 6 & 11\\
 
-\rowcolor{gray!6}  Hordeum\_vulgarum &  & GOMAP & 88130 & 80371 & 272835 & 441336 & 35237 & 36487 & 39733 & 39734 & 2 & 2 & 5 & 10\\
+\rowcolor{gray!6}  Hordeum\_vulgarum &  & GOMAP & 88130 & 80282 & 272823 & 441235 & 35237 & 36470 & 39733 & 39734 & 2 & 2 & 5 & 10\\
 
@@
 
-Oryza\_sativa &  & GOMAP & 72782 & 64783 & 248713 & 386278 & 28619 & 29876 & 35824 & 35825 & 2 & 2 & 6 & 9\\
+Oryza\_sativa &  & GOMAP & 72780 & 64685 & 248700 & 386165 & 28619 & 29853 & 35824 & 35825 & 2 & 2 & 6 & 9\\
 
@@
 
-Triticum\_aestivum &  & GOMAP & 267742 & 218839 & 786028 & 1272609 & 95604 & 98224 & 107890 & 107891 & 2 & 2 & 6 & 10\\
+Triticum\_aestivum &  & GOMAP & 267741 & 218623 & 785960 & 1272324 & 95604 & 98187 & 107890 & 107891 & 2 & 2 & 6 & 10\\
 
@@
 
-Zea\_mays.B73.v3 &  & GOMAP & 135251 & 87953 & 291855 & 515059 & 34867 & 38099 & 39469 & 39469 & 3 & 2 & 6 & 11\\
+Zea\_mays.B73.v3 &  & GOMAP & 135211 & 87420 & 291251 & 513882 & 34866 & 38073 & 39468 & 39469 & 3 & 2 & 6 & 11\\
 
-\rowcolor{gray!6}  Zea\_mays.B73.v4 &  & GOMAP & 88831 & 82849 & 278952 & 450632 & 36717 & 37431 & 39324 & 39324 & 2 & 2 & 6 & 10\\
+\rowcolor{gray!6}  Zea\_mays.B73.v4 &  & GOMAP & 88827 & 82251 & 278719 & 449797 & 36717 & 37337 & 39323 & 39324 & 2 & 2 & 6 & 10\\
 
-Zea\_mays.Mo17 &  & GOMAP & 87573 & 79755 & 278043 & 445371 & 33618 & 35177 & 38620 & 38620 & 2 & 2 & 6 & 10\\
+Zea\_mays.Mo17 &  & GOMAP & 87567 & 79214 & 277787 & 444568 & 33618 & 35105 & 38619 & 38620 & 2 & 2 & 6 & 10\\
 
-\rowcolor{gray!6}  Zea\_mays.PH207 &  & GOMAP & 90625 & 86106 & 288937 & 465668 & 35170 & 36843 & 40557 & 40557 & 2 & 2 & 6 & 10\\
+\rowcolor{gray!6}  Zea\_mays.PH207 &  & GOMAP & 90617 & 85500 & 288677 & 464794 & 35170 & 36762 & 40556 & 40557 & 2 & 2 & 6 & 10\\
 
-Zea\_mays.W22 & \multirow{-14}{*}{\raggedleft\arraybackslash 100} & GOMAP & 95397 & 85616 & 290032 & 471045 & 36987 & 37764 & 40690 & 40690 & 2 & 2 & 6 & 10\\
+Zea\_mays.W22 & \multirow{-14}{*}{\raggedleft\arraybackslash 100} & GOMAP & 95390 & 85039 & 289780 & 470209 & 36987 & 37685 & 40689 & 40690 & 2 & 2 & 6 & 10\\
 \bottomrule

### 2019-08-06 text/Paper.Rmd
Finish implementing cleanup

@@
 
+# Methods
+
+## Clean up
+All functional annotation sets were cleaned up the following way (using definitions from the Gene Ontology version 2019-07-01):
+
+1. Any annotations where the GO accession was marked as obsolete were removed.
+2.
+Some terms in the GO have 'alternative ids'.
+When naively removing duplicates, two entries will not be recognized as duplicates if they have different accessions pointing to the same GO term.
+Therefore, all GO accessions were changed to their respecitve 'main id' and the dataset was again scanned for duplicates.
+
+Table 1 provides information on the number of annotations that were removed this way from each dataset.
+All further analyses were performed on the cleaned datasets since we assume the user will only be interested in still valid and non-redundant functional annotations.
+
 # Results
 ... a quantitative comparison of the datasets in Table.
+
+```{r cleanup_table}
+dt2 <- read.csv("analyses/cleanup/results/cleanup_table.csv", header=T)
+kable(dt2, booktabs=T, caption = "Number of removed annotations during cleanup.", col.names=c("Genome", "Dataset", "Obsolete Annotations", "Duplicates")) %>%
+  kable_styling(latex_options = c("striped")) %>%
+  collapse_rows(columns = 1, latex_hline="major")
+```
 
@@
   paste0("Median Ann. per G.", footnote_marker_alphabet(3, double_escape=T)))
-kable(dt2, booktabs=T, caption = "Quantitative metrics of the generated and existing functional annotation sets.
+kable(dt2, booktabs=T, caption = "Quantitative metrics of the cleaned functional annotation sets.
 C, F, P, and A refer to the aspects of the GO: Cellular Component, Biological Function, Molecular Process, and Any/All.", col.names=c("Genome", "Genes", "Dataset", "C", "F", "P", "A","C", "F", "P", "A","C", "F", "P", "A")) %>%

### 2019-08-06 Rakefile.rb

@@ -5,10 +5,6 @@ file 'Paper.pdf' => ['analyses/quantity/results/quantity_table.csv', 'text/Paper
   sh %q(R -e 'library("rmarkdown"); render("text/Paper.Rmd", output_file="../Paper.pdf", knit_root_dir="../", clean=T)')
 end
 
-desc 'Quantity analysis'
-file 'analyses/quantity/results/quantity_table.csv' => [:cleanup, 'data/n_genes_per_genome.csv', 'analyses/quantity/quantity.R'] do
-  sh "Rscript analyses/quantity/quantity.R"
-end
 
 # Cleanup
 def cleanup
@@ -32,3 +28,8 @@ end
 desc 'Clean up datasets'
 # Cleanup depends on all cleanup target files
 task :cleanup => cleanup_targets
+
+desc 'Quantity analysis'
+file 'analyses/quantity/results/quantity_table.csv' => cleanup_targets + ['data/n_genes_per_genome.csv', 'analyses/quantity/quantity.R'] do
+  sh "Rscript analyses/quantity/quantity.R"
+end

### 2019-08-06 analyses/cleanup/cleanup.py

@@ -88,9 +88,7 @@ for genome in [x for x in os.listdir("data/go_annotation_sets") if os.path.isdir
     dataset = ".".join(os.path.basename(dataset).split(".")[:-2])
     stats_table.append([genome, dataset] + process_gaf(genome, dataset))
 
-# @TODO this doesn't work yet
-puts stats_table
 with open("analyses/cleanup/results/cleanup_table.csv", "w") as f:
   writer = csv.writer(f, delimiter=",")
   for r in stats_table:
-    writer.writerow[r]
+    writer.writerow(r)

### 2019-08-06 text/Paper.Rmd
Replace absolute genes annotated with percent value in quantity table

@@
 dt2 <- read.csv("analyses/quantity/results/quantity_table.csv", header=T)
+# Drop the absolute 'genes annotated' counts, we only want the percentual ones
+dt2 <- dt2[, !names(dt2) %in% c("genes_annotated_c", "genes_annotated_f", "genes_annotated_p", "genes_annotated_a")]
 headers_above = c(a = 3, b = 4, c = 4, d =4)
@@
   paste0("Annotations", footnote_marker_alphabet(1, double_escape=T)),
-  paste0("Annotated Genes", footnote_marker_alphabet(2, double_escape=T)), 
+  paste0("Annotated Genes [\\\\%]", footnote_marker_alphabet(2, double_escape=T)), 
   paste0("Median Ann. per G.", footnote_marker_alphabet(3, double_escape=T)))

### 2019-08-06 analyses/quantity/quantity.R

@@ -57,6 +57,11 @@ csv = data.frame(
   genes_annotated_f = 0,
   genes_annotated_p = 0,
   genes_annotated_a = 0,
+  # Proportion (percentage) of genes annotated
+  p_genes_annotated_c = 0,
+  p_genes_annotated_f = 0,
+  p_genes_annotated_p = 0,
+  p_genes_annotated_a = 0,
   median_annotations_per_gene_c = 0,
   median_annotations_per_gene_f = 0,
   median_annotations_per_gene_p = 0,
@@ -87,6 +92,10 @@ for(genome_path in genomes) {
       genes_annotated_f = genes_annotated[["F"]],
       genes_annotated_p = genes_annotated[["P"]],
       genes_annotated_a = genes_annotated[["A"]],
+      p_genes_annotated_c = genes_annotated[["C"]]/n_genes_per_genome[n_genes_per_genome$genome == genome_name,"n_genes"],
+      p_genes_annotated_f = genes_annotated[["F"]]/n_genes_per_genome[n_genes_per_genome$genome == genome_name,"n_genes"],
+      p_genes_annotated_p = genes_annotated[["P"]]/n_genes_per_genome[n_genes_per_genome$genome == genome_name,"n_genes"],
+      p_genes_annotated_a = genes_annotated[["A"]]/n_genes_per_genome[n_genes_per_genome$genome == genome_name,"n_genes"],
       median_annotations_per_gene_c = medians[["C"]],
       median_annotations_per_gene_f = medians[["F"]],
       median_annotations_per_gene_p = medians[["P"]],

### 2019-08-07 data/go_annotation_sets/Oryza_sativa/transformGoldStandard2GAF.sh
Added Oryza sativa gold standard

@@ -1,0 +1,32 @@
+# This file converts the GoldStandard TSV file downloaded from Gramene to the GAF 2 format
+# so that we don't need to deal with different file formats in the following analyses.
+
+# Print GAF headers
+echo "!gaf-version:2.0" > GoldStandard.gaf
+echo "!db	db_object_id	db_object_symbol	qualifier	term_accession	db_reference	evidence_code	with	aspect	db_object_name	db_object_synonym	db_object_type	taxon	date	assigned_by	annotation_extension	gene_product_form_id" >> GoldStandard.gaf
+
+# Skip TSV header and rearrange/expand columns
+tail -n +2 GoldStandard.tsv | awk -F $'\t' 'BEGIN {OFS = FS} 
+ { print "Gramene/Plant_Genes_61/IRGSP-1.0", 
+   $1, 
+   $1,
+   "",
+   $2, 
+   "", 
+   $4,
+   "",
+   $3,
+   "",
+   "",
+   "protein",
+   "taxon:4530",
+   "",
+   "",
+   "",
+   ""
+ }' >> GoldStandard.gaf
+
+# Rename aspect names of the TSV to GAF codes
+sed -i 's/cellular_component/C/' GoldStandard.gaf
+sed -i 's/biological_process/P/' GoldStandard.gaf
+sed -i 's/molecular_function/F/' GoldStandard.gaf

### 2019-08-08 Rakefile.rb
Quality evaluation preparation 2

@@ -12,6 +12,13 @@ def cleanup
   sh 'python analyses/cleanup/cleanup.py'
 end
 
+# converted GO files
+['analyses/cleanup/results/GO.json', 'analyses/cleanup/results/GO_names.json'].each do |f|
+  file f => ['analyses/cleanup/convert_obo.py', 'analyses/cleanup/go.obo.gz', 'analyses/cleanup/obo_parser.py'] do
+    sh 'python analyses/cleanup/convert_obo.py'
+  end
+end
+
 # Each individual cleaned up file depends on its non-cleaned source
 cleanup_targets = ['analyses/cleanup/results/cleanup_table.csv']
 file cleanup_targets.first do
@@ -19,7 +26,7 @@ file cleanup_targets.first do
 end
 FileList.new("data/go_annotation_sets/*/*.gaf.gz").to_a.each do |f|
   target = "analyses/cleanup/results/" + ((f.split(".")[0..-3] + ["mgaf.gz"]).join(".").split("/")[2..-1]).join("/")
-  file target => f do
+  file target => [f, 'analyses/cleanup/cleanup.py', 'analyses/cleanup/go.obo.gz'] do
     cleanup
   end
   cleanup_targets << target

### 2019-08-08 analyses/cleanup/convert_obo.py

@@ -1,0 +1,54 @@
+# This script reads an OBO file using the obo_parser and outputs JSON files that are then used by the crystal scripts.
+# The GO.json file looks like this:
+# {
+#   "parents": {
+#     "GO:122335": ["GO:4433", "GO:5432"],
+#     "GO:122341": ["GO:1243", "GO:1532"],
+#     ...
+#   },
+#   "main_id" : {"GO:1443":"GO:532", "GO:2533":"GO:5234"}
+#   "obsolete": ["GO:1432", "GO:4322", ...]
+# }
+#
+# The GO_names.json file looks like this:
+# {
+#   "GO:43334":"Photosynthesis",
+#   "GO:93743":"Something else",
+#   ...
+# }
+
+import obo_parser
+import json
+import gzip
+
+parents = {}
+main_id = {}
+obsolete = []
+go_names = {}
+with gzip.open("analyses/cleanup/go.obo.gz") as obofile:
+  parser = obo_parser.Parser(obofile)
+  for stanza in parser:
+    if not stanza.name == "Term":
+      continue
+
+    go_id = stanza.tags["id"][0]
+
+    if 'is_a' in stanza.tags:
+      parents[go_id] = stanza.tags['is_a']
+    else:
+      parents[go_id] = []
+
+    if 'alt_id' in stanza.tags:
+      for alt_id in stanza.tags['alt_id']:
+        main_id[alt_id] = go_id
+
+    if 'is_obsolete' in stanza.tags and stanza.tags['is_obsolete'][0] == "true":
+      obsolete.append(go_id)
+    else:
+      go_names[go_id] = stanza.tags['name'][0]
+
+with open('analyses/cleanup/results/GO.json', 'w') as f:
+  f.write(json.dumps({"parents":parents,"main_id":main_id,"obsolete":obsolete},indent=2))
+
+with open('analyses/cleanup/results/GO_names.json', 'w') as f:
+  f.write(json.dumps(go_names,indent=2))

### 2019-08-14 text/02-methods.Rmd
Switch to Bookdown

--- 2019-08-06 text/Paper.Rmd
@@
----
-title: 'TBD'
-author: "The Pickles"
-date: "Febcember 32nd 3023"
-language: en-US
-output: pdf_document
----
-
-```{r load_libs, include=F}
-library(knitr)
-library(kableExtra)
-knitr::opts_chunk$set(echo=FALSE)
-```
-
 # Methods
@@
 All further analyses were performed on the cleaned datasets since we assume the user will only be interested in still valid and non-redundant functional annotations.
-
-# Results
-... a quantitative comparison of the datasets in Table.
-
-```{r cleanup_table}
-dt2 <- read.csv("analyses/cleanup/results/cleanup_table.csv", header=T)
-kable(dt2, booktabs=T, caption = "Number of removed annotations during cleanup.", col.names=c("Genome", "Dataset", "Obsolete Annotations", "Duplicates")) %>%
-  kable_styling(latex_options = c("striped")) %>%
-  collapse_rows(columns = 1, latex_hline="major")
-```
-
-```{r t_annotation_quantities}
-dt2 <- read.csv("analyses/quantity/results/quantity_table.csv", header=T)
-headers_above = c(a = 3, b = 4, c = 4, d =4)
-names(headers_above) <- c(" ", 
-  paste0("Annotations", footnote_marker_alphabet(1, double_escape=T)),
-  paste0("Annotated Genes", footnote_marker_alphabet(2, double_escape=T)), 
-  paste0("Median Ann. per G.", footnote_marker_alphabet(3, double_escape=T)))
-kable(dt2, booktabs=T, caption = "Quantitative metrics of the cleaned functional annotation sets.
-C, F, P, and A refer to the aspects of the GO: Cellular Component, Biological Function, Molecular Process, and Any/All.", col.names=c("Genome", "Genes", "Dataset", "C", "F", "P", "A","C", "F", "P", "A","C", "F", "P", "A")) %>%
-  kable_styling(latex_options = c("striped", "scale_down")) %>%
-  add_header_above(headers_above, escape=F)%>%
-  column_spec(c(15), bold = T) %>%
-  column_spec(c(7,11), bold=T, border_right = T) %>%
-  collapse_rows(columns = 1:2, latex_hline="major") %>%
-  footnote(alphabet=c(
-    "How many annotations in the C, F, and P aspect does this dataset contain? A = How many in total? $A = C + F + P$",
-    "How many genes in the genome have at least one GO term from the C, F, P aspect annotated to them? A = How many at least one from any aspect? ($A = C \\\\cup F \\\\cup P$)",
-    "Take a typical gene that is present in the annotation set. How many annotations does it have in each aspect? A = How many in total? Ask your favorite statistician why $A \\\\neq C + F +P$"
-  ), threeparttable=T, escape=F)
-```

### 2019-08-14 text/03-results.Rmd
Switch to Bookdown

--- 2019-08-04 text/Paper.Rmd
@@
----
-title: 'TBD'
-author: "The Pickles"
-date: "Febcember 32nd 3023"
-language: en-US
-output: pdf_document
----
-
-```{r load_libs, include=F}
-library(knitr)
-library(kableExtra)
-knitr::opts_chunk$set(echo=FALSE)
-```
-
 # Results
@@
 
-```{r t_annotation_quantities}
-dt2 <- read.csv("analyses/quantity/results/quantity_table.csv", header=T)
+```{r cleanup-table}
+dt2 <- read.csv("../analyses/cleanup/results/cleanup_table.csv", header=T)
+kable(dt2, booktabs=TRUE, caption = "Number of removed annotations during cleanup.", col.names=c("Genome", "Dataset", "Obsolete Annotations", "Duplicates")) %>%
+ kable_styling(latex_options = c("striped")) %>%
+ collapse_rows(columns = 1, latex_hline="major")
+```
+
+```{r annotation-quantities}
+dt2 <- read.csv("../analyses/quantity/results/quantity_table.csv", header=T)
+# Drop the absolute 'genes annotated' counts, we only want the percentual ones
+dt2 <- dt2[, !names(dt2) %in% c("genes_annotated_c", "genes_annotated_f", "genes_annotated_p", "genes_annotated_a")]
 headers_above = c(a = 3, b = 4, c = 4, d =4)
@@
   paste0("Annotations", footnote_marker_alphabet(1, double_escape=T)),
-  paste0("Annotated Genes", footnote_marker_alphabet(2, double_escape=T)), 
+  paste0("Annotated Genes [\\\\%]", footnote_marker_alphabet(2, double_escape=T)), 
   paste0("Median Ann. per G.", footnote_marker_alphabet(3, double_escape=T)))
-kable(dt2, booktabs=T, caption = "Quantitative metrics of the generated and existing functional annotation sets.
+kable(dt2, booktabs=T, caption = "Quantitative metrics of the cleaned functional annotation sets.
 C, F, P, and A refer to the aspects of the GO: Cellular Component, Biological Function, Molecular Process, and Any/All.", col.names=c("Genome", "Genes", "Dataset", "C", "F", "P", "A","C", "F", "P", "A","C", "F", "P", "A")) %>%

### 2019-08-14 text/index.Rmd
Switch to Bookdown

---
title: "This is the title"
author: "The Pickles"
date: "Febcember 32nd 3023"
language: en-US
site: "bookdown::bookdown_site"
output:
  bookdown::pdf_book:
    keep_tex: true
    keep_md: true
    includes:
      in_header:
        preamble.tex
documentclass: book
---

```{r load_libs, include=F}
library(knitr)
library(kableExtra)
knitr::opts_chunk$set(echo=FALSE)
```

# Introduction
Hello, how are we doing?

### 2019-08-14 Rakefile.rb

@@ -1,8 +1,8 @@
 task :default => 'Paper.pdf'
 
 desc 'Typeset the Paper'
-file 'Paper.pdf' => ['analyses/quantity/results/quantity_table.csv', 'text/Paper.Rmd'] do
-  sh %q(R -e 'library("rmarkdown"); render("text/Paper.Rmd", output_file="../Paper.pdf", knit_root_dir="../", clean=T)')
+file 'Paper.pdf' => ['analyses/quantity/results/quantity_table.csv'] + FileList.new("text/*") do
+  sh %q(R -e 'library("bookdown"); xfun::in_dir("text", render_book("index.Rmd", output_file="../../Paper.pdf", clean=T))')
 end
 
 

### 2019-08-18 Paper.tex
Replace absolute genes annotated with percent value in quantity table
Added Oryza sativa gold standard
Use Frontiers template

@@
-\documentclass[]{article}
-\usepackage{lmodern}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-\else % if luatex or xelatex
-  \ifxetex
-    \usepackage{mathspec}
-  \else
-    \usepackage{fontspec}
-  \fi
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-\fi
-% use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
-\usepackage{microtype}
-\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\usepackage[margin=1in]{geometry}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% This is just an example/guide for you to refer to when submitting manuscripts to Frontiers, it is not mandatory to use Frontiers .cls files nor frontiers.tex  %
+% This will only generate the Manuscript, the final article will be typeset by Frontiers after acceptance.
+%                                              %
+%                                                                                                                                                         %
+% When submitting your files, remember to upload this *tex file, the pdf generated with it, the *bib file (if bibliography is not within the *tex) and all the figures.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%% Version 3.4 Generated 2018/06/15 %%%
+%%% You will need to have the following packages installed: datetime, fmtcount, etoolbox, fcprefix, which are normally inlcuded in WinEdt. %%%
+%%% In http://www.ctan.org/ you can find the packages and how to install them, if necessary. %%%
+
+\documentclass[utf8]{frontiersSCNS}
+
+%\setcitestyle{square} % for Physics and Applied Mathematics and Statistics articles
+\usepackage{url,hyperref,lineno,microtype,subcaption}
+\usepackage[onehalfspacing]{setspace}
+
+\linenumbers
+
+% BELOW TAKEN FROM rticles plos template
+%
+% amsmath package, useful for mathematical formulas
+\usepackage{amsmath}
+% amssymb package, useful for mathematical symbols
+\usepackage{amssymb}
+
+% hyperref package, useful for hyperlinks
 \usepackage{hyperref}
-\hypersetup{unicode=true,
-            pdftitle={TBD},
-            pdfauthor={The Pickles},
-            pdfborder={0 0 0},
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
-\usepackage{graphicx,grffile}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
-\setlength{\emergencystretch}{3em}  % prevent overfull lines
+
+% graphicx package, useful for including eps and pdf graphics
+% include graphics with the command \includegraphics
+\usepackage{graphicx}
+
+% Sweave(-like)
+\usepackage{fancyvrb}
+\DefineVerbatimEnvironment{Sinput}{Verbatim}{fontshape=sl}
+\DefineVerbatimEnvironment{Soutput}{Verbatim}{}
+\DefineVerbatimEnvironment{Scode}{Verbatim}{fontshape=sl}
+\newenvironment{Schunk}{}{}
+\DefineVerbatimEnvironment{Code}{Verbatim}{}
+\DefineVerbatimEnvironment{CodeInput}{Verbatim}{fontshape=sl}
+\DefineVerbatimEnvironment{CodeOutput}{Verbatim}{}
+\newenvironment{CodeChunk}{}{}
+
+% cite package, to clean up citations in the main text. Do not remove.
+\usepackage{cite}
+
+\usepackage{color}
+
 \providecommand{\tightlist}{%
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{0}
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
 
-%%% Use protect on footnotes to avoid problems with footnotes in titles
-\let\rmarkdownfootnote\footnote%
-\def\footnote{\protect\rmarkdownfootnote}
+% Below is from frontiers
+%
+\bibliographystyle{frontiersinSCNS}
+% Use doublespacing - comment out for single spacing
+%\usepackage{setspace}
+%\doublespacing
 
-%%% Change title format to be more compact
-\usepackage{titling}
+% Leave a blank line between paragraphs instead of using \\
 
-% Create subtitle command for use in maketitle
-\providecommand{\subtitle}[1]{
-  \posttitle{
-    \begin{center}\large#1\end{center}
-    }
-}
+\def\keyFont{\fontsize{8}{11}\helveticabold }
 
-\setlength{\droptitle}{-2em}
+%% ** EDIT HERE **
+%% PLEASE INCLUDE ALL MACROS BELOW
 
-  \title{TBD}
-    \pretitle{\vspace{\droptitle}\centering\huge}
-  \posttitle{\par}
-    \author{The Pickles}
-    \preauthor{\centering\large\emph}
-  \postauthor{\par}
-      \predate{\centering\large\emph}
-  \postdate{\par}
-    \date{Febcember 32nd 3023}
+%% END MACROS SECTION
 
+%\usepackage[table]{xcolor}
 \usepackage{booktabs}
@@
 \usepackage{makecell}
-\usepackage{xcolor}
+
+\def\Authors{
+  First Author\,\textsuperscript{1},
+  Co-Author\,\textsuperscript{2},
+  Co-Author\,\textsuperscript{1,3*}}
+
+\def\Address{
+
+  \textsuperscript{1} Department X, Institution X,  City X,  State XX,  Country X
+
+  \textsuperscript{2} Department X, Institution X,  City X,  State XX,  Country X
+
+  \textsuperscript{3} Department X, Institution X,  City X,  State XX,  Country X
+  }
+
+  \def\firstAuthorLast{LASTNAME {et~al.}}
+
+  \def\corrAuthor{Co-Author}\def\corrAddress{Laboratory X, Institute X, Department X, Organization X\\Street X\\City X, State XX, Zip Code X Country X}\def\corrEmail{\href{mailto:email@uni.edu}{\nolinkurl{email@uni.edu}}}
 
 \begin{document}
+\onecolumn
+\firstpage{1}
+
+\title[Short Title]{Article Title}
+\author[\firstAuthorLast]{\Authors}
+\address{} %This field will be automatically populated
+\correspondance{} %This field will be automatically populated
+
+\extraAuth{}% If there are more than 1 corresponding author, comment this line and uncomment the next one.
+%\extraAuth{corresponding Author2 \\ Laboratory X2, Institute X2, Department X2, Organization X2, Street X2, City X2 , State XX2 (only USA, Canada and Australia), Zip Code2, X2 Country X2, email2@uni2.edu}
+
 \maketitle
+
+\begin{abstract}
+
+Abstract length and content varies depending on article type. Refer to 
+\url{http://www.frontiersin.org/about/AuthorGuidelines} for abstract requirement
+and length according to article type.
+
+%All article types: you may provide up to 8 keywords; at least 5 are mandatory.
+\tiny
+ \keyFont{ \section{Keywords:} Text Text Text Text Text Text Text Text }
+
+\end{abstract}
+
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
+
+Hello, how are we doing?
 
@@
 
-All functional annotation sets were cleaned up the following way (using
-definitions from the Gene Ontology version 2019-07-01):
+All functional annotation sets were cleaned up the following way (using definitions from the Gene Ontology version 2019-07-01):
 
@@
 \item
-  Any annotations where the GO accession was marked as obsolete were
-  removed.
+  Any annotations where the GO accession was marked as obsolete were removed.
 \item
-  Some terms in the GO have `alternative ids'. When naively removing
-  duplicates, two entries will not be recognized as duplicates if they
-  have different accessions pointing to the same GO term. Therefore, all
-  GO accessions were changed to their respecitve `main id' and the
-  dataset was again scanned for duplicates.
+  Some terms in the GO have `alternative ids'.
+When naively removing duplicates, two entries will not be recognized as duplicates if they have different accessions pointing to the same GO term.
+Therefore, all GO accessions were changed to their respecitve `main id' and the dataset was again scanned for duplicates.
 \end{enumerate}
 
-Table 1 provides information on the number of annotations that were
-removed this way from each dataset. All further analyses were performed
-on the cleaned datasets since we assume the user will only be interested
-in still valid and non-redundant functional annotations.
+Table 1 provides information on the number of annotations that were removed this way from each dataset.
+All further analyses were performed on the cleaned datasets since we assume the user will only be interested in still valid and non-redundant functional annotations.
 
@@
 
-\caption{\label{tab:cleanup_table}Number of removed annotations during cleanup.}
+\caption{\label{tab:cleanup-table}Number of removed annotations during cleanup.}
 \centering
@@
 \cmidrule{1-4}
-Oryza\_sativa & GOMAP & 111 & 2\\
+ & GoldStandard & 38 & 556\\
+
+\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash Oryza\_sativa} & GOMAP & 111 & 2\\
 \bottomrule
@@
 
-\caption{\label{tab:t_annotation_quantities}Quantitative metrics of the cleaned functional annotation sets.
+\caption{\label{tab:annotation-quantities}Quantitative metrics of the cleaned functional annotation sets.
 C, F, P, and A refer to the aspects of the GO: Cellular Component, Biological Function, Molecular Process, and Any/All.}
@@
 \toprule
-\multicolumn{3}{c}{ } & \multicolumn{4}{c}{Annotations\textsuperscript{a}} & \multicolumn{4}{c}{Annotated Genes\textsuperscript{b}} & \multicolumn{4}{c}{Median Ann. per G.\textsuperscript{c}} \\
+\multicolumn{3}{c}{ } & \multicolumn{4}{c}{Annotations\textsuperscript{a}} & \multicolumn{4}{c}{Annotated Genes [\%]\textsuperscript{b}} & \multicolumn{4}{c}{Median Ann. per G.\textsuperscript{c}} \\
 \cmidrule(l{3pt}r{3pt}){4-7} \cmidrule(l{3pt}r{3pt}){8-11} \cmidrule(l{3pt}r{3pt}){12-15}
@@
 \midrule
-\rowcolor{gray!6}  Arachis\_hypogaea &  & GOMAP & 153433 & 132944 & 493799 & 780176 & 57667 & 56855 & 67123 & 67124 & 2 & 2 & 6 & 10\\
+\rowcolor{gray!6}  Arachis\_hypogaea &  & GOMAP & 153433 & 132944 & 493799 & 780176 & 576.67 & 568.55 & 671.23 & 671.24 & 2 & 2 & 6 & 10\\
 
-Glycine\_max &  & GOMAP & 129215 & 113827 & 417555 & 660597 & 46020 & 47034 & 52871 & 52872 & 2 & 2 & 6 & 11\\
+Glycine\_max &  & GOMAP & 129215 & 113827 & 417555 & 660597 & 460.20 & 470.34 & 528.71 & 528.72 & 2 & 2 & 6 & 11\\
 
-\rowcolor{gray!6}  Hordeum\_vulgarum &  & GOMAP & 88130 & 80282 & 272823 & 441235 & 35237 & 36470 & 39733 & 39734 & 2 & 2 & 5 & 10\\
+\rowcolor{gray!6}  Hordeum\_vulgarum &  & GOMAP & 88130 & 80282 & 272823 & 441235 & 352.37 & 364.70 & 397.33 & 397.34 & 2 & 2 & 5 & 10\\
 
-Medicago\_truncatula.A17 &  & GOMAP & 107362 & 99719 & 364065 & 571146 & 42325 & 43736 & 50443 & 50444 & 2 & 2 & 6 & 10\\
+Medicago\_truncatula.A17 &  & GOMAP & 107362 & 99719 & 364065 & 571146 & 423.25 & 437.36 & 504.43 & 504.44 & 2 & 2 & 6 & 10\\
 
-\rowcolor{gray!6}  Medicago\_truncatula.R108 &  & GOMAP & 112343 & 108031 & 382322 & 602696 & 40332 & 50220 & 55706 & 55706 & 1 & 2 & 5 & 9\\
+\rowcolor{gray!6}  Medicago\_truncatula.R108 &  & GOMAP & 112343 & 108031 & 382322 & 602696 & 403.32 & 502.20 & 557.06 & 557.06 & 1 & 2 & 5 & 9\\
 
-Oryza\_sativa &  & GOMAP & 72780 & 64685 & 248700 & 386165 & 28619 & 29853 & 35824 & 35825 & 2 & 2 & 6 & 9\\
+ &  & GOMAP & 72780 & 64685 & 248700 & 386165 & 286.19 & 298.53 & 358.24 & 358.25 & 2 & 2 & 6 & 9\\
 
-\rowcolor{gray!6}  Phaseolus\_vulgaris &  & GOMAP & 72005 & 64583 & 229630 & 366218 & 25934 & 25539 & 27432 & 27433 & 2 & 2 & 6 & 11\\
+\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash Oryza\_sativa} &  & GoldStandard & 7730 & 11060 & 19378 & 38176 & 57.25 & 73.83 & 90.31 & 113.87 & 1 & 1 & 1 & 3\\
 
-Triticum\_aestivum &  & GOMAP & 267741 & 218623 & 785960 & 1272324 & 95604 & 98187 & 107890 & 107891 & 2 & 2 & 6 & 10\\
+Phaseolus\_vulgaris &  & GOMAP & 72005 & 64583 & 229630 & 366218 & 259.34 & 255.39 & 274.32 & 274.33 & 2 & 2 & 6 & 11\\
 
-\rowcolor{gray!6}  Vigna\_unguiculata &  & GOMAP & 75867 & 68313 & 243278 & 387458 & 27173 & 27124 & 29772 & 29773 & 2 & 2 & 6 & 11\\
+\rowcolor{gray!6}  Triticum\_aestivum &  & GOMAP & 267741 & 218623 & 785960 & 1272324 & 956.04 & 981.87 & 1078.90 & 1078.91 & 2 & 2 & 6 & 10\\
 
-Zea\_mays.B73.v3 &  & GOMAP & 135211 & 87420 & 291251 & 513882 & 34866 & 38073 & 39468 & 39469 & 3 & 2 & 6 & 11\\
+Vigna\_unguiculata &  & GOMAP & 75867 & 68313 & 243278 & 387458 & 271.73 & 271.24 & 297.72 & 297.73 & 2 & 2 & 6 & 11\\
 
-\rowcolor{gray!6}  Zea\_mays.B73.v4 &  & GOMAP & 88827 & 82251 & 278719 & 449797 & 36717 & 37337 & 39323 & 39324 & 2 & 2 & 6 & 10\\
+\rowcolor{gray!6}  Zea\_mays.B73.v3 &  & GOMAP & 135211 & 87420 & 291251 & 513882 & 348.66 & 380.73 & 394.68 & 394.69 & 3 & 2 & 6 & 11\\
 
-Zea\_mays.Mo17 &  & GOMAP & 87567 & 79214 & 277787 & 444568 & 33618 & 35105 & 38619 & 38620 & 2 & 2 & 6 & 10\\
+Zea\_mays.B73.v4 &  & GOMAP & 88827 & 82251 & 278719 & 449797 & 367.17 & 373.37 & 393.23 & 393.24 & 2 & 2 & 6 & 10\\
 
-\rowcolor{gray!6}  Zea\_mays.PH207 &  & GOMAP & 90617 & 85500 & 288677 & 464794 & 35170 & 36762 & 40556 & 40557 & 2 & 2 & 6 & 10\\
+\rowcolor{gray!6}  Zea\_mays.Mo17 &  & GOMAP & 87567 & 79214 & 277787 & 444568 & 336.18 & 351.05 & 386.19 & 386.20 & 2 & 2 & 6 & 10\\
 
-Zea\_mays.W22 & \multirow{-14}{*}{\raggedleft\arraybackslash 100} & GOMAP & 95390 & 85039 & 289780 & 470209 & 36987 & 37685 & 40689 & 40690 & 2 & 2 & 6 & 10\\
+Zea\_mays.PH207 &  & GOMAP & 90617 & 85500 & 288677 & 464794 & 351.70 & 367.62 & 405.56 & 405.57 & 2 & 2 & 6 & 10\\
+
+\rowcolor{gray!6}  Zea\_mays.W22 & \multirow{-15}{*}{\raggedleft\arraybackslash 100} & GOMAP & 95390 & 85039 & 289780 & 470209 & 369.87 & 376.85 & 406.89 & 406.90 & 2 & 2 & 6 & 10\\
 \bottomrule

### 2019-08-18 text/index.Rmd
Use Frontiers template

@@
 ---
-title: "This is the title"
-author: "The Pickles"
+title: "Article Title"
+runtitle: "Short Title"
+documentclass: frontiersSCNS  # or frontiersHLTH, or frontiersFPHY
+author:
+  - name: First Author
+    affiliation: '1'
+    etal: LASTNAME # First author's last name. 
+  - name: Co-Author
+    affiliation: '2'
+  - name: Co-Author
+    affiliation: '1,3'
+    email: email@uni.edu # Indicates corresponding Author
+    institution: Laboratory X, Institute X, Department X, Organization X
+    street: Street X
+    city: City X
+    state: State XX # only USA, Australia, Canada
+    zip: Zip Code X
+    country: Country X
+affiliation:
+  - id: '1'
+    department: Department X
+    institution: Institution X
+    city: City X
+    state: State XX # only USA, Australia, Canada
+    country: Country X
+  - id: '2' 
+    department: Department X
+    institution: Institution X
+    city: City X
+    state: State XX # only USA, Australia, Canada
+    country: Country X
+  - id: '3' 
+    department: Department X
+    institution: Institution X
+    city: City X
+    state: State XX # only USA, Australia, Canada
+    country: Country X
 date: "Febcember 32nd 3023"
@@
 site: "bookdown::bookdown_site"
+csl: frontiers.csl
+bibliography: test.bib
 output:
@@
     keep_md: true
+    base_format: rticles::frontiers_article
     includes:
@@
         preamble.tex
-documentclass: book
 ---
@@
 
+\begin{abstract}
+
+Abstract length and content varies depending on article type. Refer to 
+\url{http://www.frontiersin.org/about/AuthorGuidelines} for abstract requirement
+and length according to article type.
+
+%All article types: you may provide up to 8 keywords; at least 5 are mandatory.
+\tiny
+ \keyFont{ \section{Keywords:} Text Text Text Text Text Text Text Text }
+
+\end{abstract}
+
 # Introduction

### 2019-08-20 Rakefile.rb
Started writing unit tests for analyses

@@ -56,3 +56,8 @@ desc 'Quantity analysis'
 file 'analyses/quantity/results/quantity_table.csv' => cleanup_targets + ['data/n_genes_per_genome.csv', 'analyses/quantity/quantity.R'] do
   sh "Rscript analyses/quantity/quantity.R"
 end
+
+desc 'Run unit tests for analyses code'
+task :test do
+  sh 'crystal spec'
+end

### 2019-08-22 Rakefile.rb
Cleanup: Keep all columns and headers so that the files are compatible with ads

@@ -31,7 +31,7 @@ cleanup_targets = ['analyses/cleanup/results/cleanup_table.csv']
 ## For each raw dataset there should be an up-to-date cleaned one
 FileList.new("data/go_annotation_sets/*/*.gaf.gz").to_a.each do |f|
   # Corresponding cleaned up file:
-  target = "analyses/cleanup/results/" + ((f.split(".")[0..-3] + ["mgaf.gz"]).join(".").split("/")[2..-1]).join("/")
+  target = "analyses/cleanup/results/" + ((f.split(".")[0..-3] + ["gaf.gz"]).join(".").split("/")[2..-1]).join("/")
   # The cleaned up file depends on its source file, the cleanup executable and the go_files
   file target => [f, 'analyses/cleanup/cleanup'] + go_files do
     sh "analyses/cleanup/cleanup #{f}"
@@ -44,7 +44,7 @@ FileList.new("data/go_annotation_sets/*/*.gaf.gz").to_a.each do |f|
 end
 
 ## If there are any cleaned up files that do not have a source file anymore, remove them
-(FileList.new("analyses/cleanup/results/*/*.mgaf.gz").to_a - cleanup_targets).each do |f|
+(FileList.new("analyses/cleanup/results/*/*.gaf.gz").to_a - cleanup_targets).each do |f|
     sh "analyses/cleanup/cleanup --delete #{f}"
 end
 

### 2019-08-22 analyses/quantity/quantity.R

@@ -8,7 +8,7 @@ possibly_read_gaf <- function(gaf_file) {
   if(is.data.frame(gaf_file))
     return(gaf_file)
   if(is.character(gaf_file))
-    return(read.csv(gaf_file, header=T, sep="\t"))
+    return(read.csv(gaf_file, header=T, skip=1, sep="\t"))
   # If neither dataframe nor string: something is wrong:
   stop("Passed argument is neither data frame nor path to GAF file!")
 }
@@ -73,7 +73,7 @@ genomes = list.dirs("analyses/cleanup/results", recursive = F)
 for(genome_path in genomes) {
   genome_name = basename(genome_path)
   print(genome_name)
-  for(gaf_file in list.files(genome_path, pattern = ".mgaf", full.names = T)) {
+  for(gaf_file in list.files(genome_path, pattern = ".gaf", full.names = T)) {
     print(gaf_file)
     gaf_df = possibly_read_gaf(gaf_file)
     aspect_counts = count_aspects(gaf_df)

### 2019-08-22 text/03-results.Rmd
Add quality evaluation step

@@
 ```
+
+```{r quality-table}
+dt2 <- read.csv("../analyses/quality/quality_table.csv", header=T)
+kable(dt2, booktabs=TRUE, caption = "Quality evaluation of the used GO annotation sets.", col.names=c("Genome", "Dataset", "SimGIC2 score")) %>%
+ kable_styling(latex_options = c("striped")) %>%
+ collapse_rows(columns = 1, latex_hline="major")
+```

### 2019-08-22 Rakefile.rb

@@ -1,7 +1,9 @@
+require "csv"
+
 task :default => 'Paper.pdf'
 
 desc 'Typeset the Paper'
-file 'Paper.pdf' => ['analyses/quantity/results/quantity_table.csv'] + FileList.new("text/*") do
+file 'Paper.pdf' => ['analyses/quantity/results/quantity_table.csv', 'analyses/quality/quality_table.csv'] + FileList.new("text/*") do
   sh %q(R -e 'library("bookdown"); xfun::in_dir("text", render_book("index.Rmd", output_file="../../Paper.pdf", clean=T))')
 end
 
@@ -61,3 +63,56 @@ desc 'Run unit tests for analyses code'
 task :test do
   sh 'crystal spec'
 end
+
+# Quality Evaluation
+## For each Gold Standard there should be an ADS equivalent
+quality_targets = []
+FileList.new("analyses/cleanup/results/*/GoldStandard.gaf.gz").to_a.each do |f|
+  genome = File.basename(File.dirname(f))
+  # We're taking the corresponding ic.tab file as a representative for all files created by ADS
+  file "analyses/quality/#{genome}/ic.tab" => f do
+    Dir.chdir("analyses/quality/ads/") do # ADS requires to be run from the ads directory
+      sh "gunzip -k ../../cleanup/results/#{genome}/GoldStandard.gaf.gz"
+      sh "gunzip -k ../../cleanup/go.obo.gz"
+      rm_f "../#{genome}/ic.* ../#{genome}/goparents.tab" # Remove old files to start from a clean slate
+      sh "perl pipeline.pl --datadir ../#{genome}/ --obo ../../cleanup/go.obo --goa ../../cleanup/results/#{genome}/GoldStandard.gaf --pipev 1,2"
+      sh "tail -n+3 ../../cleanup/results/#{genome}/GoldStandard.gaf | cut -f2,5 > ../#{genome}/GoldStandard.tsv"
+      rm "../../cleanup/results/#{genome}/GoldStandard.gaf"
+      rm "../../cleanup/go.obo"
+    end
+  end
+
+  # For each of the genomes where a Gold Standard is present, all other datasets should also be evaluated
+  FileList.new("analyses/cleanup/results/#{genome}/*.gaf.gz").to_a.each do |ds|
+    dataset = File.basename(ds).split(".").first
+    target = "analyses/quality/#{genome}/#{dataset}.SimGIC2"
[…]

### 2019-08-24 Paper.tex
Add quality evaluation step
Make tables conform to conventions

@@
 \midrule
-\rowcolor{gray!6}  Triticum\_aestivum & GOMAP & 285 & 0\\
+\rowcolor{gray!6}  \textit{Glycine max} & GOMAP & 203 & 0\\
 \cmidrule{1-4}
-Hordeum\_vulgarum & GOMAP & 101 & 0\\
+\textit{Hordeum vulgarum} & GOMAP & 101 & 0\\
 \cmidrule{1-4}
-\rowcolor{gray!6}  Glycine\_max & GOMAP & 203 & 0\\
+\rowcolor{gray!6}  \textit{Medicago truncatula} A17 & GOMAP & 0 & 0\\
 \cmidrule{1-4}
-Arachis\_hypogaea & GOMAP & 0 & 0\\
+\textit{Medicago truncatula} R108 & GOMAP & 0 & 0\\
 \cmidrule{1-4}
-\rowcolor{gray!6}  Zea\_mays.PH207 & GOMAP & 798 & 76\\
+\rowcolor{gray!6}   & GOMAP & 111 & 2\\
+
+\multirow{-2}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & GoldStandard & 38 & 556\\
 \cmidrule{1-4}
-Zea\_mays.Mo17 & GOMAP & 726 & 77\\
+\rowcolor{gray!6}  \textit{Phaseolus vulgaris} & GOMAP & 0 & 0\\
 \cmidrule{1-4}
-\rowcolor{gray!6}  Phaseolus\_vulgaris & GOMAP & 0 & 0\\
+\textit{Triticum aestivum} & GOMAP & 285 & 0\\
 \cmidrule{1-4}
-Vigna\_unguiculata & GOMAP & 0 & 0\\
+\rowcolor{gray!6}  \textit{Vigna unguiculata} & GOMAP & 0 & 0\\
 \cmidrule{1-4}
-\rowcolor{gray!6}  Medicago\_truncatula.R108 & GOMAP & 0 & 0\\
+\textit{Zea mays} B73.v4 & GOMAP & 752 & 83\\
 \cmidrule{1-4}
-Zea\_mays.B73.v3 & GOMAP & 1107 & 70\\
+\rowcolor{gray!6}  \textit{Zea mays} Mo17 & GOMAP & 726 & 77\\
 \cmidrule{1-4}
-\rowcolor{gray!6}  Zea\_mays.W22 & GOMAP & 754 & 82\\
+\textit{Zea mays} PH207 & GOMAP & 798 & 76\\
 \cmidrule{1-4}
-Medicago\_truncatula.A17 & GOMAP & 0 & 0\\
+\rowcolor{gray!6}  \textit{Zea mays} W22 & GOMAP & 754 & 82\\
 \cmidrule{1-4}
-\rowcolor{gray!6}  Zea\_mays.B73.v4 & GOMAP & 752 & 83\\
+\textit{Arachis hypogaea} & GOMAP & 0 & 0\\
 \cmidrule{1-4}
- & GoldStandard & 38 & 556\\
+\rowcolor{gray!6}   & GOMAP & 1107 & 70\\
 
-\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash Oryza\_sativa} & GOMAP & 111 & 2\\
+ & GoldStandard & 1 & 0\\
+
+\rowcolor{gray!6}   & Gramene49 & 94 & 2\\
+
+\multirow{-4}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} & Phytozome & 54 & 0\\
+\cmidrule{1-4}
+\rowcolor{gray!6}   & Gramene61-IEA & 10 & 14\\
+
+\multirow{-2}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & Gramene61-all & 48 & 9565\\
 \bottomrule
@@
 \caption{\label{tab:annotation-quantities}Quantitative metrics of the cleaned functional annotation sets.
-C, F, P, and A refer to the aspects of the GO: Cellular Component, Biological Function, Molecular Process, and Any/All.}
+CC, BF, MP, and A refer to the aspects of the GO: Cellular Component, Biological Function, Molecular Process, and Any/All.}
 \centering
@@
 \cmidrule(l{3pt}r{3pt}){4-7} \cmidrule(l{3pt}r{3pt}){8-11} \cmidrule(l{3pt}r{3pt}){12-15}
-Genome & Genes & Dataset & C & F & P & A & C & F & P & A & C & F & P & A\\
+Genome & Genes & Dataset & CC & BF & MP & A & CC & BF & MP & A & CC & BF & MP & A\\
 \midrule
-\rowcolor{gray!6}  Arachis\_hypogaea &  & GOMAP & 153433 & 132944 & 493799 & 780176 & 576.67 & 568.55 & 671.23 & 671.24 & 2 & 2 & 6 & 10\\
+\rowcolor{gray!6}  \textit{Arachis hypogaea} &  & GOMAP & 153433 & 132944 & 493799 & 780176 & 57667 & 56855 & 67123 & 67124 & 2 & 2 & 6 & 10\\
 
-Glycine\_max &  & GOMAP & 129215 & 113827 & 417555 & 660597 & 460.20 & 470.34 & 528.71 & 528.72 & 2 & 2 & 6 & 11\\
+\textit{Glycine max} &  & GOMAP & 129215 & 113827 & 417555 & 660597 & 46020 & 47034 & 52871 & 52872 & 2 & 2 & 6 & 11\\
 
-\rowcolor{gray!6}  Hordeum\_vulgarum &  & GOMAP & 88130 & 80282 & 272823 & 441235 & 352.37 & 364.70 & 397.33 & 397.34 & 2 & 2 & 5 & 10\\
+\rowcolor{gray!6}  \textit{Hordeum vulgarum} &  & GOMAP & 88130 & 80282 & 272823 & 441235 & 35237 & 36470 & 39733 & 39734 & 2 & 2 & 5 & 10\\
 
-Medicago\_truncatula.A17 &  & GOMAP & 107362 & 99719 & 364065 & 571146 & 423.25 & 437.36 & 504.43 & 504.44 & 2 & 2 & 6 & 10\\
+\textit{Medicago truncatula} A17 &  & GOMAP & 107362 & 99719 & 364065 & 571146 & 42325 & 43736 & 50443 & 50444 & 2 & 2 & 6 & 10\\
 
-\rowcolor{gray!6}  Medicago\_truncatula.R108 &  & GOMAP & 112343 & 108031 & 382322 & 602696 & 403.32 & 502.20 & 557.06 & 557.06 & 1 & 2 & 5 & 9\\
+\rowcolor{gray!6}  \textit{Medicago truncatula} R108 &  & GOMAP & 112343 & 108031 & 382322 & 602696 & 40332 & 50220 & 55706 & 55706 & 1 & 2 & 5 & 9\\
 
- &  & GOMAP & 72780 & 64685 & 248700 & 386165 & 286.19 & 298.53 & 358.24 & 358.25 & 2 & 2 & 6 & 9\\
+ &  & GOMAP & 72780 & 64685 & 248700 & 386165 & 28619 & 29853 & 35824 & 35825 & 2 & 2 & 6 & 9\\
 
-\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash Oryza\_sativa} &  & GoldStandard & 7730 & 11060 & 19378 & 38176 & 57.25 & 73.83 & 90.31 & 113.87 & 1 & 1 & 1 & 3\\
+\rowcolor{gray!6}   &  & GoldStandard & 7730 & 11060 & 19378 & 38176 & 5725 & 7383 & 9031 & 11387 & 1 & 1 & 1 & 3\\
 
-Phaseolus\_vulgaris &  & GOMAP & 72005 & 64583 & 229630 & 366218 & 259.34 & 255.39 & 274.32 & 274.33 & 2 & 2 & 6 & 11\\
+ &  & Gramene61-IEA & 14633 & 32787 & 39105 & 86529 & 10771 & 15537 & 16705 & 21446 & 1 & 1 & 1 & 3\\
 
-\rowcolor{gray!6}  Triticum\_aestivum &  & GOMAP & 267741 & 218623 & 785960 & 1272324 & 956.04 & 981.87 & 1078.90 & 1078.91 & 2 & 2 & 6 & 10\\
+\rowcolor{gray!6}  \multirow{-4}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} &  & Gramene61-all & 20622 & 40674 & 54402 & 115710 & 13272 & 16962 & 18513 & 22272 & 1 & 1 & 2 & 4\\
 
-Vigna\_unguiculata &  & GOMAP & 75867 & 68313 & 243278 & 387458 & 271.73 & 271.24 & 297.72 & 297.73 & 2 & 2 & 6 & 11\\
+\textit{Phaseolus vulgaris} &  & GOMAP & 72005 & 64583 & 229630 & 366218 & 25934 & 25539 & 27432 & 27433 & 2 & 2 & 6 & 11\\
 
-\rowcolor{gray!6}  Zea\_mays.B73.v3 &  & GOMAP & 135211 & 87420 & 291251 & 513882 & 348.66 & 380.73 & 394.68 & 394.69 & 3 & 2 & 6 & 11\\
+\rowcolor{gray!6}  \textit{Triticum aestivum} &  & GOMAP & 267741 & 218623 & 785960 & 1272324 & 95604 & 98187 & 107890 & 107891 & 2 & 2 & 6 & 10\\
 
-Zea\_mays.B73.v4 &  & GOMAP & 88827 & 82251 & 278719 & 449797 & 367.17 & 373.37 & 393.23 & 393.24 & 2 & 2 & 6 & 10\\
+\textit{Vigna unguiculata} &  & GOMAP & 75867 & 68313 & 243278 & 387458 & 27173 & 27124 & 29772 & 29773 & 2 & 2 & 6 & 11\\
 
-\rowcolor{gray!6}  Zea\_mays.Mo17 &  & GOMAP & 87567 & 79214 & 277787 & 444568 & 336.18 & 351.05 & 386.19 & 386.20 & 2 & 2 & 6 & 10\\
+\rowcolor{gray!6}   &  & GOMAP & 135211 & 87420 & 291251 & 513882 & 34866 & 38073 & 39468 & 39469 & 3 & 2 & 6 & 11\\
 
-Zea\_mays.PH207 &  & GOMAP & 90617 & 85500 & 288677 & 464794 & 351.70 & 367.62 & 405.56 & 405.57 & 2 & 2 & 6 & 10\\
+ &  & GoldStandard & 1565 & 65 & 299 & 1929 & 1548 & 60 & 151 & 1634 & 1 & 0 & 0 & 1\\
 
-\rowcolor{gray!6}  Zea\_mays.W22 & \multirow{-15}{*}{\raggedleft\arraybackslash 100} & GOMAP & 95390 & 85039 & 289780 & 470209 & 369.87 & 376.85 & 406.89 & 406.90 & 2 & 2 & 6 & 10\\
+\rowcolor{gray!6}   &  & Gramene49 & 20072 & 31056 & 30089 & 81217 & 11834 & 17991 & 15800 & 21926 & 1 & 1 & 1 & 3\\
+
+\multirow{-4}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} &  & Phytozome & 4787 & 19044 & 13100 & 36931 & 4524 & 13728 & 11365 & 16132 & 0 & 1 & 1 & 2\\
+
+\rowcolor{gray!6}  \textit{Zea mays} B73.v4 &  & GOMAP & 88827 & 82251 & 278719 & 449797 & 36717 & 37337 & 39323 & 39324 & 2 & 2 & 6 & 10\\
+
+\textit{Zea mays} Mo17 &  & GOMAP & 87567 & 79214 & 277787 & 444568 & 33618 & 35105 & 38619 & 38620 & 2 & 2 & 6 & 10\\
+
+\rowcolor{gray!6}  \textit{Zea mays} PH207 &  & GOMAP & 90617 & 85500 & 288677 & 464794 & 35170 & 36762 & 40556 & 40557 & 2 & 2 & 6 & 10\\
+
+\textit{Zea mays} W22 & \multirow{-20}{*}{\raggedleft\arraybackslash 100} & GOMAP & 95390 & 85039 & 289780 & 470209 & 36987 & 37685 & 40689 & 40690 & 2 & 2 & 6 & 10\\
 \bottomrule
@@
 \begin{tablenotes}
-\item[a] How many annotations in the C, F, and P aspect does this dataset contain? A = How many in total? $A = C + F + P$
-\item[b] How many genes in the genome have at least one GO term from the C, F, P aspect annotated to them? A = How many at least one from any aspect? ($A = C \cup F \cup P$)
-\item[c] Take a typical gene that is present in the annotation set. How many annotations does it have in each aspect? A = How many in total? Ask your favorite statistician why $A \neq C + F +P$
+\item[a] How many annotations in the CC, BF, and MP aspect does this dataset contain? A = How many in total? $\textrm{A} = \textrm{CC} + \textrm{BF} + \textrm{MP}$
+\item[b] How many genes in the genome have at least one GO term from the CC, BF, MP aspect annotated to them?
+A = How many at least one from any aspect?
+($\textrm{A} = \textrm{CC} \cup \textrm{BF} \cup \textrm{MP}$)
+\item[c] Take a typical gene that is present in the annotation set.
+How many annotations does it have in each aspect?
+A = How many in total?
+Ask your favorite statistician why $\textrm{A} \neq \textrm{CC} + \textrm{BF} +\textrm{MP}$
 \end{tablenotes}
@@
 
+\begin{table}[t]
+
+\caption{\label{tab:quality-table}Quality evaluation of the used GO annotation sets.}
+\centering
+\begin{tabular}{llr}
+\toprule
+Genome & Dataset & SimGIC2 score\\
+\midrule
+\rowcolor{gray!6}   & GOMAP & 0.248394\\
+
+ & GoldStandard & 0.999974\\
+
+\rowcolor{gray!6}   & Gramene61-IEA & 0.319345\\
+
+\multirow{-4}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & Gramene61-all & 0.732175\\
+\cmidrule{1-3}
+\rowcolor{gray!6}   & GOMAP & 0.024565\\
+
+ & GoldStandard & 0.996264\\
+
+\rowcolor{gray!6}   & Gramene49 & 0.043521\\
+
+\multirow{-4}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} & Phytozome & 0.021982\\
+\bottomrule
+\end{tabular}
+\end{table}
+
 \end{document}

### 2019-08-24 text/03-results.Rmd
Make tables conform to conventions

--- 2019-08-14 text/03-results.Rmd
@@
 ```{r cleanup-table}
-dt2 <- read.csv("../analyses/cleanup/results/cleanup_table.csv", header=T)
-kable(dt2, booktabs=TRUE, caption = "Number of removed annotations during cleanup.", col.names=c("Genome", "Dataset", "Obsolete Annotations", "Duplicates")) %>%
+dt2 <- read.csv("../analyses/cleanup/results/cleanup_table.csv", header=F, stringsAsFactors=F)
+dt2$V1 = format_genome(dt2$V1)
+kable(dt2, booktabs=TRUE, escape=F, caption = "Number of removed annotations during cleanup.", col.names=c("Genome", "Dataset", "Obsolete Annotations", "Duplicates")) %>%
  kable_styling(latex_options = c("striped")) %>%
@@
 ```{r annotation-quantities}
-dt2 <- read.csv("../analyses/quantity/results/quantity_table.csv", header=T)
+dt2 <- read.csv("../analyses/quantity/results/quantity_table.csv", header=T, stringsAsFactors=F)
+# Format the genome names according to conventions
+dt2$genome = format_genome(dt2$genome)
 # Drop the absolute 'genes annotated' counts, we only want the percentual ones
@@
   paste0("Median Ann. per G.", footnote_marker_alphabet(3, double_escape=T)))
-kable(dt2, booktabs=T, caption = "Quantitative metrics of the cleaned functional annotation sets.
-C, F, P, and A refer to the aspects of the GO: Cellular Component, Biological Function, Molecular Process, and Any/All.", col.names=c("Genome", "Genes", "Dataset", "C", "F", "P", "A","C", "F", "P", "A","C", "F", "P", "A")) %>%
+kable(dt2, booktabs=T, escape=F, caption = "Quantitative metrics of the cleaned functional annotation sets.
+CC, BF, MP, and A refer to the aspects of the GO: Cellular Component, Biological Function, Molecular Process, and Any/All.", col.names=c("Genome", "Genes", "Dataset", "CC", "BF", "MP", "A","CC", "BF", "MP", "A","CC", "BF", "MP", "A")) %>%
   kable_styling(latex_options = c("striped", "scale_down")) %>%
@@
   footnote(alphabet=c(
-    "How many annotations in the C, F, and P aspect does this dataset contain? A = How many in total? $A = C + F + P$",
-    "How many genes in the genome have at least one GO term from the C, F, P aspect annotated to them? A = How many at least one from any aspect? ($A = C \\\\cup F \\\\cup P$)",
-    "Take a typical gene that is present in the annotation set. How many annotations does it have in each aspect? A = How many in total? Ask your favorite statistician why $A \\\\neq C + F +P$"
+    "How many annotations in the CC, BF, and MP aspect does this dataset contain? A = How many in total? $\\\\textrm{A} = \\\\textrm{CC} + \\\\textrm{BF} + \\\\textrm{MP}$",
+    "How many genes in the genome have at least one GO term from the CC, BF, MP aspect annotated to them?
+A = How many at least one from any aspect?
+($\\\\textrm{A} = \\\\textrm{CC} \\\\cup \\\\textrm{BF} \\\\cup \\\\textrm{MP}$)",
+    "Take a typical gene that is present in the annotation set.
+How many annotations does it have in each aspect?
+A = How many in total?
+Ask your favorite statistician why $\\\\textrm{A} \\\\neq \\\\textrm{CC} + \\\\textrm{BF} +\\\\textrm{MP}$"
   ), threeparttable=T, escape=F)
 ```
+
+```{r quality-table}
+dt2 <- read.csv("../analyses/quality/quality_table.csv", header=T, stringsAsFactors=F)
+dt2$genome = format_genome(dt2$genome)
+kable(dt2, booktabs=TRUE, escape=F, caption = "Quality evaluation of the used GO annotation sets.", col.names=c("Genome", "Dataset", "SimGIC2 score")) %>%
+ kable_styling(latex_options = c("striped")) %>%
+ collapse_rows(columns = 1, latex_hline="major")
+```

### 2019-08-24 Rakefile.rb

@@ -4,6 +4,7 @@ task :default => 'Paper.pdf'
 
 desc 'Typeset the Paper'
 file 'Paper.pdf' => ['analyses/quantity/results/quantity_table.csv', 'analyses/quality/quality_table.csv'] + FileList.new("text/*") do
+  rm_f 'text/_main.Rmd'
   sh %q(R -e 'library("bookdown"); xfun::in_dir("text", render_book("index.Rmd", output_file="../../Paper.pdf", clean=T))')
 end
 

### 2019-08-24 analyses/quantity/quantity.R

@@ -92,10 +92,10 @@ for(genome_path in genomes) {
       genes_annotated_f = genes_annotated[["F"]],
       genes_annotated_p = genes_annotated[["P"]],
       genes_annotated_a = genes_annotated[["A"]],
-      p_genes_annotated_c = genes_annotated[["C"]]/n_genes_per_genome[n_genes_per_genome$genome == genome_name,"n_genes"],
-      p_genes_annotated_f = genes_annotated[["F"]]/n_genes_per_genome[n_genes_per_genome$genome == genome_name,"n_genes"],
-      p_genes_annotated_p = genes_annotated[["P"]]/n_genes_per_genome[n_genes_per_genome$genome == genome_name,"n_genes"],
-      p_genes_annotated_a = genes_annotated[["A"]]/n_genes_per_genome[n_genes_per_genome$genome == genome_name,"n_genes"],
+      p_genes_annotated_c = genes_annotated[["C"]]/n_genes_per_genome[n_genes_per_genome$genome == genome_name,"n_genes"]*100,
+      p_genes_annotated_f = genes_annotated[["F"]]/n_genes_per_genome[n_genes_per_genome$genome == genome_name,"n_genes"]*100,
+      p_genes_annotated_p = genes_annotated[["P"]]/n_genes_per_genome[n_genes_per_genome$genome == genome_name,"n_genes"]*100,
+      p_genes_annotated_a = genes_annotated[["A"]]/n_genes_per_genome[n_genes_per_genome$genome == genome_name,"n_genes"]*100,
       median_annotations_per_gene_c = medians[["C"]],
       median_annotations_per_gene_f = medians[["F"]],
       median_annotations_per_gene_p = medians[["P"]],

### 2019-08-25 text/index.Rmd
Make tables conform to conventions
Set up proper citations

--- 2019-08-14 text/index.Rmd
@@
 site: "bookdown::bookdown_site"
+csl: frontiers.csl
+bibliography: test.bib
+link-citations: true
 output:
@@
     keep_md: true
+    base_format: rticles::frontiers_article
+    citation_package: natbib
     includes:
@@
 
+```{r helper-functions}
+format_genome <- function(genomes) {
+  return(unlist(lapply(strsplit(genomes, "\\."), function(x) { 
+    if(length(x) > 1) {
+      paste0("\\textit{",gsub("_", " ",x[1]),"} ", paste(x[2:length(x)], collapse="."))
+    } else {
+      paste0("\\textit{",gsub("_", " ",x[1]),"} ")
+    }
+  }))
+  )
+}
+```
+
+\begin{abstract}
+
+Abstract length and content varies depending on article type. Refer to 
+\url{http://www.frontiersin.org/about/AuthorGuidelines} for abstract requirement
+and length according to article type.
+
+%All article types: you may provide up to 8 keywords; at least 5 are mandatory.
+\tiny
+ \keyFont{ \section{Keywords:} Text Text Text Text Text Text Text Text }
+
+\end{abstract}
+
 # Introduction

### 2019-08-25 text/02-methods.Rmd
Wrote short intro about choosing quality metric

@@
 All further analyses were performed on the cleaned datasets since we assume the user will only be interested in still valid and non-redundant functional annotations.
+
+## Choosing the right evaluation metric
+A plethora of different metric to evaluate the quality of functional annotation predictions is available using different approaches and there seems to be no clear standard yet. `TODO: THIS IS WEAK`
+Additionally, each of the metrics has a different focus and lalala so choosing a metric for quality evaluation is not trivial.
+When we first published GOMAP [@Wimalanathan2018], we used a modified version of the hierarchical evaluation metrics originally introduced in [@Verspoor2006] because they were simple, clear, and part of an earlier attempt at unifying and standardizing GO annotation comparisons [@Defoin-Platel2011].
+In the meantime, @Plyusnin2018 have published an approach for evaluating different metrics showing substantial differences within the robustness of different approaches.
+`TODO DESCRIBE THEIR APPROACH`
+We have applied their method on the Gold Standards available to us to determine which evaluation metric is the most appropriate in our case.
+The results of this analysis can be seen in `TODO`.
+
+We then evaluated our predictions and the other annotation sets using the best performing metrics as well as the one we previously used.
+`TODO`

### 2019-08-25 text/index.Rmd
Wrote short intro about choosing quality metric

@@
 csl: frontiers.csl
-bibliography: test.bib
 link-citations: true

### 2019-08-30 Paper.tex
Set up proper citations
List of Authors (preliminary)

@@
 \def\Authors{
-  First Author\,\textsuperscript{1},
-  Co-Author\,\textsuperscript{2},
-  Co-Author\,\textsuperscript{1,3*}}
+  Dennis Psaroudakis\,\textsuperscript{1},
+  Ha Vu\,\textsuperscript{1},
+  Colleen Yanarella\,\textsuperscript{1},
+  Steven Cannon\,\textsuperscript{1},
+  Darwin Campbell\,\textsuperscript{1},
+  Parnal Joshi\,\textsuperscript{1},
+  Iddo Friedberg\,\textsuperscript{1,4},
+  Kokulapalan Wimalanathan\,\textsuperscript{1,2},
+  Carolyn J. Lawrence-Dill\,\textsuperscript{1,2,3*}}
 
@@
 
-  \textsuperscript{1} Department X, Institution X,  City X,  State XX,  Country X
+  \textsuperscript{1} Bioinformatics and Computational Biology, Iowa State University,  Ames,  IA,  USA
 
-  \textsuperscript{2} Department X, Institution X,  City X,  State XX,  Country X
+  \textsuperscript{2} Department of Genetics, Development, and Cell Biology, Iowa State University,  Ames,  IA,  USA
 
-  \textsuperscript{3} Department X, Institution X,  City X,  State XX,  Country X
+  \textsuperscript{3} Department of Agronomy, Iowa State University,  Ames,  IA,  USA
+
+  \textsuperscript{4} Department of Veterinary Microbiology, Iowa State University,  Ames,  IA,  USA
   }
 
-  \def\firstAuthorLast{LASTNAME {et~al.}}
+  \def\firstAuthorLast{Psaroudakis {et~al.}}
 
-  \def\corrAuthor{Co-Author}\def\corrAddress{Laboratory X, Institute X, Department X, Organization X\\Street X\\City X, State XX, Zip Code X Country X}\def\corrEmail{\href{mailto:email@uni.edu}{\nolinkurl{email@uni.edu}}}
+  \def\corrAuthor{Carolyn J.
+Lawrence-Dill}\def\corrAddress{Roy J.
+Carver Co-Lab, Iowa State University\\1111 WOI Rd\\Ames, State IA, 50011 USA}\def\corrEmail{\href{mailto:triffid@iastate.edu}{\nolinkurl{triffid@iastate.edu}}}
 
@@
 All further analyses were performed on the cleaned datasets since we assume the user will only be interested in still valid and non-redundant functional annotations.
+
+\hypertarget{choosing-the-right-evaluation-metric}{%
+\subsection{Choosing the right evaluation metric}\label{choosing-the-right-evaluation-metric}}
+
+A plethora of different metric to evaluate the quality of functional annotation predictions is available using different approaches and there seems to be no clear standard yet.
+\texttt{TODO:\ THIS\ IS\ WEAK}
+Additionally, each of the metrics has a different focus and lalala so choosing a metric for quality evaluation is not trivial.
+When we first published GOMAP \citep{Wimalanathan2018}, we used a modified version of the hierarchical evaluation metrics originally introduced in \citep{Verspoor2006} because they were simple, clear, and part of an earlier attempt at unifying and standardizing GO annotation comparisons \citep{Defoin-Platel2011}.
+In the meantime, \citet{Plyusnin2018} have published an approach for evaluating different metrics showing substantial differences within the robustness of different approaches.
+\texttt{TODO\ DESCRIBE\ THEIR\ APPROACH}
+We have applied their method on the Gold Standards available to us to determine which evaluation metric is the most appropriate in our case.
+The results of this analysis can be seen in \texttt{TODO}.
+
+We then evaluated our predictions and the other annotation sets using the best performing metrics as well as the one we previously used.
+\texttt{TODO}
 
@@
 
+\hypertarget{quality-evaluation}{%
+\subsection{Quality Evaluation}\label{quality-evaluation}}
+
+\texttt{TODO} If it turns out that our predictions are good with hF but bad with more approriate metrics, explanation would be that score thresholds for the prediction tools used in the GOMAP pipeline have been chosen to maximize this hF value.
+It now seems reasonable to re-adjust these thresholds to maximize a different metric which will likely result in a drop in hF score but increase in other metrics.
+Again emphasizes the importance of choosing the right evaluation metric.
+
 \begin{table}[t]
@@
 \midrule
-\rowcolor{gray!6}   & GOMAP & 0.248394\\
+\rowcolor{gray!6}   & GOMAP & 0.241470\\
 
- & GoldStandard & 0.999974\\
+ & GoldStandard & 0.999971\\
 
-\rowcolor{gray!6}   & Gramene61-IEA & 0.319345\\
+\rowcolor{gray!6}   & Gramene61-IEA & 0.324831\\
 
-\multirow{-4}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & Gramene61-all & 0.732175\\
+\multirow{-4}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & Gramene61-all & 0.732289\\
 \cmidrule{1-3}
-\rowcolor{gray!6}   & GOMAP & 0.024565\\
+\rowcolor{gray!6}   & GOMAP & 0.072971\\
 
- & GoldStandard & 0.996264\\
+ & GoldStandard & 0.998562\\
 
-\rowcolor{gray!6}   & Gramene49 & 0.043521\\
+\rowcolor{gray!6}   & Gramene49 & 0.126450\\
 
-\multirow{-4}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} & Phytozome & 0.021982\\
+\multirow{-4}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} & Phytozome & 0.032693\\
 \bottomrule
@@
 
+\bibliography{GOMAP-Paper-Used}
+
 \end{document}

### 2019-08-30 text/03-results.Rmd
Set up proper citations
List of Authors (preliminary)

@@
 
+## Quality Evaluation
+
+`TODO` If it turns out that our predictions are good with hF but bad with more approriate metrics, explanation would be that score thresholds for the prediction tools used in the GOMAP pipeline have been chosen to maximize this hF value.
+It now seems reasonable to re-adjust these thresholds to maximize a different metric which will likely result in a drop in hF score but increase in other metrics.
+Again emphasizes the importance of choosing the right evaluation metric.
+
 ```{r quality-table}

### 2019-08-30 text/index.Rmd
List of Authors (preliminary)

@@
 author:
-  - name: First Author
+  - name: Dennis Psaroudakis
     affiliation: '1'
-    etal: LASTNAME # First author's last name. 
-  - name: Co-Author
-    affiliation: '2'
-  - name: Co-Author
-    affiliation: '1,3'
-    email: email@uni.edu # Indicates corresponding Author
-    institution: Laboratory X, Institute X, Department X, Organization X
-    street: Street X
-    city: City X
-    state: State XX # only USA, Australia, Canada
-    zip: Zip Code X
-    country: Country X
+    etal: Psaroudakis # First author's last name. 
+  - name: Ha Vu
+    affiliation: '1'
+  - name: Colleen Yanarella
+    affiliation: '1'
+  - name: Steven Cannon
+    affiliation: '1'
+  - name: Darwin Campbell
+    affiliation: '1'
+  - name: Parnal Joshi
+    affiliation: '1'
+  - name: Iddo Friedberg
+    affiliation: '1,4'
+  - name: Kokulapalan Wimalanathan
+    affiliation: '1,2'
+  - name: Carolyn J. Lawrence-Dill
+    affiliation: '1,2,3'
+    email: triffid@iastate.edu
+    institution: Roy J. Carver Co-Lab, Iowa State University
+    street: 1111 WOI Rd
+    city: Ames
+    state: State IA # only USA, Australia, Canada
+    zip: 50011
+    country: USA
 affiliation:
   - id: '1'
-    department: Department X
-    institution: Institution X
-    city: City X
-    state: State XX # only USA, Australia, Canada
-    country: Country X
+    department: Bioinformatics and Computational Biology
+    institution: Iowa State University
+    city: Ames
+    state: IA # only USA, Australia, Canada
+    country: USA
   - id: '2'
-    department: Department X
-    institution: Institution X
-    city: City X
-    state: State XX # only USA, Australia, Canada
-    country: Country X
+    department: Department of Genetics, Development, and Cell Biology
+    institution: Iowa State University
+    city: Ames
+    state: IA # only USA, Australia, Canada
+    country: USA
   - id: '3'
-    department: Department X
-    institution: Institution X
-    city: City X
-    state: State XX # only USA, Australia, Canada
-    country: Country X
+    department: Department of Agronomy
+    institution: Iowa State University
+    city: Ames
+    state: IA # only USA, Australia, Canada
+    country: USA
+  - id: '4'
+    department: Department of Veterinary Microbiology
+    institution: Iowa State University
+    city: Ames
+    state: IA # only USA, Australia, Canada
+    country: USA
 date: "Febcember 32nd 3023"

### 2019-09-20 data/go_annotation_sets/Oryza_sativa/transformGoldStandard2GAF.sh
Added Gramene61-IEA annotations for Rice

@@ -1,32 +1,0 @@
-# This file converts the GoldStandard TSV file downloaded from Gramene to the GAF 2 format
-# so that we don't need to deal with different file formats in the following analyses.
-
-# Print GAF headers
-echo "!gaf-version:2.0" > GoldStandard.gaf
-echo "!db	db_object_id	db_object_symbol	qualifier	term_accession	db_reference	evidence_code	with	aspect	db_object_name	db_object_synonym	db_object_type	taxon	date	assigned_by	annotation_extension	gene_product_form_id" >> GoldStandard.gaf
-
-# Skip TSV header and rearrange/expand columns
-tail -n +2 GoldStandard.tsv | awk -F $'\t' 'BEGIN {OFS = FS} 
- { print "Gramene/Plant_Genes_61/IRGSP-1.0", 
-   $1, 
-   $1,
-   "",
-   $2, 
-   "", 
-   $4,
-   "",
-   $3,
-   "",
-   "",
-   "protein",
-   "taxon:4530",
-   "",
-   "",
-   "",
-   ""
- }' >> GoldStandard.gaf
-
-# Rename aspect names of the TSV to GAF codes
-sed -i 's/cellular_component/C/' GoldStandard.gaf
-sed -i 's/biological_process/P/' GoldStandard.gaf
-sed -i 's/molecular_function/F/' GoldStandard.gaf

### 2019-09-20 data/go_annotation_sets/biomart2gaf.sh

@@ -1,0 +1,35 @@
+#!/bin/bash
+
+# This file converts the TSV files downloaded from Gramene to the GAF 2 format
+# Usage:
+# biomart2gaf.sh <TSV file> <db column string>
+# Example:
+#  biomart2gaf.sh Oryza_sativa/Gramene61_IEA "Gramene/Plant_Genes_61/IRGSP-1.0" > Oryza_sativa/Gramene61_IEA.gaf
+
+# Print GAF headers
+echo "!gaf-version:2.0"
+echo "!db	db_object_id	db_object_symbol	qualifier	term_accession	db_reference	evidence_code	with	aspect	db_object_name	db_object_synonym	db_object_type	taxon	date	assigned_by	annotation_extension	gene_product_form_id"
+
+# Skip TSV header and rearrange/expand columns
+tail -n +2 $1 | awk -F $'\t' 'BEGIN {OFS = FS} 
+ { gsub("cellular_component","C",$4)
+   gsub("biological_process","P",$4)
+   gsub("molecular_function","F",$4)
+   print "'"${2}"'", 
+   $1, 
+   $1,
+   "",
+   $2, 
+   "", 
+   $3,
+   "",
+   $4,
+   "",
+   "",
+   "protein",
+   "taxon:4530",
+   "",
+   "",
+   "",
+   ""
+ }'

### 2019-09-20 data/go_annotation_sets/Zea_mays.B73.v4/convert_gold_standard.py
Added more Zea_mays.B73 datasets

@@ -1,0 +1,27 @@
+# This is used to convert the B73.v3 gold standard to B73.v4
+#  1. The gene name mapping from v3 to v4 is read
+#  2. Columns 2 and 3 are populated with the new id if it exists
+ 
+import sys
+import csv
+
+v3_to_v4 = {}
+with open("maize.v3TOv4.geneIDhistory.txt") as mapfile:
+  reader = csv.reader(mapfile, delimiter="\t")
+  for row in reader:
+    if row[1].startswith("Zm"):
+      v3_to_v4[row[0]] = row[1]
+  
+with open(sys.argv[1]) as infile:
+  reader = csv.reader(infile, delimiter="\t")
+  writer = csv.writer(sys.stdout, delimiter="\t")
+ 
+  # Write back two header lines unchanged
+  writer.writerow(reader.next())
+  writer.writerow(reader.next())
+ 
+  for row in reader:
+    if row[2] in v3_to_v4:
+      row[2] = v3_to_v4[row[2]]
+      row[1] = row[2]
+      writer.writerow(row)

### 2019-09-20 text/03-results.Rmd
Restructuring

@@
 ```{r cleanup-table}
-dt2 <- read.csv("../analyses/cleanup/results/cleanup_table.csv", header=F, stringsAsFactors=F)
-dt2$V1 = format_genome(dt2$V1)
+dt2 <- read.csv("../analyses/cleanup/results/cleanup_table.csv", header=T, stringsAsFactors=F)
+dt2$genome = format_genome(dt2$genome)
 kable(dt2, booktabs=TRUE, escape=F, caption = "Number of removed annotations during cleanup.", col.names=c("Genome", "Dataset", "Obsolete Annotations", "Duplicates")) %>%

### 2019-09-20 analyses/cleanup/convert_obo.py

@@ -25,7 +25,7 @@ parents = {}
 main_id = {}
 obsolete = []
 go_names = {}
-with gzip.open("analyses/cleanup/go.obo.gz") as obofile:
+with gzip.open("data/go.obo.gz") as obofile:
   parser = obo_parser.Parser(obofile)
   for stanza in parser:
     if not stanza.name == "Term":

### 2019-09-20 Rakefile.rb
Added quality evaluation

@@ -23,7 +23,7 @@ end
 ## converted GO files
 go_files = ['analyses/cleanup/results/GO.json', 'analyses/cleanup/results/GO_names.json']
 go_files.each do |f|
-  file f => ['analyses/cleanup/convert_obo.py', 'analyses/cleanup/go.obo.gz', 'analyses/cleanup/obo_parser.py'] do
+  file f => ['analyses/cleanup/convert_obo.py', 'data/go.obo.gz', 'analyses/cleanup/obo_parser.py'] do
     sh 'python analyses/cleanup/convert_obo.py'
   end
 end
@@ -66,37 +66,48 @@ task :test do
 end
 
 # Quality Evaluation
-## For each Gold Standard there should be an ADS equivalent
+# Stuff that needs to be created only once from the GOA/OBO
+file "analyses/quality/ads_files/ic.tab" => ["data/go.obo.gz", "data/goa_arabidopsis.gaf.gz"] do
+  sh "gunzip -k data/go.obo.gz"
+  sh "gunzip -k data/goa_arabidopsis.gz"
+  rm_rf "analyses/quality/ads_files/*" # make a clean slate
+  Dir.chdir("analyses/shared/ads/") do # ADS requires to be run from the ads directory
+    sh "perl pipeline.pl --datadir ../../quality/ads_files --obo ../../../data/go.obo --goa ../../../data/goa_arabidopsis.gaf --pipev 1,2"
+  end
+  rm "data/go.obo"
+  rm "data/goa_arabidopsis.gaf"
+end
+
 quality_targets = []
+## For each Gold Standard there should be an ADS equivalent
 FileList.new("analyses/cleanup/results/*/GoldStandard.gaf.gz").to_a.each do |f|
   genome = File.basename(File.dirname(f))
-  # We're taking the corresponding ic.tab file as a representative for all files created by ADS
-  file "analyses/quality/#{genome}/ic.tab" => f do
-    Dir.chdir("analyses/quality/ads/") do # ADS requires to be run from the ads directory
-      sh "gunzip -k ../../cleanup/results/#{genome}/GoldStandard.gaf.gz"
-      sh "gunzip -k ../../cleanup/go.obo.gz"
-      rm_f "../#{genome}/ic.* ../#{genome}/goparents.tab" # Remove old files to start from a clean slate
[…]

### 2019-09-20 Rakefile.rb
New Datasets from Gramene

@@ -10,11 +10,6 @@ end
 
 
 # Cleanup
-def cleanup
-  rm_rf 'analyses/cleanup/results/*'
-  sh 'python analyses/cleanup/cleanup.py'
-end
-
 ## cleanup executable
 file 'analyses/cleanup/cleanup' => 'analyses/cleanup/cleanup.cr' do
   sh 'crystal build --release --no-debug -o analyses/cleanup/cleanup analyses/cleanup/cleanup.cr'
@@ -40,9 +35,10 @@ FileList.new("data/go_annotation_sets/*/*.gaf.gz").to_a.each do |f|
     sh "analyses/cleanup/cleanup #{f}"
   end
   # The cleanup_table also depends on each of these things (in the loop because it depends on all source files)
-  file 'analyses/cleanup/results/cleanup_table.csv' => [f, 'analyses/cleanup/cleanup'] + go_files do
-    sh "analyses/cleanup/cleanup #{f}"
-  end
+  # @TODO for some reason this causes all datasets to be cleaned up again when just one changes
+  # file 'analyses/cleanup/results/cleanup_table.csv' => [f, 'analyses/cleanup/cleanup'] + go_files do
+  #   sh "analyses/cleanup/cleanup #{f}"
+  # end
   cleanup_targets << target
 end
 

### 2019-09-20 data/go_annotation_sets/Zea_mays.B73.v4/convert_gold_standard.py

@@ -1,27 +1,0 @@
-# This is used to convert the B73.v3 gold standard to B73.v4
-#  1. The gene name mapping from v3 to v4 is read
-#  2. Columns 2 and 3 are populated with the new id if it exists
- 
-import sys
-import csv
-
-v3_to_v4 = {}
-with open("maize.v3TOv4.geneIDhistory.txt") as mapfile:
-  reader = csv.reader(mapfile, delimiter="\t")
-  for row in reader:
-    if row[1].startswith("Zm"):
-      v3_to_v4[row[0]] = row[1]
-  
-with open(sys.argv[1]) as infile:
-  reader = csv.reader(infile, delimiter="\t")
-  writer = csv.writer(sys.stdout, delimiter="\t")
- 
-  # Write back two header lines unchanged
-  writer.writerow(reader.next())
-  writer.writerow(reader.next())
- 
-  for row in reader:
-    if row[2] in v3_to_v4:
-      row[2] = v3_to_v4[row[2]]
-      row[1] = row[2]
-      writer.writerow(row)

### 2019-09-20 data/go_annotation_sets/biomart2gaf.sh

@@ -2,9 +2,9 @@
 
 # This file converts the TSV files downloaded from Gramene to the GAF 2 format
 # Usage:
-# biomart2gaf.sh <TSV file> <db column string>
+# biomart2gaf.sh <TSV file> <db column string> <taxon id>
 # Example:
-#  biomart2gaf.sh Oryza_sativa/Gramene61_IEA "Gramene/Plant_Genes_61/IRGSP-1.0" > Oryza_sativa/Gramene61_IEA.gaf
+#  biomart2gaf.sh Oryza_sativa/Gramene61_IEA "Gramene/Plant_Genes_61/IRGSP-1.0" 4530 > Oryza_sativa/Gramene61_IEA.gaf
 
 # Print GAF headers
 echo "!gaf-version:2.0"
@@ -27,7 +27,7 @@ tail -n +2 $1 | awk -F $'\t' 'BEGIN {OFS = FS}
    "",
    "",
    "protein",
-   "taxon:4530",
+   "taxon:'"${3}"'",
    "",
    "",
    "",

### 2019-09-23 Rakefile.rb
Update ADS, exclude intermediary files from git

@@ -3,7 +3,7 @@ require "csv"
 task :default => 'Paper.pdf'
 
 desc 'Typeset the Paper'
-file 'Paper.pdf' => ['analyses/quantity/results/quantity_table.csv', 'analyses/quality/quality_table.csv'] + FileList.new("text/*") do
+file 'Paper.pdf' => ['analyses/quantity/results/quantity_table.csv', 'analyses/quality/results/quality_table.csv'] + FileList.new("text/*") do
   rm_f 'text/_main.Rmd'
   sh %q(R -e 'library("bookdown"); xfun::in_dir("text", render_book("index.Rmd", output_file="../../Paper.pdf", clean=T))')
 end
@@ -79,10 +79,10 @@ quality_targets = []
 FileList.new("analyses/cleanup/results/*/GoldStandard.gaf.gz").to_a.each do |f|
   genome = File.basename(File.dirname(f))
   # Reformat the Gold Standard GAF to the format ADS requires
-  file "analyses/quality/#{genome}/GoldStandard.tsv" => f do
-    sh "mkdir -p analyses/quality/#{genome}"
+  file "analyses/quality/results/#{genome}/GoldStandard.tsv" => f do
+    sh "mkdir -p analyses/quality/results/#{genome}"
     sh "gunzip -k analyses/cleanup/results/#{genome}/GoldStandard.gaf.gz"
-    sh "tail -n+3 analyses/cleanup/results/#{genome}/GoldStandard.gaf | cut -f2,5 > analyses/quality/#{genome}/GoldStandard.tsv"
+    sh "tail -n+3 analyses/cleanup/results/#{genome}/GoldStandard.gaf | cut -f2,5 > analyses/quality/results/#{genome}/GoldStandard.tsv"
     rm "analyses/cleanup/results/#{genome}/GoldStandard.gaf"
   end
 
@@ -90,18 +90,18 @@ FileList.new("analyses/cleanup/results/*/GoldStandard.gaf.gz").to_a.each do |f|
   FileList.new("analyses/cleanup/results/#{genome}/*.gaf.gz").to_a.each do |ds|
     dataset = File.basename(ds).split(".").first
     next if dataset == "GoldStandard" # We don't need to evaluate the GoldStandard against itself.
-    target = "analyses/quality/#{genome}/#{dataset}.SimGIC2"
-    file target => [ds, "analyses/quality/ads_files/ic.tab", "analyses/quality/#{genome}/GoldStandard.tsv"] do
[…]

### 2019-09-23 text/03-results.Rmd
Fix some restructuring artefacts

@@
 ```{r quality-table}
-dt2 <- read.csv("../analyses/quality/quality_table.csv", header=T, stringsAsFactors=F)
+dt2 <- read.csv("../analyses/quality/results/quality_table.csv", header=T, stringsAsFactors=F)
 dt2$genome = format_genome(dt2$genome)

### 2019-09-23 Rakefile.rb

@@ -24,7 +24,7 @@ go_files.each do |f|
 end
 
 ## Collect everything that needs to be up-to-date after cleanup
-cleanup_targets = ['analyses/cleanup/results/cleanup_table.csv']
+cleanup_targets = [] # ['analyses/cleanup/results/cleanup_table.csv']
 
 ## For each raw dataset there should be an up-to-date cleaned one
 FileList.new("data/go_annotation_sets/*/*.gaf.gz").to_a.each do |f|
@@ -41,6 +41,7 @@ FileList.new("data/go_annotation_sets/*/*.gaf.gz").to_a.each do |f|
   # end
   cleanup_targets << target
 end
+
 
 ## If there are any cleaned up files that do not have a source file anymore, remove them
 (FileList.new("analyses/cleanup/results/*/*.gaf.gz").to_a - cleanup_targets).each do |f|
@@ -63,12 +64,12 @@ end
 
 # Quality Evaluation
 # Stuff that needs to be created only once from the GOA/OBO
-file "analyses/quality/ads_files/ic.tab" => ["data/go.obo.gz", "data/goa_arabidopsis.gaf.gz"] do
+file "analyses/quality/results/ads_files/ic.tab" => ["data/go.obo.gz", "data/goa_arabidopsis.gaf.gz"] do
   sh "gunzip -k data/go.obo.gz"
-  sh "gunzip -k data/goa_arabidopsis.gz"
-  rm_rf "analyses/quality/ads_files/*" # make a clean slate
+  sh "gunzip -k data/goa_arabidopsis.gaf.gz"
+  rm_rf "analyses/quality/results/ads_files/*" # make a clean slate
   Dir.chdir("analyses/shared/ads/") do # ADS requires to be run from the ads directory
-    sh "perl pipeline.pl --datadir ../../quality/ads_files --obo ../../../data/go.obo --goa ../../../data/goa_arabidopsis.gaf --pipev 1,2"
+    sh "perl pipeline.pl --datadir ../../quality/results/ads_files --obo ../../../data/go.obo --goa ../../../data/goa_arabidopsis.gaf --pipev 1,2"
   end
   rm "data/go.obo"
   rm "data/goa_arabidopsis.gaf"

### 2019-09-26 text/03-results.Rmd
Add another quality evaluation metric: TC_AUCPCR

--- 2019-09-20 text/03-results.Rmd
@@
 ```{r quality-table}
-dt2 <- read.csv("../analyses/quality/quality_table.csv", header=T, stringsAsFactors=F)
+dt2 <- read.csv("../analyses/quality/results/quality_table.csv", header=T, stringsAsFactors=F)
 dt2$genome = format_genome(dt2$genome)
-kable(dt2, booktabs=TRUE, escape=F, caption = "Quality evaluation of the used GO annotation sets.", col.names=c("Genome", "Dataset", "SimGIC2 score")) %>%
+kable(dt2, booktabs=TRUE, escape=F, caption = "Quality evaluation of the used GO annotation sets.", col.names=c("Genome", "Dataset", "SimGIC2 score", "TC AUCPCR score")) %>%
  kable_styling(latex_options = c("striped")) %>%

### 2019-09-26 Rakefile.rb

@@ -103,6 +103,7 @@ FileList.new("analyses/cleanup/results/*/GoldStandard.gaf.gz").to_a.each do |f|
       sh "gunzip -k data/go.obo.gz"
       Dir.chdir("analyses/shared/ads/") do # ADS requires to be run from the ads directory
         sh "bin/goscores -p ../../quality/results/#{genome}/#{dataset}.predictions -t ../../quality/results/#{genome}/GoldStandard.tsv -g -b ../../../data/go.obo -i ../../quality/results/ads_files/ic.tab ../../quality/results/ads_files/goparents.tab -m 'SF=SimGIC2' > ../../quality/results/#{genome}/#{dataset}.SimGIC2"
+        sh "bin/goscores -p ../../quality/results/#{genome}/#{dataset}.predictions -t ../../quality/results/#{genome}/GoldStandard.tsv -g -b ../../../data/go.obo -m 'LIST=gene,TH=all,SUMF1=mean,SF=AUCPR' > ../../quality/results/#{genome}/#{dataset}.TC_AUCPCR"
       end
       rm "data/go.obo"
     end
@@ -113,12 +114,13 @@ end
 # Collect all SimGIC2 scores in a table
 file 'analyses/quality/results/quality_table.csv' => quality_targets do
   CSV.open("analyses/quality/results/quality_table.csv", "wb+") do |csv|
-    csv << ["genome", "dataset", "SimGIC2"]
+    csv << ["genome", "dataset", "SimGIC2", "TC_AUCPCR"]
     quality_targets.each do |t|
       dataset = File.basename(t).split(".").first
       genome = File.basename(File.dirname(t))
-      score = IO.read(t).chomp
-      csv << [genome, dataset, score]
+      simgic2_score = IO.read(t).chomp
+      tc_aucpcr_score = IO.read("analyses/quality/results/#{genome}/#{dataset}.TC_AUCPCR").chomp
+      csv << [genome, dataset, simgic2_score, tc_aucpcr_score]
     end
   end
 end

### 2019-10-04 Paper.tex
Added quality evaluation
New Datasets from Gramene
Fix some restructuring artefacts
Add a Gold Standard for barley and GOMAP dataset for Cotton
Add another quality evaluation metric: TC_AUCPCR
Restructure quantity table and add some real gene counts

@@
 \midrule
-\rowcolor{gray!6}  \textit{Glycine max} & GOMAP & 203 & 0\\
+\rowcolor{gray!6}  \textit{Brachypodium distachyon} & GOMAP & 696 & 43\\
 \cmidrule{1-4}
-\textit{Hordeum vulgarum} & GOMAP & 101 & 0\\
+\textit{Gossypium raimondii} & GOMAP & 184 & 0\\
 \cmidrule{1-4}
-\rowcolor{gray!6}  \textit{Medicago truncatula} A17 & GOMAP & 0 & 0\\
+\rowcolor{gray!6}  \textit{Hordeum vulgarum} & GoldStandard & 0 & 4\\
 \cmidrule{1-4}
-\textit{Medicago truncatula} R108 & GOMAP & 0 & 0\\
+\textit{Medicago truncatula} A17 & GOMAP & 0 & 0\\
 \cmidrule{1-4}
-\rowcolor{gray!6}   & GOMAP & 111 & 2\\
+\rowcolor{gray!6}  \textit{Medicago truncatula} R108 & GOMAP & 0 & 0\\
+\cmidrule{1-4}
+ & GOMAP & 111 & 2\\
 
-\multirow{-2}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & GoldStandard & 38 & 556\\
+\rowcolor{gray!6}   & GoldStandard & 38 & 556\\
+
+\multirow{-3}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & Gramene61-IEA & 10 & 14\\
 \cmidrule{1-4}
@@
 \cmidrule{1-4}
-\textit{Triticum aestivum} & GOMAP & 285 & 0\\
+\textit{Sorghum bicolor} & GOMAP & 690 & 59\\
 \cmidrule{1-4}
-\rowcolor{gray!6}  \textit{Vigna unguiculata} & GOMAP & 0 & 0\\
+\rowcolor{gray!6}   & GOMAP & 285 & 0\\
+
+ & GoldStandard & 0 & 10\\
+
+\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash \textit{Triticum aestivum}} & Gramene61-IEA & 47 & 48\\
 \cmidrule{1-4}
-\textit{Zea mays} B73.v4 & GOMAP & 752 & 83\\
-\cmidrule{1-4}
-\rowcolor{gray!6}  \textit{Zea mays} Mo17 & GOMAP & 726 & 77\\
-\cmidrule{1-4}
-\textit{Zea mays} PH207 & GOMAP & 798 & 76\\
-\cmidrule{1-4}
-\rowcolor{gray!6}  \textit{Zea mays} W22 & GOMAP & 754 & 82\\
-\cmidrule{1-4}
-\textit{Arachis hypogaea} & GOMAP & 0 & 0\\
+\textit{Vigna unguiculata} & GOMAP & 0 & 0\\
 \cmidrule{1-4}
@@
 \cmidrule{1-4}
-\rowcolor{gray!6}   & Gramene61-IEA & 10 & 14\\
+\rowcolor{gray!6}   & GOMAP & 752 & 83\\
 
-\multirow{-2}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & Gramene61-all & 48 & 9565\\
+ & GoldStandard & 55 & 174\\
+
+\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} & Gramene61-IEA & 99 & 157\\
+\cmidrule{1-4}
+\textit{Zea mays} Mo17 & GOMAP & 726 & 77\\
+\cmidrule{1-4}
+\rowcolor{gray!6}  \textit{Zea mays} PH207 & GOMAP & 798 & 76\\
+\cmidrule{1-4}
+\textit{Zea mays} W22 & GOMAP & 754 & 82\\
 \bottomrule
@@
 \toprule
-\multicolumn{3}{c}{ } & \multicolumn{4}{c}{Annotations\textsuperscript{a}} & \multicolumn{4}{c}{Annotated Genes [\%]\textsuperscript{b}} & \multicolumn{4}{c}{Median Ann. per G.\textsuperscript{c}} \\
+\multicolumn{3}{c}{ } & \multicolumn{4}{c}{Genes Annotated[\%]\textsuperscript{a}} & \multicolumn{4}{c}{Annotations\textsuperscript{b}} & \multicolumn{4}{c}{Median Ann. per G.\textsuperscript{c}} \\
 \cmidrule(l{3pt}r{3pt}){4-7} \cmidrule(l{3pt}r{3pt}){8-11} \cmidrule(l{3pt}r{3pt}){12-15}
@@
 \midrule
-\rowcolor{gray!6}  \textit{Arachis hypogaea} &  & GOMAP & 153433 & 132944 & 493799 & 780176 & 57667 & 56855 & 67123 & 67124 & 2 & 2 & 6 & 10\\
+\rowcolor{gray!6}  \textit{Arachis hypogaea} & 67,124 & GOMAP & 85.91 & 84.70 & 100.00 & 100.00 & 153,433 & 132,944 & 493,799 & 780,176 & 2 & 2 & 6 & 10\\
+\cmidrule{1-15}
+\textit{Brachypodium distachyon} & 100 & GOMAP & 27,923.00 & 29,292.00 & 34,309.00 & 34,310.00 & 75,877 & 69,709 & 255,807 & 401,393 & 2 & 2 & 6 & 10\\
+\cmidrule{1-15}
+\rowcolor{gray!6}  \textit{Glycine max} & 52,872 & GOMAP & 87.04 & 88.96 & 100.00 & 100.00 & 129,215 & 113,827 & 417,555 & 660,597 & 2 & 2 & 6 & 11\\
+\cmidrule{1-15}
+\textit{Gossypium raimondii} & 100 & GOMAP & 34,908.00 & 34,651.00 & 37,504.00 & 37,505.00 & 96,793 & 85,511 & 307,921 & 490,225 & 2 & 2 & 6 & 11\\
+\cmidrule{1-15}
+\rowcolor{gray!6}   &  & GOMAP & 88.68 & 91.79 & 100.00 & 100.00 & 88,130 & 80,282 & 272,823 & 441,235 & 2 & 2 & 5 & 10\\
 
-\textit{Glycine max} &  & GOMAP & 129215 & 113827 & 417555 & 660597 & 46020 & 47034 & 52871 & 52872 & 2 & 2 & 6 & 11\\
+\multirow{-2}{*}{\raggedright\arraybackslash \textit{Hordeum vulgarum}} & \multirow{-2}{*}{\raggedleft\arraybackslash 39,734} & GoldStandard & 0.02 & 0.05 & 0.05 & 0.07 & 7 & 23 & 45 & 75 & 0 & 1 & 1 & 2\\
+\cmidrule{1-15}
+\rowcolor{gray!6}  \textit{Medicago truncatula} A17 & 50,444 & GOMAP & 83.90 & 86.70 & 100.00 & 100.00 & 107,362 & 99,719 & 364,065 & 571,146 & 2 & 2 & 6 & 10\\
+\cmidrule{1-15}
+\textit{Medicago truncatula} R108 & 55,706 & GOMAP & 72.40 & 90.15 & 100.00 & 100.00 & 112,343 & 108,031 & 382,322 & 602,696 & 1 & 2 & 5 & 9\\
+\cmidrule{1-15}
+\rowcolor{gray!6}   &  & GOMAP & 79.89 & 83.33 & 100.00 & 100.00 & 72,780 & 64,685 & 248,700 & 386,165 & 2 & 2 & 6 & 9\\
 
-\rowcolor{gray!6}  \textit{Hordeum vulgarum} &  & GOMAP & 88130 & 80282 & 272823 & 441235 & 35237 & 36470 & 39733 & 39734 & 2 & 2 & 5 & 10\\
+ &  & GoldStandard & 15.98 & 20.61 & 25.21 & 31.79 & 7,730 & 11,060 & 19,378 & 38,176 & 1 & 1 & 1 & 3\\
 
-\textit{Medicago truncatula} A17 &  & GOMAP & 107362 & 99719 & 364065 & 571146 & 42325 & 43736 & 50443 & 50444 & 2 & 2 & 6 & 10\\
+\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & \multirow{-3}{*}{\raggedleft\arraybackslash 35,825} & Gramene61-IEA & 30.07 & 43.37 & 46.63 & 59.86 & 14,633 & 32,787 & 39,105 & 86,529 & 1 & 1 & 1 & 3\\
+\cmidrule{1-15}
+\textit{Phaseolus vulgaris} & 27,433 & GOMAP & 94.54 & 93.10 & 100.00 & 100.00 & 72,005 & 64,583 & 229,630 & 366,218 & 2 & 2 & 6 & 11\\
+\cmidrule{1-15}
+\rowcolor{gray!6}  \textit{Sorghum bicolor} & 100 & GOMAP & 28,154.00 & 29,353.00 & 34,128.00 & 34,129.00 & 76,689 & 70,190 & 259,413 & 406,292 & 2 & 2 & 6 & 10\\
+\cmidrule{1-15}
+ &  & GOMAP & 88.61 & 91.01 & 100.00 & 100.00 & 267,741 & 218,623 & 785,960 & 1,272,324 & 2 & 2 & 6 & 10\\
 
-\rowcolor{gray!6}  \textit{Medicago truncatula} R108 &  & GOMAP & 112343 & 108031 & 382322 & 602696 & 40332 & 50220 & 55706 & 55706 & 1 & 2 & 5 & 9\\
+\rowcolor{gray!6}   &  & GoldStandard & 0.89 & 0.57 & 1.54 & 1.73 & 1,590 & 923 & 4,807 & 7,323 & 1 & 0 & 2 & 3\\
 
- &  & GOMAP & 72780 & 64685 & 248700 & 386165 & 28619 & 29853 & 35824 & 35825 & 2 & 2 & 6 & 9\\
+\multirow{-3}{*}{\raggedright\arraybackslash \textit{Triticum aestivum}} & \multirow{-3}{*}{\raggedleft\arraybackslash 107,891} & Gramene61-IEA & 26.74 & 55.24 & 48.72 & 70.24 & 38,975 & 109,319 & 109,518 & 257,832 & 0 & 1 & 1 & 2\\
+\cmidrule{1-15}
+\rowcolor{gray!6}  \textit{Vigna unguiculata} & 29,773 & GOMAP & 91.27 & 91.10 & 100.00 & 100.00 & 75,867 & 68,313 & 243,278 & 387,458 & 2 & 2 & 6 & 11\\
+\cmidrule{1-15}
+ &  & GOMAP & 34,866.00 & 38,073.00 & 39,468.00 & 39,469.00 & 135,211 & 87,420 & 291,251 & 513,882 & 3 & 2 & 6 & 11\\
 
-\rowcolor{gray!6}   &  & GoldStandard & 7730 & 11060 & 19378 & 38176 & 5725 & 7383 & 9031 & 11387 & 1 & 1 & 1 & 3\\
+\rowcolor{gray!6}   &  & GoldStandard & 1,548.00 & 60.00 & 151.00 & 1,634.00 & 1,565 & 65 & 299 & 1,929 & 1 & 0 & 0 & 1\\
 
- &  & Gramene61-IEA & 14633 & 32787 & 39105 & 86529 & 10771 & 15537 & 16705 & 21446 & 1 & 1 & 1 & 3\\
+ &  & Gramene49 & 11,834.00 & 17,991.00 & 15,800.00 & 21,926.00 & 20,072 & 31,056 & 30,089 & 81,217 & 1 & 1 & 1 & 3\\
 
-\rowcolor{gray!6}  \multirow{-4}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} &  & Gramene61-all & 20622 & 40674 & 54402 & 115710 & 13272 & 16962 & 18513 & 22272 & 1 & 1 & 2 & 4\\
+\rowcolor{gray!6}  \multirow{-4}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} &  & Phytozome & 4,524.00 & 13,728.00 & 11,365.00 & 16,132.00 & 4,787 & 19,044 & 13,100 & 36,931 & 0 & 1 & 1 & 2\\
 
-\textit{Phaseolus vulgaris} &  & GOMAP & 72005 & 64583 & 229630 & 366218 & 25934 & 25539 & 27432 & 27433 & 2 & 2 & 6 & 11\\
+ &  & GOMAP & 36,717.00 & 37,337.00 & 39,323.00 & 39,324.00 & 88,827 & 82,251 & 278,719 & 449,797 & 2 & 2 & 6 & 10\\
 
-\rowcolor{gray!6}  \textit{Triticum aestivum} &  & GOMAP & 267741 & 218623 & 785960 & 1272324 & 95604 & 98187 & 107890 & 107891 & 2 & 2 & 6 & 10\\
+\rowcolor{gray!6}   &  & GoldStandard & 8,349.00 & 10,067.00 & 12,120.00 & 14,971.00 & 11,510 & 15,019 & 25,737 & 52,428 & 1 & 1 & 1 & 3\\
 
-\textit{Vigna unguiculata} &  & GOMAP & 75867 & 68313 & 243278 & 387458 & 27173 & 27124 & 29772 & 29773 & 2 & 2 & 6 & 11\\
+\multirow{-3}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} &  & Gramene61-IEA & 14,774.00 & 22,064.00 & 23,965.00 & 29,152.00 & 20,265 & 47,657 & 58,110 & 126,525 & 1 & 1 & 2 & 3\\
 
-\rowcolor{gray!6}   &  & GOMAP & 135211 & 87420 & 291251 & 513882 & 34866 & 38073 & 39468 & 39469 & 3 & 2 & 6 & 11\\
+\rowcolor{gray!6}  \textit{Zea mays} Mo17 &  & GOMAP & 33,618.00 & 35,105.00 & 38,619.00 & 38,620.00 & 87,567 & 79,214 & 277,787 & 444,568 & 2 & 2 & 6 & 10\\
 
- &  & GoldStandard & 1565 & 65 & 299 & 1929 & 1548 & 60 & 151 & 1634 & 1 & 0 & 0 & 1\\
+\textit{Zea mays} PH207 &  & GOMAP & 35,170.00 & 36,762.00 & 40,556.00 & 40,557.00 & 90,617 & 85,500 & 288,677 & 464,794 & 2 & 2 & 6 & 10\\
 
-\rowcolor{gray!6}   &  & Gramene49 & 20072 & 31056 & 30089 & 81217 & 11834 & 17991 & 15800 & 21926 & 1 & 1 & 1 & 3\\
-
-\multirow{-4}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} &  & Phytozome & 4787 & 19044 & 13100 & 36931 & 4524 & 13728 & 11365 & 16132 & 0 & 1 & 1 & 2\\
-
-\rowcolor{gray!6}  \textit{Zea mays} B73.v4 &  & GOMAP & 88827 & 82251 & 278719 & 449797 & 36717 & 37337 & 39323 & 39324 & 2 & 2 & 6 & 10\\
-
-\textit{Zea mays} Mo17 &  & GOMAP & 87567 & 79214 & 277787 & 444568 & 33618 & 35105 & 38619 & 38620 & 2 & 2 & 6 & 10\\
-
-\rowcolor{gray!6}  \textit{Zea mays} PH207 &  & GOMAP & 90617 & 85500 & 288677 & 464794 & 35170 & 36762 & 40556 & 40557 & 2 & 2 & 6 & 10\\
-
-\textit{Zea mays} W22 & \multirow{-20}{*}{\raggedleft\arraybackslash 100} & GOMAP & 95390 & 85039 & 289780 & 470209 & 36987 & 37685 & 40689 & 40690 & 2 & 2 & 6 & 10\\
+\rowcolor{gray!6}  \textit{Zea mays} W22 & \multirow{-10}{*}{\raggedleft\arraybackslash 100} & GOMAP & 36,987.00 & 37,685.00 & 40,689.00 & 40,690.00 & 95,390 & 85,039 & 289,780 & 470,209 & 2 & 2 & 6 & 10\\
 \bottomrule
@@
 \begin{tablenotes}
-\item[a] How many annotations in the CC, BF, and MP aspect does this dataset contain? A = How many in total? $\textrm{A} = \textrm{CC} + \textrm{BF} + \textrm{MP}$
-\item[b] How many genes in the genome have at least one GO term from the CC, BF, MP aspect annotated to them?
+\item[a] How many genes in the genome have at least one GO term from the CC, BF, MP aspect annotated to them?
 A = How many at least one from any aspect?
 ($\textrm{A} = \textrm{CC} \cup \textrm{BF} \cup \textrm{MP}$)
+\item[b] How many annotations in the CC, BF, and MP aspect does this dataset contain? A = How many in total? $\textrm{A} = \textrm{CC} + \textrm{BF} + \textrm{MP}$
 \item[c] Take a typical gene that is present in the annotation set.
@@
 \centering
-\begin{tabular}{llr}
+\begin{tabular}{llrr}
 \toprule
-Genome & Dataset & SimGIC2 score\\
+Genome & Dataset & SimGIC2 score & TC AUCPCR score\\
 \midrule
-\rowcolor{gray!6}   & GOMAP & 0.241470\\
+\rowcolor{gray!6}  \textit{Hordeum vulgarum} & GOMAP & 0.158996 & 0.000477\\
+\cmidrule{1-4}
+ & GOMAP & 0.253680 & 0.204084\\
 
- & GoldStandard & 0.999971\\
+\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & Gramene61-IEA & 0.330437 & 0.193740\\
+\cmidrule{1-4}
+ & GOMAP & 0.218996 & 0.010039\\
 
-\rowcolor{gray!6}   & Gramene61-IEA & 0.324831\\
+\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Triticum aestivum}} & Gramene61-IEA & 0.175564 & 0.005397\\
+\cmidrule{1-4}
+ & GOMAP & 0.052182 & 0.012709\\
 
-\multirow{-4}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & Gramene61-all & 0.732289\\
-\cmidrule{1-3}
-\rowcolor{gray!6}   & GOMAP & 0.072971\\
+\rowcolor{gray!6}   & Gramene49 & 0.091475 & 0.019127\\
 
- & GoldStandard & 0.998562\\
+\multirow{-3}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} & Phytozome & 0.028721 & 0.004498\\
+\cmidrule{1-4}
+\rowcolor{gray!6}   & GOMAP & 0.257543 & 0.196845\\
 
-\rowcolor{gray!6}   & Gramene49 & 0.126450\\
-
-\multirow{-4}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} & Phytozome & 0.032693\\
+\multirow{-2}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} & Gramene61-IEA & 0.328777 & 0.188584\\
 \bottomrule

### 2019-10-04 text/03-results.Rmd
Restructure quantity table and add some real gene counts

@@
 names(headers_above) <- c(" ", 
-  paste0("Annotations", footnote_marker_alphabet(1, double_escape=T)),
-  paste0("Annotated Genes [\\\\%]", footnote_marker_alphabet(2, double_escape=T)), 
+  paste0("Genes Annotated[\\\\%]", footnote_marker_alphabet(1, double_escape=T)), 
+  paste0("Annotations", footnote_marker_alphabet(2, double_escape=T)),
   paste0("Median Ann. per G.", footnote_marker_alphabet(3, double_escape=T)))
-kable(dt2, booktabs=T, escape=F, caption = "Quantitative metrics of the cleaned functional annotation sets.
+kable(dt2, booktabs=T, digits=2, format.args=list(big.mark=","), escape=F, caption = "Quantitative metrics of the cleaned functional annotation sets.
 CC, BF, MP, and A refer to the aspects of the GO: Cellular Component, Biological Function, Molecular Process, and Any/All.", col.names=c("Genome", "Genes", "Dataset", "CC", "BF", "MP", "A","CC", "BF", "MP", "A","CC", "BF", "MP", "A")) %>%
@@
   footnote(alphabet=c(
-    "How many annotations in the CC, BF, and MP aspect does this dataset contain? A = How many in total? $\\\\textrm{A} = \\\\textrm{CC} + \\\\textrm{BF} + \\\\textrm{MP}$",
     "How many genes in the genome have at least one GO term from the CC, BF, MP aspect annotated to them?
@@
 ($\\\\textrm{A} = \\\\textrm{CC} \\\\cup \\\\textrm{BF} \\\\cup \\\\textrm{MP}$)",
+    "How many annotations in the CC, BF, and MP aspect does this dataset contain? A = How many in total? $\\\\textrm{A} = \\\\textrm{CC} + \\\\textrm{BF} + \\\\textrm{MP}$",
     "Take a typical gene that is present in the annotation set.

### 2019-10-04 Rakefile.rb

@@ -96,7 +96,7 @@ FileList.new("analyses/cleanup/results/*/GoldStandard.gaf.gz").to_a.each do |f|
       # Reformat GAF to required format
       sh "gunzip -k analyses/cleanup/results/#{genome}/#{dataset}.gaf.gz"
       # @TODO ADS requires a score for each prediction and they can't all be 1, so I'm adding a dummy entry
-      IO.write("analyses/quality/results/#{genome}/#{dataset}.predictions", "foobar\tGO:00000331\t0")
+      IO.write("analyses/quality/results/#{genome}/#{dataset}.predictions", "foobar\tGO:00000331\t0\n")
       sh "tail -n+3 analyses/cleanup/results/#{genome}/#{dataset}.gaf | cut -f2,5 | awk '{print $0\"\\t1\"}' >> analyses/quality/results/#{genome}/#{dataset}.predictions"
       rm "analyses/cleanup/results/#{genome}/#{dataset}.gaf"
 

### 2019-10-04 analyses/quantity/quantity.R

@@ -49,10 +49,6 @@ csv = data.frame(
   genome = "",
   n_genes = 0,
   dataset = "",
-  annotations_c = 0,
-  annotations_f = 0,
-  annotations_p = 0,
-  annotations_a = 0,
   genes_annotated_c = 0,
   genes_annotated_f = 0,
   genes_annotated_p = 0,
@@ -62,6 +58,10 @@ csv = data.frame(
   p_genes_annotated_f = 0,
   p_genes_annotated_p = 0,
   p_genes_annotated_a = 0,
+  annotations_c = 0,
+  annotations_f = 0,
+  annotations_p = 0,
+  annotations_a = 0,
   median_annotations_per_gene_c = 0,
   median_annotations_per_gene_f = 0,
   median_annotations_per_gene_p = 0,
@@ -84,10 +84,6 @@ for(genome_path in genomes) {
       genome = genome_name,
       n_genes = n_genes_per_genome[n_genes_per_genome$genome == genome_name,"n_genes"],
       dataset = strsplit(basename(gaf_file), "\\.")[[1]][1], # filename without extension
-      annotations_c = aspect_counts[["C"]],
-      annotations_f = aspect_counts[["F"]],
-      annotations_p = aspect_counts[["P"]],
-      annotations_a = sum(aspect_counts),
       genes_annotated_c = genes_annotated[["C"]],
       genes_annotated_f = genes_annotated[["F"]],
       genes_annotated_p = genes_annotated[["P"]],
@@ -96,6 +92,10 @@ for(genome_path in genomes) {
       p_genes_annotated_f = genes_annotated[["F"]]/n_genes_per_genome[n_genes_per_genome$genome == genome_name,"n_genes"]*100,
       p_genes_annotated_p = genes_annotated[["P"]]/n_genes_per_genome[n_genes_per_genome$genome == genome_name,"n_genes"]*100,
       p_genes_annotated_a = genes_annotated[["A"]]/n_genes_per_genome[n_genes_per_genome$genome == genome_name,"n_genes"]*100,
+      annotations_c = aspect_counts[["C"]],
+      annotations_f = aspect_counts[["F"]],
+      annotations_p = aspect_counts[["P"]],
+      annotations_a = sum(aspect_counts),
       median_annotations_per_gene_c = medians[["C"]],
       median_annotations_per_gene_f = medians[["F"]],
       median_annotations_per_gene_p = medians[["P"]],

### 2019-10-19 Paper.tex
Added some text, genes per genome, and links to download tables

@@
 
+\hypertarget{generating-predictions}{%
+\subsection{Generating Predictions}\label{generating-predictions}}
+
+Used GOMAP on condo lalala. Input files are (usually) published along results.
+
 \hypertarget{clean-up}{%
@@
 
-\hypertarget{choosing-the-right-evaluation-metric}{%
-\subsection{Choosing the right evaluation metric}\label{choosing-the-right-evaluation-metric}}
+\hypertarget{quantitative-evaluation}{%
+\subsection{Quantitative Evaluation}\label{quantitative-evaluation}}
 
-A plethora of different metric to evaluate the quality of functional annotation predictions is available using different approaches and there seems to be no clear standard yet.
-\texttt{TODO:\ THIS\ IS\ WEAK}
-Additionally, each of the metrics has a different focus and lalala so choosing a metric for quality evaluation is not trivial.
+lalala lololo table xyz
+
+\hypertarget{quality-evaluation}{%
+\subsection{Quality Evaluation}\label{quality-evaluation}}
+
+Quality evaluation of gene function predictions is not trivial and usually done by comparing the set of predicted functions of a gene against a \emph{gold standard} consisting of annotations that are assumed to be correct.
+We used annotations that were created or in some way curated with human participation for gold standards.
+There are a plethora of different metrics to perform the comparison of predictions against this gold standard.
 When we first published GOMAP \citep{Wimalanathan2018}, we used a modified version of the hierarchical evaluation metrics originally introduced in \citep{Verspoor2006} because they were simple, clear, and part of an earlier attempt at unifying and standardizing GO annotation comparisons \citep{Defoin-Platel2011}.
@@
 
-We then evaluated our predictions and the other annotation sets using the best performing metrics as well as the one we previously used.
-\texttt{TODO}
+We then evaluated our predictions and the other annotation sets using the best performing metrics as well as the one we previously used (Table \texttt{TODO}).
+
+\hypertarget{phylogenetic-tree-construction}{%
+\subsection{Phylogenetic Tree Construction}\label{phylogenetic-tree-construction}}
+
+To demonstrate that a more top-level and holistic use of whole-genome functional predictions can still be useful we devised some simple ways of applying phylogenetic methods to our predictions.
+\#\#\# Distance Based
+\#\#\# Character Based
+
+\hypertarget{ensuring-reproducibility}{%
+\subsection{Ensuring Reproducibility}\label{ensuring-reproducibility}}
+
+containerization, github\ldots{}
 
@@
 \centering
+\begin{threeparttable}
 \begin{tabular}{llrr}
@@
 \end{tabular}
+\begin{tablenotes}
+\item \href{https://raw.githubusercontent.com/Dill-PICL/GOMAP-Paper-2019.1/master/analyses/cleanup/results/cleanup_table.csv}{Download this table (CSV)}
+\end{tablenotes}
+\end{threeparttable}
 \end{table}
@@
 \cmidrule{1-15}
-\textit{Brachypodium distachyon} & 100 & GOMAP & 27,923.00 & 29,292.00 & 34,309.00 & 34,310.00 & 75,877 & 69,709 & 255,807 & 401,393 & 2 & 2 & 6 & 10\\
+\textit{Brachypodium distachyon} & 34,310 & GOMAP & 81.38 & 85.37 & 100.00 & 100.00 & 75,877 & 69,709 & 255,807 & 401,393 & 2 & 2 & 6 & 10\\
 \cmidrule{1-15}
@@
 \cmidrule{1-15}
-\textit{Gossypium raimondii} & 100 & GOMAP & 34,908.00 & 34,651.00 & 37,504.00 & 37,505.00 & 96,793 & 85,511 & 307,921 & 490,225 & 2 & 2 & 6 & 11\\
+\textit{Gossypium raimondii} & 37,505 & GOMAP & 93.08 & 92.39 & 100.00 & 100.00 & 96,793 & 85,511 & 307,921 & 490,225 & 2 & 2 & 6 & 11\\
 \cmidrule{1-15}
@@
 \cmidrule{1-15}
-\rowcolor{gray!6}  \textit{Sorghum bicolor} & 100 & GOMAP & 28,154.00 & 29,353.00 & 34,128.00 & 34,129.00 & 76,689 & 70,190 & 259,413 & 406,292 & 2 & 2 & 6 & 10\\
+\rowcolor{gray!6}  \textit{Sorghum bicolor} & 34,129 & GOMAP & 82.49 & 86.01 & 100.00 & 100.00 & 76,689 & 70,190 & 259,413 & 406,292 & 2 & 2 & 6 & 10\\
 \cmidrule{1-15}
@@
 \cmidrule{1-15}
- &  & GOMAP & 34,866.00 & 38,073.00 & 39,468.00 & 39,469.00 & 135,211 & 87,420 & 291,251 & 513,882 & 3 & 2 & 6 & 11\\
+ &  & GOMAP & 88.34 & 96.46 & 100.00 & 100.00 & 135,211 & 87,420 & 291,251 & 513,882 & 3 & 2 & 6 & 11\\
 
-\rowcolor{gray!6}   &  & GoldStandard & 1,548.00 & 60.00 & 151.00 & 1,634.00 & 1,565 & 65 & 299 & 1,929 & 1 & 0 & 0 & 1\\
+\rowcolor{gray!6}   &  & GoldStandard & 3.92 & 0.15 & 0.38 & 4.14 & 1,565 & 65 & 299 & 1,929 & 1 & 0 & 0 & 1\\
 
- &  & Gramene49 & 11,834.00 & 17,991.00 & 15,800.00 & 21,926.00 & 20,072 & 31,056 & 30,089 & 81,217 & 1 & 1 & 1 & 3\\
+ &  & Gramene49 & 29.98 & 45.58 & 40.03 & 55.55 & 20,072 & 31,056 & 30,089 & 81,217 & 1 & 1 & 1 & 3\\
 
-\rowcolor{gray!6}  \multirow{-4}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} &  & Phytozome & 4,524.00 & 13,728.00 & 11,365.00 & 16,132.00 & 4,787 & 19,044 & 13,100 & 36,931 & 0 & 1 & 1 & 2\\
+\rowcolor{gray!6}  \multirow{-4}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} & \multirow{-4}{*}{\raggedleft\arraybackslash 39,469} & Phytozome & 11.46 & 34.78 & 28.79 & 40.87 & 4,787 & 19,044 & 13,100 & 36,931 & 0 & 1 & 1 & 2\\
+\cmidrule{1-15}
+ &  & GOMAP & 93.37 & 94.95 & 100.00 & 100.00 & 88,827 & 82,251 & 278,719 & 449,797 & 2 & 2 & 6 & 10\\
 
- &  & GOMAP & 36,717.00 & 37,337.00 & 39,323.00 & 39,324.00 & 88,827 & 82,251 & 278,719 & 449,797 & 2 & 2 & 6 & 10\\
+\rowcolor{gray!6}   &  & GoldStandard & 21.23 & 25.60 & 30.82 & 38.07 & 11,510 & 15,019 & 25,737 & 52,428 & 1 & 1 & 1 & 3\\
 
-\rowcolor{gray!6}   &  & GoldStandard & 8,349.00 & 10,067.00 & 12,120.00 & 14,971.00 & 11,510 & 15,019 & 25,737 & 52,428 & 1 & 1 & 1 & 3\\
-
-\multirow{-3}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} &  & Gramene61-IEA & 14,774.00 & 22,064.00 & 23,965.00 & 29,152.00 & 20,265 & 47,657 & 58,110 & 126,525 & 1 & 1 & 2 & 3\\
-
-\rowcolor{gray!6}  \textit{Zea mays} Mo17 &  & GOMAP & 33,618.00 & 35,105.00 & 38,619.00 & 38,620.00 & 87,567 & 79,214 & 277,787 & 444,568 & 2 & 2 & 6 & 10\\
-
-\textit{Zea mays} PH207 &  & GOMAP & 35,170.00 & 36,762.00 & 40,556.00 & 40,557.00 & 90,617 & 85,500 & 288,677 & 464,794 & 2 & 2 & 6 & 10\\
-
-\rowcolor{gray!6}  \textit{Zea mays} W22 & \multirow{-10}{*}{\raggedleft\arraybackslash 100} & GOMAP & 36,987.00 & 37,685.00 & 40,689.00 & 40,690.00 & 95,390 & 85,039 & 289,780 & 470,209 & 2 & 2 & 6 & 10\\
+\multirow{-3}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} & \multirow{-3}{*}{\raggedleft\arraybackslash 39,324} & Gramene61-IEA & 37.57 & 56.11 & 60.94 & 74.13 & 20,265 & 47,657 & 58,110 & 126,525 & 1 & 1 & 2 & 3\\
+\cmidrule{1-15}
+\rowcolor{gray!6}  \textit{Zea mays} Mo17 & 38,620 & GOMAP & 87.05 & 90.90 & 100.00 & 100.00 & 87,567 & 79,214 & 277,787 & 444,568 & 2 & 2 & 6 & 10\\
+\cmidrule{1-15}
+\textit{Zea mays} PH207 & 40,557 & GOMAP & 86.72 & 90.64 & 100.00 & 100.00 & 90,617 & 85,500 & 288,677 & 464,794 & 2 & 2 & 6 & 10\\
+\cmidrule{1-15}
+\rowcolor{gray!6}  \textit{Zea mays} W22 & 40,690 & GOMAP & 90.90 & 92.61 & 100.00 & 100.00 & 95,390 & 85,039 & 289,780 & 470,209 & 2 & 2 & 6 & 10\\
 \bottomrule
@@
 \begin{tablenotes}
+\item \href{https://raw.githubusercontent.com/Dill-PICL/GOMAP-Paper-2019.1/master/analyses/quantity/results/quantity_table.csv}{Download this table (CSV)}
 \item[a] How many genes in the genome have at least one GO term from the CC, BF, MP aspect annotated to them?
@@
 A = How many in total?
-Ask your favorite statistician why $\textrm{A} \neq \textrm{CC} + \textrm{BF} +\textrm{MP}$
+Please note that $\textrm{A} \neq \textrm{CC} + \textrm{BF} +\textrm{MP}$
 \end{tablenotes}
@@
 
-\hypertarget{quality-evaluation}{%
-\subsection{Quality Evaluation}\label{quality-evaluation}}
+\hypertarget{quality-evaluation-1}{%
+\subsection{Quality Evaluation}\label{quality-evaluation-1}}
 
+\href{https://github.com/Dill-PICL/GOMAP-Paper-2019.1/blob/master/analyses/quantity/results/quantity_table.csv}{Open as CSV}
 \texttt{TODO} If it turns out that our predictions are good with hF but bad with more approriate metrics, explanation would be that score thresholds for the prediction tools used in the GOMAP pipeline have been chosen to maximize this hF value.
@@
 Again emphasizes the importance of choosing the right evaluation metric.
+Also shows how comparison between different pipelines/predictions can be difficult if chose different metric or optimized for different metric.
+Also: if an annotation is not present in the gold standard, there is no way of knowing whether that gene truly doesn't have that function or whether it has just never been characterized/examined.
+So we cannot distinguish between a biologically true negative and an actually false negative in the gold standard.
+This poses a problem when annotations are predicted that are not found in the gold standard: Is this truly a wrong prediction or is the gold standard incomplete?
+Especially in our case where the predictions not only contain more annotations than the gold standard, but are also more diverse.
+In effect this means that a quality score as calculated above may not only describe the quality of the prediction, but to some extent also the completeness of the gold standard itself.
+At least we can see here that gold standards with a median of 3 annotations per gene resulted in higher quality scores than gold standards with less annotations per gene, even though predictions were generated the same way in all cases.
+\texttt{TODO\ maybe\ put\ a\ figure\ with\ regression\ quality\ score/median\ annotions\ per\ gene\ or\ something}
+In conclusion this means that truly making a statement about the quality of a prediction set would require the ideal and complete gold standard.
+The scores we can generate so far are by far not as meaningful.
 
@@
 \end{tabular}
+\begin{tablenotes}
+\item \href{https://raw.githubusercontent.com/Dill-PICL/GOMAP-Paper-2019.1/master/analyses/quality/results/quality_table.csv}{Download this table (CSV)}
+\end{tablenotes}
+\end{threeparttable}
 \end{table}

### 2019-10-19 text/02-methods.Rmd
Added some text, genes per genome, and links to download tables

@@
 # Methods
+
+## Generating Predictions
+Used GOMAP on condo lalala. Input files are (usually) published along results.
 
@@
 
-## Choosing the right evaluation metric
-A plethora of different metric to evaluate the quality of functional annotation predictions is available using different approaches and there seems to be no clear standard yet. `TODO: THIS IS WEAK`
-Additionally, each of the metrics has a different focus and lalala so choosing a metric for quality evaluation is not trivial.
+## Quantitative Evaluation
+lalala lololo table xyz
+
+## Quality Evaluation
+Quality evaluation of gene function predictions is not trivial and usually done by comparing the set of predicted functions of a gene against a *gold standard* consisting of annotations that are assumed to be correct.
+We used annotations that were created or in some way curated with human participation for gold standards.
+There are a plethora of different metrics to perform the comparison of predictions against this gold standard.
 When we first published GOMAP [@Wimalanathan2018], we used a modified version of the hierarchical evaluation metrics originally introduced in [@Verspoor2006] because they were simple, clear, and part of an earlier attempt at unifying and standardizing GO annotation comparisons [@Defoin-Platel2011].
@@
 
-We then evaluated our predictions and the other annotation sets using the best performing metrics as well as the one we previously used.
-`TODO`
+We then evaluated our predictions and the other annotation sets using the best performing metrics as well as the one we previously used (Table `TODO`).
+
+## Phylogenetic Tree Construction
+To demonstrate that a more top-level and holistic use of whole-genome functional predictions can still be useful we devised some simple ways of applying phylogenetic methods to our predictions.
+### Distance Based
+### Character Based
+
+## Ensuring Reproducibility
+containerization, github...

### 2019-10-19 text/03-results.Rmd
Added some text, genes per genome, and links to download tables

@@
  kable_styling(latex_options = c("striped")) %>%
- collapse_rows(columns = 1, latex_hline="major")
+ collapse_rows(columns = 1, latex_hline="major") %>%
+ footnote(general=c("\\\\href{https://raw.githubusercontent.com/Dill-PICL/GOMAP-Paper-2019.1/master/analyses/cleanup/results/cleanup_table.csv}{Download this table (CSV)}"), general_title="", threeparttable=T, escape=F)
 ```
@@
 A = How many in total?
-Ask your favorite statistician why $\\\\textrm{A} \\\\neq \\\\textrm{CC} + \\\\textrm{BF} +\\\\textrm{MP}$"
-  ), threeparttable=T, escape=F)
+Please note that $\\\\textrm{A} \\\\neq \\\\textrm{CC} + \\\\textrm{BF} +\\\\textrm{MP}$"),
+   general=c("\\\\href{https://raw.githubusercontent.com/Dill-PICL/GOMAP-Paper-2019.1/master/analyses/quantity/results/quantity_table.csv}{Download this table (CSV)}"), general_title="", threeparttable=T, escape=F)
 ```
@@
 ## Quality Evaluation
-
+ [Open as CSV](https://github.com/Dill-PICL/GOMAP-Paper-2019.1/blob/master/analyses/quantity/results/quantity_table.csv)
 `TODO` If it turns out that our predictions are good with hF but bad with more approriate metrics, explanation would be that score thresholds for the prediction tools used in the GOMAP pipeline have been chosen to maximize this hF value.
@@
 Again emphasizes the importance of choosing the right evaluation metric.
+Also shows how comparison between different pipelines/predictions can be difficult if chose different metric or optimized for different metric.
+Also: if an annotation is not present in the gold standard, there is no way of knowing whether that gene truly doesn't have that function or whether it has just never been characterized/examined.
+So we cannot distinguish between a biologically true negative and an actually false negative in the gold standard.
+This poses a problem when annotations are predicted that are not found in the gold standard: Is this truly a wrong prediction or is the gold standard incomplete?
+Especially in our case where the predictions not only contain more annotations than the gold standard, but are also more diverse.
+In effect this means that a quality score as calculated above may not only describe the quality of the prediction, but to some extent also the completeness of the gold standard itself.
+At least we can see here that gold standards with a median of 3 annotations per gene resulted in higher quality scores than gold standards with less annotations per gene, even though predictions were generated the same way in all cases.
+`TODO maybe put a figure with regression quality score/median annotions per gene or something`
+In conclusion this means that truly making a statement about the quality of a prediction set would require the ideal and complete gold standard.
+The scores we can generate so far are by far not as meaningful.
 
@@
  kable_styling(latex_options = c("striped")) %>%
- collapse_rows(columns = 1, latex_hline="major")
+ collapse_rows(columns = 1, latex_hline="major") %>%
+ footnote(general=c("\\\\href{https://raw.githubusercontent.com/Dill-PICL/GOMAP-Paper-2019.1/master/analyses/quality/results/quality_table.csv}{Download this table (CSV)}"), general_title="", threeparttable=T, escape=F)
 ```

### 2019-10-19 text/03-results.Rmd
Do quality evaluation by aspect

@@
 ## Quality Evaluation
- [Open as CSV](https://github.com/Dill-PICL/GOMAP-Paper-2019.1/blob/master/analyses/quantity/results/quantity_table.csv)
 `TODO` If it turns out that our predictions are good with hF but bad with more approriate metrics, explanation would be that score thresholds for the prediction tools used in the GOMAP pipeline have been chosen to maximize this hF value.
@@
 dt2$genome = format_genome(dt2$genome)
-kable(dt2, booktabs=TRUE, escape=F, caption = "Quality evaluation of the used GO annotation sets.", col.names=c("Genome", "Dataset", "SimGIC2 score", "TC AUCPCR score")) %>%
- kable_styling(latex_options = c("striped")) %>%
+headers_above = c(a = 2, b = 3, c = 3)
+names(headers_above) <- c(" ", "SimGIC2", "TC-AUCPCR")
+kable(dt2, booktabs=TRUE, escape=F, caption = "Quality evaluation of the used GO annotation sets.", col.names=c("Genome", "Dataset", "CC", "MF", "BP", "CC", "MF", "BP")) %>%
+ kable_styling(latex_options = c("striped", "scale_down")) %>%
+ add_header_above(headers_above, escape=F)%>%
+ column_spec(c(5), border_right = T) %>%
  collapse_rows(columns = 1, latex_hline="major") %>%

### 2019-10-19 Rakefile.rb

@@ -80,10 +80,13 @@ quality_targets = []
 FileList.new("analyses/cleanup/results/*/GoldStandard.gaf.gz").to_a.each do |f|
   genome = File.basename(File.dirname(f))
   # Reformat the Gold Standard GAF to the format ADS requires
-  file "analyses/quality/results/#{genome}/GoldStandard.tsv" => f do
+  file "analyses/quality/results/#{genome}/GoldStandard.C.tsv" => f do # the C aspect will be used representatively for all aspects
     sh "mkdir -p analyses/quality/results/#{genome}"
     sh "gunzip -k analyses/cleanup/results/#{genome}/GoldStandard.gaf.gz"
-    sh "tail -n+3 analyses/cleanup/results/#{genome}/GoldStandard.gaf | cut -f2,5 > analyses/quality/results/#{genome}/GoldStandard.tsv"
+    # All aspects of the GO are going to be evaluated individually
+    ["C","F","P"].each do |aspect|
+      sh "awk -F '\\t' 'BEGIN {OFS = FS}($9 == \"#{aspect}\")' analyses/cleanup/results/#{genome}/GoldStandard.gaf | cut -f 2,5 > analyses/quality/results/#{genome}/GoldStandard.#{aspect}.tsv"
+    end
     rm "analyses/cleanup/results/#{genome}/GoldStandard.gaf"
   end
 
@@ -91,19 +94,25 @@ FileList.new("analyses/cleanup/results/*/GoldStandard.gaf.gz").to_a.each do |f|
   FileList.new("analyses/cleanup/results/#{genome}/*.gaf.gz").to_a.each do |ds|
     dataset = File.basename(ds).split(".").first
     next if dataset == "GoldStandard" # We don't need to evaluate the GoldStandard against itself.
-    target = "analyses/quality/results/#{genome}/#{dataset}.SimGIC2"
-    file target => [ds, "analyses/quality/results/ads_files/ic.tab", "analyses/quality/results/#{genome}/GoldStandard.tsv"] do
+    # Datasets
+    target = "analyses/quality/results/#{genome}/#{dataset}.C.SimGIC2"
+    file target => [ds, "analyses/quality/results/ads_files/ic.tab", "analyses/quality/results/#{genome}/GoldStandard.C.tsv"] do
       # Reformat GAF to required format
       sh "gunzip -k analyses/cleanup/results/#{genome}/#{dataset}.gaf.gz"
[…]

### 2019-10-20 Paper.tex
Do quality evaluation by aspect
Remove annotations with modifiers during cleanup

@@
 Therefore, all GO accessions were changed to their respecitve `main id' and the dataset was again scanned for duplicates.
+\item
+  Any annotations with modifiers (NOT, contributes\_to\ldots) were removed since no tool used in the further analysis can handle them.
 \end{enumerate}
@@
 \centering
+\resizebox{\linewidth}{!}{
 \begin{threeparttable}
-\begin{tabular}{llrr}
+\begin{tabular}{llrrr}
 \toprule
-Genome & Dataset & Obsolete Annotations & Duplicates\\
+Genome & Dataset & Obsolete Annotations & Duplicates & Annotations with Modifiers\\
 \midrule
-\rowcolor{gray!6}  \textit{Brachypodium distachyon} & GOMAP & 696 & 43\\
-\cmidrule{1-4}
-\textit{Gossypium raimondii} & GOMAP & 184 & 0\\
-\cmidrule{1-4}
-\rowcolor{gray!6}  \textit{Hordeum vulgarum} & GoldStandard & 0 & 4\\
-\cmidrule{1-4}
-\textit{Medicago truncatula} A17 & GOMAP & 0 & 0\\
-\cmidrule{1-4}
-\rowcolor{gray!6}  \textit{Medicago truncatula} R108 & GOMAP & 0 & 0\\
-\cmidrule{1-4}
- & GOMAP & 111 & 2\\
+\rowcolor{gray!6}  \textit{Arachis hypogaea} & GOMAP & 0 & 0 & 912\\
+\cmidrule{1-5}
+\textit{Brachypodium distachyon} & GOMAP & 696 & 43 & 789\\
+\cmidrule{1-5}
+\rowcolor{gray!6}  \textit{Glycine max} & GOMAP & 203 & 0 & 930\\
+\cmidrule{1-5}
+\textit{Gossypium raimondii} & GOMAP & 184 & 0 & 822\\
+\cmidrule{1-5}
+\rowcolor{gray!6}   & GOMAP & 101 & 0 & 815\\
 
-\rowcolor{gray!6}   & GoldStandard & 38 & 556\\
+\multirow{-2}{*}{\raggedright\arraybackslash \textit{Hordeum vulgarum}} & GoldStandard & 0 & 4 & 0\\
+\cmidrule{1-5}
+\rowcolor{gray!6}  \textit{Medicago truncatula} A17 & GOMAP & 0 & 0 & 798\\
+\cmidrule{1-5}
+\textit{Medicago truncatula} R108 & GOMAP & 0 & 0 & 803\\
+\cmidrule{1-5}
+\rowcolor{gray!6}   & GOMAP & 111 & 2 & 869\\
 
-\multirow{-3}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & Gramene61-IEA & 10 & 14\\
-\cmidrule{1-4}
-\rowcolor{gray!6}  \textit{Phaseolus vulgaris} & GOMAP & 0 & 0\\
-\cmidrule{1-4}
-\textit{Sorghum bicolor} & GOMAP & 690 & 59\\
-\cmidrule{1-4}
-\rowcolor{gray!6}   & GOMAP & 285 & 0\\
+ & GoldStandard & 38 & 556 & 0\\
 
- & GoldStandard & 0 & 10\\
+\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & Gramene61-IEA & 10 & 14 & 0\\
+\cmidrule{1-5}
+\textit{Phaseolus vulgaris} & GOMAP & 0 & 0 & 783\\
+\cmidrule{1-5}
+\rowcolor{gray!6}  \textit{Sorghum bicolor} & GOMAP & 690 & 59 & 783\\
+\cmidrule{1-5}
+ & GOMAP & 285 & 0 & 1132\\
 
-\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash \textit{Triticum aestivum}} & Gramene61-IEA & 47 & 48\\
-\cmidrule{1-4}
-\textit{Vigna unguiculata} & GOMAP & 0 & 0\\
-\cmidrule{1-4}
-\rowcolor{gray!6}   & GOMAP & 1107 & 70\\
+\rowcolor{gray!6}   & GoldStandard & 0 & 10 & 0\\
 
- & GoldStandard & 1 & 0\\
+\multirow{-3}{*}{\raggedright\arraybackslash \textit{Triticum aestivum}} & Gramene61-IEA & 47 & 48 & 0\\
+\cmidrule{1-5}
+\rowcolor{gray!6}  \textit{Vigna unguiculata} & GOMAP & 0 & 0 & 811\\
+\cmidrule{1-5}
+ & GOMAP & 1106 & 70 & 709\\
 
-\rowcolor{gray!6}   & Gramene49 & 94 & 2\\
+\rowcolor{gray!6}   & GoldStandard-OFF & 1 & 0 & 0\\
 
-\multirow{-4}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} & Phytozome & 54 & 0\\
-\cmidrule{1-4}
-\rowcolor{gray!6}   & GOMAP & 752 & 83\\
+ & Gramene49 & 94 & 2 & 0\\
 
- & GoldStandard & 55 & 174\\
+\rowcolor{gray!6}  \multirow{-4}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} & Phytozome & 54 & 0 & 0\\
+\cmidrule{1-5}
+ & GOMAP & 752 & 83 & 848\\
 
-\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} & Gramene61-IEA & 99 & 157\\
-\cmidrule{1-4}
-\textit{Zea mays} Mo17 & GOMAP & 726 & 77\\
-\cmidrule{1-4}
-\rowcolor{gray!6}  \textit{Zea mays} PH207 & GOMAP & 798 & 76\\
-\cmidrule{1-4}
-\textit{Zea mays} W22 & GOMAP & 754 & 82\\
+\rowcolor{gray!6}   & GoldStandard & 55 & 174 & 0\\
+
+\multirow{-3}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} & Gramene61-IEA & 99 & 157 & 0\\
+\cmidrule{1-5}
+\rowcolor{gray!6}  \textit{Zea mays} Mo17 & GOMAP & 726 & 77 & 823\\
+\cmidrule{1-5}
+\textit{Zea mays} PH207 & GOMAP & 798 & 76 & 830\\
+\cmidrule{1-5}
+\rowcolor{gray!6}  \textit{Zea mays} W22 & GOMAP & 754 & 82 & 840\\
 \bottomrule
@@
 \end{tablenotes}
-\end{threeparttable}
+\end{threeparttable}}
 \end{table}
@@
 \midrule
-\rowcolor{gray!6}  \textit{Arachis hypogaea} & 67,124 & GOMAP & 85.91 & 84.70 & 100.00 & 100.00 & 153,433 & 132,944 & 493,799 & 780,176 & 2 & 2 & 6 & 10\\
+\rowcolor{gray!6}  \textit{Arachis hypogaea} & 67,124 & GOMAP & 85.90 & 84.69 & 100.00 & 100.00 & 153,052 & 132,624 & 493,588 & 779,264 & 2 & 2 & 6 & 10\\
 \cmidrule{1-15}
-\textit{Brachypodium distachyon} & 34,310 & GOMAP & 81.38 & 85.37 & 100.00 & 100.00 & 75,877 & 69,709 & 255,807 & 401,393 & 2 & 2 & 6 & 10\\
+\textit{Brachypodium distachyon} & 34,310 & GOMAP & 81.37 & 85.36 & 100.00 & 100.00 & 75,536 & 69,452 & 255,616 & 400,604 & 2 & 2 & 6 & 10\\
 \cmidrule{1-15}
-\rowcolor{gray!6}  \textit{Glycine max} & 52,872 & GOMAP & 87.04 & 88.96 & 100.00 & 100.00 & 129,215 & 113,827 & 417,555 & 660,597 & 2 & 2 & 6 & 11\\
+\rowcolor{gray!6}  \textit{Glycine max} & 52,872 & GOMAP & 87.02 & 88.93 & 100.00 & 100.00 & 128,836 & 113,491 & 417,340 & 659,667 & 2 & 2 & 6 & 11\\
 \cmidrule{1-15}
-\textit{Gossypium raimondii} & 37,505 & GOMAP & 93.08 & 92.39 & 100.00 & 100.00 & 96,793 & 85,511 & 307,921 & 490,225 & 2 & 2 & 6 & 11\\
+\textit{Gossypium raimondii} & 37,505 & GOMAP & 93.06 & 92.37 & 100.00 & 100.00 & 96,442 & 85,234 & 307,727 & 489,403 & 2 & 2 & 6 & 11\\
 \cmidrule{1-15}
-\rowcolor{gray!6}   &  & GOMAP & 88.68 & 91.79 & 100.00 & 100.00 & 88,130 & 80,282 & 272,823 & 441,235 & 2 & 2 & 5 & 10\\
+\rowcolor{gray!6}   &  & GOMAP & 88.67 & 91.77 & 100.00 & 100.00 & 87,780 & 80,015 & 272,625 & 440,420 & 2 & 2 & 5 & 10\\
 
@@
 \cmidrule{1-15}
-\rowcolor{gray!6}  \textit{Medicago truncatula} A17 & 50,444 & GOMAP & 83.90 & 86.70 & 100.00 & 100.00 & 107,362 & 99,719 & 364,065 & 571,146 & 2 & 2 & 6 & 10\\
+\rowcolor{gray!6}  \textit{Medicago truncatula} A17 & 50,444 & GOMAP & 83.90 & 86.69 & 100.00 & 100.00 & 107,019 & 99,452 & 363,877 & 570,348 & 2 & 2 & 6 & 10\\
 \cmidrule{1-15}
-\textit{Medicago truncatula} R108 & 55,706 & GOMAP & 72.40 & 90.15 & 100.00 & 100.00 & 112,343 & 108,031 & 382,322 & 602,696 & 1 & 2 & 5 & 9\\
+\textit{Medicago truncatula} R108 & 55,706 & GOMAP & 72.39 & 90.14 & 100.00 & 100.00 & 111,991 & 107,769 & 382,133 & 601,893 & 1 & 2 & 5 & 9\\
 \cmidrule{1-15}
-\rowcolor{gray!6}   &  & GOMAP & 79.89 & 83.33 & 100.00 & 100.00 & 72,780 & 64,685 & 248,700 & 386,165 & 2 & 2 & 6 & 9\\
+\rowcolor{gray!6}   &  & GOMAP & 79.87 & 83.31 & 100.00 & 100.00 & 72,415 & 64,386 & 248,495 & 385,296 & 2 & 2 & 6 & 9\\
 
@@
 \cmidrule{1-15}
-\textit{Phaseolus vulgaris} & 27,433 & GOMAP & 94.54 & 93.10 & 100.00 & 100.00 & 72,005 & 64,583 & 229,630 & 366,218 & 2 & 2 & 6 & 11\\
+\textit{Phaseolus vulgaris} & 27,433 & GOMAP & 94.52 & 93.07 & 100.00 & 100.00 & 71,658 & 64,328 & 229,449 & 365,435 & 2 & 2 & 6 & 11\\
 \cmidrule{1-15}
-\rowcolor{gray!6}  \textit{Sorghum bicolor} & 34,129 & GOMAP & 82.49 & 86.01 & 100.00 & 100.00 & 76,689 & 70,190 & 259,413 & 406,292 & 2 & 2 & 6 & 10\\
+\rowcolor{gray!6}  \textit{Sorghum bicolor} & 34,129 & GOMAP & 82.48 & 85.98 & 100.00 & 100.00 & 76,343 & 69,937 & 259,229 & 405,509 & 2 & 2 & 6 & 10\\
 \cmidrule{1-15}
- &  & GOMAP & 88.61 & 91.01 & 100.00 & 100.00 & 267,741 & 218,623 & 785,960 & 1,272,324 & 2 & 2 & 6 & 10\\
+ &  & GOMAP & 88.60 & 90.98 & 100.00 & 100.00 & 267,317 & 218,186 & 785,689 & 1,271,192 & 2 & 2 & 6 & 10\\
 
@@
 \cmidrule{1-15}
-\rowcolor{gray!6}  \textit{Vigna unguiculata} & 29,773 & GOMAP & 91.27 & 91.10 & 100.00 & 100.00 & 75,867 & 68,313 & 243,278 & 387,458 & 2 & 2 & 6 & 11\\
+\rowcolor{gray!6}  \textit{Vigna unguiculata} & 29,773 & GOMAP & 91.26 & 91.08 & 100.00 & 100.00 & 75,513 & 68,040 & 243,094 & 386,647 & 2 & 2 & 6 & 11\\
 \cmidrule{1-15}
- &  & GOMAP & 88.34 & 96.46 & 100.00 & 100.00 & 135,211 & 87,420 & 291,251 & 513,882 & 3 & 2 & 6 & 11\\
+ &  & GOMAP & 88.33 & 96.42 & 99.99 & 100.00 & 134,917 & 87,166 & 291,091 & 513,174 & 3 & 2 & 6 & 11\\
 
-\rowcolor{gray!6}   &  & GoldStandard & 3.92 & 0.15 & 0.38 & 4.14 & 1,565 & 65 & 299 & 1,929 & 1 & 0 & 0 & 1\\
+\rowcolor{gray!6}   &  & GoldStandard-OFF & 3.92 & 0.15 & 0.38 & 4.14 & 1,565 & 65 & 299 & 1,929 & 1 & 0 & 0 & 1\\
 
@@
 \cmidrule{1-15}
- &  & GOMAP & 93.37 & 94.95 & 100.00 & 100.00 & 88,827 & 82,251 & 278,719 & 449,797 & 2 & 2 & 6 & 10\\
+ &  & GOMAP & 93.36 & 94.93 & 100.00 & 100.00 & 88,468 & 81,963 & 278,518 & 448,949 & 2 & 2 & 6 & 10\\
 
@@
 \cmidrule{1-15}
-\rowcolor{gray!6}  \textit{Zea mays} Mo17 & 38,620 & GOMAP & 87.05 & 90.90 & 100.00 & 100.00 & 87,567 & 79,214 & 277,787 & 444,568 & 2 & 2 & 6 & 10\\
+\rowcolor{gray!6}  \textit{Zea mays} Mo17 & 38,620 & GOMAP & 87.04 & 90.88 & 100.00 & 100.00 & 87,221 & 78,938 & 277,586 & 443,745 & 2 & 2 & 6 & 10\\
 \cmidrule{1-15}
-\textit{Zea mays} PH207 & 40,557 & GOMAP & 86.72 & 90.64 & 100.00 & 100.00 & 90,617 & 85,500 & 288,677 & 464,794 & 2 & 2 & 6 & 10\\
+\textit{Zea mays} PH207 & 40,557 & GOMAP & 86.71 & 90.62 & 100.00 & 100.00 & 90,267 & 85,223 & 288,474 & 463,964 & 2 & 2 & 6 & 10\\
 \cmidrule{1-15}
-\rowcolor{gray!6}  \textit{Zea mays} W22 & 40,690 & GOMAP & 90.90 & 92.61 & 100.00 & 100.00 & 95,390 & 85,039 & 289,780 & 470,209 & 2 & 2 & 6 & 10\\
+\rowcolor{gray!6}  \textit{Zea mays} W22 & 40,690 & GOMAP & 90.89 & 92.59 & 100.00 & 100.00 & 95,043 & 84,750 & 289,576 & 469,369 & 2 & 2 & 6 & 10\\
 \bottomrule
@@
 
-\href{https://github.com/Dill-PICL/GOMAP-Paper-2019.1/blob/master/analyses/quantity/results/quantity_table.csv}{Open as CSV}
 \texttt{TODO} If it turns out that our predictions are good with hF but bad with more approriate metrics, explanation would be that score thresholds for the prediction tools used in the GOMAP pipeline have been chosen to maximize this hF value.
@@
 \centering
+\resizebox{\linewidth}{!}{
 \begin{threeparttable}
-\begin{tabular}{llrr}
+\begin{tabular}{llrr>{}r|rrr}
 \toprule
-Genome & Dataset & SimGIC2 score & TC AUCPCR score\\
+\multicolumn{2}{c}{ } & \multicolumn{3}{c}{SimGIC2} & \multicolumn{3}{c}{TC-AUCPCR} \\
+\cmidrule(l{3pt}r{3pt}){3-5} \cmidrule(l{3pt}r{3pt}){6-8}
+Genome & Dataset & CC & BF & MP & CC & BF & MP\\
 \midrule
-\rowcolor{gray!6}  \textit{Hordeum vulgarum} & GOMAP & 0.158996 & 0.000477\\
-\cmidrule{1-4}
- & GOMAP & 0.253680 & 0.204084\\
+\rowcolor{gray!6}  \textit{Hordeum vulgarum} & GOMAP & 0.309334 & 0.424286 & 0.180110 & NaN & 0.000493 & 0.000388\\
+\cmidrule{1-8}
+ & GOMAP & 0.499374 & 0.448762 & 0.213827 & 0.274482 & 0.261767 & 0.142014\\
 
-\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & Gramene61-IEA & 0.330437 & 0.193740\\
-\cmidrule{1-4}
- & GOMAP & 0.218996 & 0.010039\\
+\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & Gramene61-IEA & 0.416283 & 0.415342 & 0.324981 & 0.170662 & 0.257685 & 0.126104\\
+\cmidrule{1-8}
+ & GOMAP & 0.474972 & 0.418110 & 0.202528 & 0.014568 & 0.005485 & 0.009287\\
 
-\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Triticum aestivum}} & Gramene61-IEA & 0.175564 & 0.005397\\
-\cmidrule{1-4}
- & GOMAP & 0.052182 & 0.012709\\
+\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Triticum aestivum}} & Gramene61-IEA & 0.384973 & 0.346840 & 0.191962 & 0.004446 & 0.006115 & 0.004811\\
+\cmidrule{1-8}
+ & GOMAP & 0.498781 & 0.429594 & 0.212130 & 0.276072 & 0.245183 & 0.133683\\
 
-\rowcolor{gray!6}   & Gramene49 & 0.091475 & 0.019127\\
-
-\multirow{-3}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} & Phytozome & 0.028721 & 0.004498\\
-\cmidrule{1-4}
-\rowcolor{gray!6}   & GOMAP & 0.257543 & 0.196845\\
-
-\multirow{-2}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} & Gramene61-IEA & 0.328777 & 0.188584\\
+\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} & Gramene61-IEA & 0.368491 & 0.411399 & 0.323139 & 0.159213 & 0.229186 & 0.130063\\
 \bottomrule

### 2019-10-20 text/03-results.Rmd
Remove annotations with modifiers during cleanup

@@
 dt2$genome = format_genome(dt2$genome)
-kable(dt2, booktabs=TRUE, escape=F, caption = "Number of removed annotations during cleanup.", col.names=c("Genome", "Dataset", "Obsolete Annotations", "Duplicates")) %>%
- kable_styling(latex_options = c("striped")) %>%
+kable(dt2, booktabs=TRUE, escape=F, caption = "Number of removed annotations during cleanup.", col.names=c("Genome", "Dataset", "Obsolete Annotations", "Duplicates", "Annotations with Modifiers")) %>%
+ kable_styling(latex_options = c("striped", "scale_down")) %>%
  collapse_rows(columns = 1, latex_hline="major") %>%
@@
 names(headers_above) <- c(" ", "SimGIC2", "TC-AUCPCR")
-kable(dt2, booktabs=TRUE, escape=F, caption = "Quality evaluation of the used GO annotation sets.", col.names=c("Genome", "Dataset", "CC", "MF", "BP", "CC", "MF", "BP")) %>%
+kable(dt2, booktabs=TRUE, escape=F, caption = "Quality evaluation of the used GO annotation sets.", col.names=c("Genome", "Dataset", "CC", "BF", "MP", "CC", "BF", "MP")) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%

### 2019-11-08 text/02-methods.Rmd
Remove annotations with modifiers during cleanup
Update ADS paper reference

@@
 Therefore, all GO accessions were changed to their respecitve 'main id' and the dataset was again scanned for duplicates.
+3. Any annotations with modifiers (NOT, contributes_to...) were removed since no tool used in the further analysis can handle them.
 
@@
 When we first published GOMAP [@Wimalanathan2018], we used a modified version of the hierarchical evaluation metrics originally introduced in [@Verspoor2006] because they were simple, clear, and part of an earlier attempt at unifying and standardizing GO annotation comparisons [@Defoin-Platel2011].
-In the meantime, @Plyusnin2018 have published an approach for evaluating different metrics showing substantial differences within the robustness of different approaches.
+In the meantime, @Plyusnin2019 have published an approach for evaluating different metrics showing substantial differences within the robustness of different approaches.
 `TODO DESCRIBE THEIR APPROACH`

### 2019-11-20 Paper.tex
Add mapping feature to cleanup

@@
 When we first published GOMAP \citep{Wimalanathan2018}, we used a modified version of the hierarchical evaluation metrics originally introduced in \citep{Verspoor2006} because they were simple, clear, and part of an earlier attempt at unifying and standardizing GO annotation comparisons \citep{Defoin-Platel2011}.
-In the meantime, \citet{Plyusnin2018} have published an approach for evaluating different metrics showing substantial differences within the robustness of different approaches.
+In the meantime, \citet{Plyusnin2019} have published an approach for evaluating different metrics showing substantial differences within the robustness of different approaches.
 \texttt{TODO\ DESCRIBE\ THEIR\ APPROACH}
@@
 
-\rowcolor{gray!6}   & GoldStandard-OFF & 1 & 0 & 0\\
+\rowcolor{gray!6}   & GoldStandard & 1 & 11 & NA\\
 
@@
 
-\rowcolor{gray!6}   &  & GoldStandard-OFF & 3.92 & 0.15 & 0.38 & 4.14 & 1,565 & 65 & 299 & 1,929 & 1 & 0 & 0 & 1\\
+\rowcolor{gray!6}   &  & GoldStandard & 3.89 & 0.15 & 0.38 & 4.10 & 1,554 & 65 & 299 & 1,918 & 1 & 0 & 0 & 1\\
 
@@
 \cmidrule{1-8}
- & GOMAP & 0.498781 & 0.429594 & 0.212130 & 0.276072 & 0.245183 & 0.133683\\
+ & GOMAP & 0.235407 & 0.348389 & 0.096186 & 0.035907 & 0.001639 & 0.001017\\
 
-\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} & Gramene61-IEA & 0.368491 & 0.411399 & 0.323139 & 0.159213 & 0.229186 & 0.130063\\
+\rowcolor{gray!6}   & Gramene49 & 0.299075 & 0.359259 & 0.164630 & 0.055498 & 0.003230 & 0.001965\\
+
+\multirow{-3}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} & Phytozome & 0.186238 & 0.347164 & 0.100965 & 0.014873 & 0.003058 & 0.000540\\
+\cmidrule{1-8}
+\rowcolor{gray!6}   & GOMAP & 0.498781 & 0.429594 & 0.212130 & 0.276072 & 0.245183 & 0.133683\\
+
+\multirow{-2}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} & Gramene61-IEA & 0.368491 & 0.411399 & 0.323139 & 0.159213 & 0.229186 & 0.130063\\
 \bottomrule

### 2021-02-11 data/set_operations/arachis_medi_vs_legumes.rb
add some trees and set operations

@@ -1,0 +1,6 @@
+arachis_medi = GOSet.new("Arachis_hypogaea") & (GOSet.new("Medicago_truncatula.A17") + GOSet.new("Medicago_truncatula.R108"))
+legumes = GOSet.new("Glycine_max") + 
+  GOSet.new("Phaseolus_vulgaris") + 
+  GOSet.new("Vigna_unguiculata")
+
+(arachis_medi - legumes).output

### 2021-02-11 data/set_operations/cannabis_cotton.rb

@@ -1,0 +1,21 @@
+cannabis = GOSet.new("Cannabis_sativa")
+cotton   = GOSet.new("Gossypium_raimondii")
+shared_among_legumes = GOSet.new("Phaseolus_vulgaris") &
+  GOSet.new("Vigna_unguiculata") &
+  GOSet.new("Glycine_max") &
+  GOSet.new("Medicago_truncatula.A17") &
+  GOSet.new("Medicago_truncatula.R108") &
+  GOSet.new("Arachis_hypogaea")
+merged_legumes = GOSet.new("Phaseolus_vulgaris") +
+  GOSet.new("Vigna_unguiculata") +
+  GOSet.new("Glycine_max") +
+  GOSet.new("Medicago_truncatula.A17") +
+  GOSet.new("Medicago_truncatula.R108") +
+  GOSet.new("Arachis_hypogaea")
+
+puts("What do all legumes AND cotton have in common that cannabis doesn't have?")
+((shared_among_legumes & cotton) - cannabis).output
+
+puts("\n"*5)
+puts("What does cannabis have that's not found in any of the legumes?")
+(cannabis - merged_legumes).output

### 2021-02-11 text/03-results.Rmd
add Fmax value and fix aspect names in tables

@@
 kable(dt2, booktabs=T, digits=2, format.args=list(big.mark=","), escape=F, caption = "Quantitative metrics of the cleaned functional annotation sets.
-CC, BF, MP, and A refer to the aspects of the GO: Cellular Component, Biological Function, Molecular Process, and Any/All.", col.names=c("Genome", "Genes", "Dataset", "CC", "BF", "MP", "A","CC", "BF", "MP", "A","CC", "BF", "MP", "A")) %>%
+CC, MF, BP, and A refer to the aspects of the GO: Cellular Component, Molecular Function, Biological Process, and Any/All.", col.names=c("Genome", "Genes", "Dataset", "CC", "MF", "BP", "A","CC", "MF", "BP", "A","CC", "MF", "BP", "A")) %>%
   kable_styling(latex_options = c("striped", "scale_down")) %>%
@@
   footnote(alphabet=c(
-    "How many genes in the genome have at least one GO term from the CC, BF, MP aspect annotated to them?
+    "How many genes in the genome have at least one GO term from the CC, MF, BP aspect annotated to them?
 A = How many at least one from any aspect?
-($\\\\textrm{A} = \\\\textrm{CC} \\\\cup \\\\textrm{BF} \\\\cup \\\\textrm{MP}$)",
-    "How many annotations in the CC, BF, and MP aspect does this dataset contain? A = How many in total? $\\\\textrm{A} = \\\\textrm{CC} + \\\\textrm{BF} + \\\\textrm{MP}$",
+($\\\\textrm{A} = \\\\textrm{CC} \\\\cup \\\\textrm{MF} \\\\cup \\\\textrm{BP}$)",
+    "How many annotations in the CC, MF, and BP aspect does this dataset contain? A = How many in total? $\\\\textrm{A} = \\\\textrm{CC} + \\\\textrm{MF} + \\\\textrm{BP}$",
     "Take a typical gene that is present in the annotation set.
@@
 A = How many in total?
-Please note that $\\\\textrm{A} \\\\neq \\\\textrm{CC} + \\\\textrm{BF} +\\\\textrm{MP}$"),
+Please note that $\\\\textrm{A} \\\\neq \\\\textrm{CC} + \\\\textrm{MF} +\\\\textrm{BP}$"),
    general=c("\\\\href{https://raw.githubusercontent.com/Dill-PICL/GOMAP-Paper-2019.1/master/analyses/quantity/results/quantity_table.csv}{Download this table (CSV)}"), general_title="", threeparttable=T, escape=F)
@@
 dt2$genome = format_genome(dt2$genome)
-headers_above = c(a = 2, b = 3, c = 3)
-names(headers_above) <- c(" ", "SimGIC2", "TC-AUCPCR")
-kable(dt2, booktabs=TRUE, escape=F, caption = "Quality evaluation of the used GO annotation sets.", col.names=c("Genome", "Dataset", "CC", "BF", "MP", "CC", "BF", "MP")) %>%
+headers_above = c(a = 2, b = 3, c = 3, d = 3)
+names(headers_above) <- c(" ", "SimGIC2", "TC-AUCPCR", "Fmax")
+kable(dt2, booktabs=TRUE, escape=F, caption = "Quality evaluation of the used GO annotation sets.", col.names=c("Genome", "Dataset", "CC", "MF", "BP", "CC", "MF", "BP", "CC", "MF", "BP")) %>%
  kable_styling(latex_options = c("striped", "scale_down")) %>%
  add_header_above(headers_above, escape=F)%>%
- column_spec(c(5), border_right = T) %>%
+ column_spec(c(5, 8), border_right = T) %>%
  collapse_rows(columns = 1, latex_hline="major") %>%

### 2021-02-11 Rakefile.rb

@@ -112,6 +112,7 @@ FileList.new("analyses/cleanup/results/*/GoldStandard.gaf.gz").to_a.each do |f|
         ["C","F","P"].each do |aspect|
           sh "bin/goscores -p ../../quality/results/#{genome}/#{dataset}.#{aspect}.tsv -t ../../quality/results/#{genome}/GoldStandard.#{aspect}.tsv -g -b ../../../data/go.obo -i ../../quality/results/ads_files/ic.tab ../../quality/results/ads_files/goparents.tab -m 'SF=SimGIC2' > ../../quality/results/#{genome}/#{dataset}.#{aspect}.SimGIC2"
           sh "bin/goscores -p ../../quality/results/#{genome}/#{dataset}.#{aspect}.tsv -t ../../quality/results/#{genome}/GoldStandard.#{aspect}.tsv -g -b ../../../data/go.obo -m 'LIST=gene,TH=all,SUMF1=mean,SF=AUCPR' > ../../quality/results/#{genome}/#{dataset}.#{aspect}.TC_AUCPCR"
+          sh "bin/goscores -p ../../quality/results/#{genome}/#{dataset}.#{aspect}.tsv -t ../../quality/results/#{genome}/GoldStandard.#{aspect}.tsv -g -b ../../../data/go.obo -m 'LIST=go,SF=Fmax' > ../../quality/results/#{genome}/#{dataset}.#{aspect}.Fmax"
         end
       end
       rm "data/go.obo"
@@ -123,7 +124,7 @@ end
 # Collect all scores in a table
 file 'analyses/quality/results/quality_table.csv' => quality_targets do
   CSV.open("analyses/quality/results/quality_table.csv", "wb+") do |csv|
-    metrics = ["SimGIC2", "TC_AUCPCR"]
+    metrics = ["SimGIC2", "TC_AUCPCR", "Fmax"]
     headers = ["genome", "dataset"]
     metrics.each do |metric|
       ["C", "F", "P"].each do |aspect|

### 2021-02-15 Paper.tex
fix a bug in cleanup
properly add and process Phytozome12 annotations

--- 2019-10-19 Paper.tex
@@
 \centering
+\resizebox{\linewidth}{!}{
 \begin{threeparttable}
-\begin{tabular}{llrr}
+\begin{tabular}{llrrr}
 \toprule
-Genome & Dataset & Obsolete Annotations & Duplicates\\
+Genome & Dataset & Obsolete Annotations & Duplicates & Annotations with Modifiers\\
 \midrule
-\rowcolor{gray!6}  \textit{Brachypodium distachyon} & GOMAP & 696 & 43\\
-\cmidrule{1-4}
-\textit{Gossypium raimondii} & GOMAP & 184 & 0\\
-\cmidrule{1-4}
-\rowcolor{gray!6}  \textit{Hordeum vulgarum} & GoldStandard & 0 & 4\\
-\cmidrule{1-4}
-\textit{Medicago truncatula} A17 & GOMAP & 0 & 0\\
-\cmidrule{1-4}
-\rowcolor{gray!6}  \textit{Medicago truncatula} R108 & GOMAP & 0 & 0\\
-\cmidrule{1-4}
- & GOMAP & 111 & 2\\
+\rowcolor{gray!6}  \textit{Arachis hypogaea} & GOMAP & 3437 & 13 & 912\\
+\cmidrule{1-5}
+ & GOMAP & 2512 & 49 & 789\\
 
-\rowcolor{gray!6}   & GoldStandard & 38 & 556\\
+\rowcolor{gray!6}   & GoldStandard & 21 & 204 & 0\\
 
-\multirow{-3}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & Gramene61-IEA & 10 & 14\\
-\cmidrule{1-4}
-\rowcolor{gray!6}  \textit{Phaseolus vulgaris} & GOMAP & 0 & 0\\
-\cmidrule{1-4}
-\textit{Sorghum bicolor} & GOMAP & 690 & 59\\
-\cmidrule{1-4}
-\rowcolor{gray!6}   & GOMAP & 285 & 0\\
+ & Gramene63-IEA & 166 & 114 & 0\\
 
- & GoldStandard & 0 & 10\\
+\rowcolor{gray!6}  \multirow{-4}{*}{\raggedright\arraybackslash \textit{Brachypodium distachyon}} & Phytozome12 & 99 & 18 & 0\\
+\cmidrule{1-5}
+\textit{Cannabis sativa} & GOMAP & 1714 & 6 & 757\\
+\cmidrule{1-5}
+\rowcolor{gray!6}  \textit{Glycine max} & GOMAP & 3333 & 10 & 930\\
+\cmidrule{1-5}
+\textit{Gossypium raimondii} & GOMAP & 1781 & 7 & 822\\
+\cmidrule{1-5}
+\rowcolor{gray!6}   & GOMAP & 1877 & 8 & 815\\
 
-\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash \textit{Triticum aestivum}} & Gramene61-IEA & 47 & 48\\
-\cmidrule{1-4}
-\textit{Vigna unguiculata} & GOMAP & 0 & 0\\
-\cmidrule{1-4}
-\rowcolor{gray!6}   & GOMAP & 1107 & 70\\
+\multirow{-2}{*}{\raggedright\arraybackslash \textit{Hordeum vulgare}} & GoldStandard & 1 & 9 & 0\\
+\cmidrule{1-5}
+\rowcolor{gray!6}   & GOMAP & 2673 & 10 & 798\\
 
- & GoldStandard & 1 & 0\\
+ & GoldStandard & 2 & 23 & 0\\
 
-\rowcolor{gray!6}   & Gramene49 & 94 & 2\\
+\rowcolor{gray!6}   & Gramene62-IEA & 429 & 251 & 0\\
 
-\multirow{-4}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} & Phytozome & 54 & 0\\
-\cmidrule{1-4}
-\rowcolor{gray!6}   & GOMAP & 752 & 83\\
+ & Gramene63-IEA & 309 & 243 & 0\\
 
- & GoldStandard & 55 & 174\\
+\rowcolor{gray!6}  \multirow{-5}{*}{\raggedright\arraybackslash \textit{Medicago truncatula} A17} & Phytozome12 & 132 & 17 & 0\\
+\cmidrule{1-5}
+\textit{Medicago truncatula} R108 & GOMAP & 4168 & 7 & 803\\
+\cmidrule{1-5}
+\rowcolor{gray!6}   & GOMAP & 1642 & 7 & 869\\
 
-\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} & Gramene61-IEA & 99 & 157\\
-\cmidrule{1-4}
-\textit{Zea mays} Mo17 & GOMAP & 726 & 77\\
-\cmidrule{1-4}
-\rowcolor{gray!6}  \textit{Zea mays} PH207 & GOMAP & 798 & 76\\
-\cmidrule{1-4}
-\textit{Zea mays} W22 & GOMAP & 754 & 82\\
+ & GoldStandard & 37 & 833 & 0\\
+
+\rowcolor{gray!6}   & Gramene61-IEA & 242 & 28 & 0\\
+
+ & Gramene63-IEA & 238 & 64 & 0\\
+
+\rowcolor{gray!6}  \multirow{-5}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & Phytozome12 & 119 & 19 & 0\\
+\cmidrule{1-5}
+\textit{Phaseolus vulgaris} & GOMAP & 1190 & 6 & 783\\
+\cmidrule{1-5}
+\rowcolor{gray!6}  \textit{Pinus lambertiana} & GOMAP & 1839 & 4 & 587\\
+\cmidrule{1-5}
+ & GOMAP & 2384 & 66 & 783\\
+
+\rowcolor{gray!6}   & GoldStandard & 178 & 219 & 0\\
+
+ & Gramene63-IEA & 278 & 198 & 0\\
+
+\rowcolor{gray!6}  \multirow{-4}{*}{\raggedright\arraybackslash \textit{Sorghum bicolor}} & Phytozome12 & 131 & 12 & 0\\
+\cmidrule{1-5}
+ & GOMAP & 9624 & 17 & 1132\\
+
+\rowcolor{gray!6}   & GoldStandard & 1 & 5 & 0\\
+
+ & Gramene61-IEA & 706 & 88 & 0\\
+
+\rowcolor{gray!6}  \multirow{-4}{*}{\raggedright\arraybackslash \textit{Triticum aestivum}} & Gramene63-IEA & 584 & 319 & 0\\
+\cmidrule{1-5}
+ & GOMAP & 1269 & 6 & 811\\
+
+\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Vigna unguiculata}} & Phytozome12 & 122 & 27 & 0\\
+\cmidrule{1-5}
+ & GOMAP & 1805 & 92 & 709\\
+
+\rowcolor{gray!6}   & GoldStandard & 1 & 11 & 0\\
+
+ & Gramene49 & 221 & 6 & 0\\
+
+\rowcolor{gray!6}  \multirow{-4}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} & Phytozome & 132 & 0 & 0\\
+\cmidrule{1-5}
+ & GOMAP & 2077 & 89 & 848\\
+
+\rowcolor{gray!6}   & GoldStandard & 65 & 207 & 0\\
+
+\multirow{-3}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} & Gramene61-IEA & 600 & 178 & 0\\
+\cmidrule{1-5}
+\rowcolor{gray!6}   & GOMAP & 2346 & 83 & 823\\
+
+\multirow{-2}{*}{\raggedright\arraybackslash \textit{Zea mays} Mo17} & GoldStandard & 1 & 60 & 0\\
+\cmidrule{1-5}
+\rowcolor{gray!6}   & GOMAP & 2676 & 82 & 830\\
+
+\multirow{-2}{*}{\raggedright\arraybackslash \textit{Zea mays} PH207} & GoldStandard & 1 & 70 & 0\\
+\cmidrule{1-5}
+\rowcolor{gray!6}   & GOMAP & 2681 & 88 & 840\\
+
+\multirow{-2}{*}{\raggedright\arraybackslash \textit{Zea mays} W22} & GoldStandard & 1 & 52 & 0\\
 \bottomrule
@@
 \caption{\label{tab:annotation-quantities}Quantitative metrics of the cleaned functional annotation sets.
-CC, BF, MP, and A refer to the aspects of the GO: Cellular Component, Biological Function, Molecular Process, and Any/All.}
+CC, MF, BP, and A refer to the aspects of the GO: Cellular Component, Molecular Function, Biological Process, and Any/All.}
 \centering
@@
 \cmidrule(l{3pt}r{3pt}){4-7} \cmidrule(l{3pt}r{3pt}){8-11} \cmidrule(l{3pt}r{3pt}){12-15}
-Genome & Genes & Dataset & CC & BF & MP & A & CC & BF & MP & A & CC & BF & MP & A\\
+Genome & Genes & Dataset & CC & MF & BP & A & CC & MF & BP & A & CC & MF & BP & A\\
 \midrule
-\rowcolor{gray!6}  \textit{Arachis hypogaea} & 67,124 & GOMAP & 85.91 & 84.70 & 100.00 & 100.00 & 153,433 & 132,944 & 493,799 & 780,176 & 2 & 2 & 6 & 10\\
+\rowcolor{gray!6}  \textit{Arachis hypogaea} & 67,124 & GOMAP & 85.85 & 84.68 & 100.00 & 100.00 & 150,525 & 132,144 & 493,145 & 775,814 & 2 & 2 & 6 & 10\\
 \cmidrule{1-15}
-\textit{Brachypodium distachyon} & 34,310 & GOMAP & 81.38 & 85.37 & 100.00 & 100.00 & 75,877 & 69,709 & 255,807 & 401,393 & 2 & 2 & 6 & 10\\
+ &  & GOMAP & 81.33 & 85.35 & 100.00 & 100.00 & 74,172 & 69,213 & 255,397 & 398,782 & 2 & 2 & 6 & 10\\
+
+\rowcolor{gray!6}   &  & GoldStandard & 21.54 & 19.53 & 18.20 & 26.66 & 10,985 & 10,436 & 11,120 & 32,673 & 1 & 1 & 1 & 3\\
+
+ &  & Gramene63-IEA & 33.12 & 49.29 & 38.29 & 63.60 & 21,658 & 36,372 & 23,899 & 82,026 & 1 & 1 & 1 & 3\\
+
+\rowcolor{gray!6}  \multirow{-4}{*}{\raggedright\arraybackslash \textit{Brachypodium distachyon}} & \multirow{-4}{*}{\raggedleft\arraybackslash 34,310} & Phytozome12 & 10.25 & 37.21 & 26.86 & 43.11 & 4,186 & 18,597 & 11,070 & 34,060 & 0 & 1 & 1 & 2\\
 \cmidrule{1-15}
-\rowcolor{gray!6}  \textit{Glycine max} & 52,872 & GOMAP & 87.04 & 88.96 & 100.00 & 100.00 & 129,215 & 113,827 & 417,555 & 660,597 & 2 & 2 & 6 & 11\\
+\textit{Cannabis sativa} & 33,677 & GOMAP & 94.22 & 95.48 & 100.00 & 100.00 & 85,755 & 73,614 & 262,741 & 422,110 & 2 & 2 & 6 & 11\\
 \cmidrule{1-15}
-\textit{Gossypium raimondii} & 37,505 & GOMAP & 93.08 & 92.39 & 100.00 & 100.00 & 96,793 & 85,511 & 307,921 & 490,225 & 2 & 2 & 6 & 11\\
+\rowcolor{gray!6}  \textit{Glycine max} & 52,872 & GOMAP & 86.95 & 88.92 & 100.00 & 100.00 & 126,470 & 113,068 & 416,989 & 656,527 & 2 & 2 & 6 & 11\\
 \cmidrule{1-15}
-\rowcolor{gray!6}   &  & GOMAP & 88.68 & 91.79 & 100.00 & 100.00 & 88,130 & 80,282 & 272,823 & 441,235 & 2 & 2 & 5 & 10\\
+\textit{Gossypium raimondii} & 37,505 & GOMAP & 93.00 & 92.37 & 100.00 & 100.00 & 95,419 & 84,910 & 307,470 & 487,799 & 2 & 2 & 6 & 11\\
+\cmidrule{1-15}
+\rowcolor{gray!6}   &  & GOMAP & 88.57 & 91.76 & 100.00 & 100.00 & 86,489 & 79,727 & 272,420 & 438,636 & 2 & 2 & 5 & 10\\
 
-\multirow{-2}{*}{\raggedright\arraybackslash \textit{Hordeum vulgarum}} & \multirow{-2}{*}{\raggedleft\arraybackslash 39,734} & GoldStandard & 0.02 & 0.05 & 0.05 & 0.07 & 7 & 23 & 45 & 75 & 0 & 1 & 1 & 2\\
+\multirow{-2}{*}{\raggedright\arraybackslash \textit{Hordeum vulgare}} & \multirow{-2}{*}{\raggedleft\arraybackslash 39,734} & GoldStandard & 28.23 & 26.30 & 23.43 & 35.64 & 15,734 & 15,391 & 15,267 & 46,414 & 1 & 1 & 1 & 3\\
 \cmidrule{1-15}
-\rowcolor{gray!6}  \textit{Medicago truncatula} A17 & 50,444 & GOMAP & 83.90 & 86.70 & 100.00 & 100.00 & 107,362 & 99,719 & 364,065 & 571,146 & 2 & 2 & 6 & 10\\
+\rowcolor{gray!6}   &  & GOMAP & 83.79 & 86.69 & 100.00 & 100.00 & 104,902 & 99,155 & 363,608 & 567,665 & 2 & 2 & 6 & 10\\
+
+ &  & GoldStandard & 25.45 & 23.26 & 21.51 & 32.12 & 17,938 & 18,416 & 18,461 & 54,827 & 1 & 1 & 1 & 3\\
+
+\rowcolor{gray!6}   &  & Gramene63-IEA & 34.25 & 50.84 & 40.26 & 66.14 & 32,753 & 63,470 & 40,441 & 137,001 & 1 & 1 & 1 & 3\\
+
+\multirow{-4}{*}{\raggedright\arraybackslash \textit{Medicago truncatula} A17} & \multirow{-4}{*}{\raggedleft\arraybackslash 50,444} & Phytozome12 & 8.87 & 36.05 & 25.83 & 41.07 & 5,315 & 25,950 & 15,576 & 47,098 & 0 & 1 & 1 & 2\\
 \cmidrule{1-15}
-\textit{Medicago truncatula} R108 & 55,706 & GOMAP & 72.40 & 90.15 & 100.00 & 100.00 & 112,343 & 108,031 & 382,322 & 602,696 & 1 & 2 & 5 & 9\\
+\rowcolor{gray!6}  \textit{Medicago truncatula} R108 & 55,706 & GOMAP & 72.10 & 90.14 & 100.00 & 100.00 & 108,388 & 107,499 & 381,831 & 597,718 & 1 & 2 & 5 & 9\\
 \cmidrule{1-15}
-\rowcolor{gray!6}   &  & GOMAP & 79.89 & 83.33 & 100.00 & 100.00 & 72,780 & 64,685 & 248,700 & 386,165 & 2 & 2 & 6 & 9\\
+ &  & GOMAP & 79.78 & 83.31 & 100.00 & 100.00 & 71,306 & 64,150 & 248,304 & 383,760 & 2 & 2 & 6 & 9\\
 
- &  & GoldStandard & 15.98 & 20.61 & 25.21 & 31.79 & 7,730 & 11,060 & 19,378 & 38,176 & 1 & 1 & 1 & 3\\
+\rowcolor{gray!6}   &  & GoldStandard & 29.95 & 27.29 & 25.33 & 37.57 & 15,492 & 15,176 & 16,536 & 47,339 & 1 & 1 & 1 & 3\\
 
-\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & \multirow{-3}{*}{\raggedleft\arraybackslash 35,825} & Gramene61-IEA & 30.07 & 43.37 & 46.63 & 59.86 & 14,633 & 32,787 & 39,105 & 86,529 & 1 & 1 & 1 & 3\\
+ &  & Gramene63-IEA & 32.21 & 45.83 & 36.75 & 60.13 & 21,935 & 37,425 & 24,255 & 83,645 & 1 & 1 & 1 & 3\\
+
+\rowcolor{gray!6}  \multirow{-4}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & \multirow{-4}{*}{\raggedleft\arraybackslash 35,825} & Phytozome12 & 10.31 & 40.10 & 29.18 & 46.09 & 4,361 & 20,842 & 12,451 & 37,884 & 0 & 1 & 1 & 2\\
 \cmidrule{1-15}
-\textit{Phaseolus vulgaris} & 27,433 & GOMAP & 94.54 & 93.10 & 100.00 & 100.00 & 72,005 & 64,583 & 229,630 & 366,218 & 2 & 2 & 6 & 11\\
+\textit{Phaseolus vulgaris} & 27,433 & GOMAP & 94.48 & 93.06 & 100.00 & 100.00 & 70,987 & 64,022 & 229,230 & 364,239 & 2 & 2 & 6 & 11\\
 \cmidrule{1-15}
-\rowcolor{gray!6}  \textit{Sorghum bicolor} & 34,129 & GOMAP & 82.49 & 86.01 & 100.00 & 100.00 & 76,689 & 70,190 & 259,413 & 406,292 & 2 & 2 & 6 & 10\\
+\rowcolor{gray!6}  \textit{Pinus lambertiana} & 31,007 & GOMAP & 92.67 & 95.91 & 100.00 & 100.00 & 71,247 & 68,315 & 212,248 & 351,810 & 2 & 2 & 5 & 10\\
 \cmidrule{1-15}
- &  & GOMAP & 88.61 & 91.01 & 100.00 & 100.00 & 267,741 & 218,623 & 785,960 & 1,272,324 & 2 & 2 & 6 & 10\\
+ &  & GOMAP & 82.44 & 85.98 & 100.00 & 100.00 & 75,145 & 69,659 & 259,004 & 403,808 & 2 & 2 & 6 & 10\\
 
-\rowcolor{gray!6}   &  & GoldStandard & 0.89 & 0.57 & 1.54 & 1.73 & 1,590 & 923 & 4,807 & 7,323 & 1 & 0 & 2 & 3\\
+\rowcolor{gray!6}   &  & GoldStandard & 34.48 & 32.91 & 30.90 & 42.84 & 16,837 & 17,614 & 17,850 & 52,593 & 1 & 1 & 1 & 3\\
 
-\multirow{-3}{*}{\raggedright\arraybackslash \textit{Triticum aestivum}} & \multirow{-3}{*}{\raggedleft\arraybackslash 107,891} & Gramene61-IEA & 26.74 & 55.24 & 48.72 & 70.24 & 38,975 & 109,319 & 109,518 & 257,832 & 0 & 1 & 1 & 2\\
+ &  & Gramene63-IEA & 35.91 & 52.11 & 42.36 & 67.41 & 23,608 & 39,418 & 27,074 & 90,313 & 1 & 1 & 1 & 3\\
+
+\rowcolor{gray!6}  \multirow{-4}{*}{\raggedright\arraybackslash \textit{Sorghum bicolor}} & \multirow{-4}{*}{\raggedleft\arraybackslash 34,129} & Phytozome12 & 10.54 & 39.19 & 27.90 & 45.10 & 4,246 & 19,724 & 11,432 & 35,599 & 0 & 1 & 1 & 2\\
 \cmidrule{1-15}
-\rowcolor{gray!6}  \textit{Vigna unguiculata} & 29,773 & GOMAP & 91.27 & 91.10 & 100.00 & 100.00 & 75,867 & 68,313 & 243,278 & 387,458 & 2 & 2 & 6 & 11\\
+ &  & GOMAP & 88.53 & 90.98 & 100.00 & 100.00 & 259,318 & 217,467 & 785,051 & 1,261,836 & 2 & 2 & 6 & 10\\
+
+\rowcolor{gray!6}   &  & GoldStandard & 2.98 & 2.78 & 2.56 & 3.82 & 4,727 & 4,512 & 4,793 & 14,035 & 1 & 1 & 1 & 3\\
+
+\multirow{-3}{*}{\raggedright\arraybackslash \textit{Triticum aestivum}} & \multirow{-3}{*}{\raggedleft\arraybackslash 107,891} & Gramene63-IEA & 29.12 & 58.62 & 38.72 & 70.41 & 47,595 & 111,889 & 62,977 & 222,721 & 0 & 1 & 1 & 2\\
 \cmidrule{1-15}
- &  & GOMAP & 88.34 & 96.46 & 100.00 & 100.00 & 135,211 & 87,420 & 291,251 & 513,882 & 3 & 2 & 6 & 11\\
+\rowcolor{gray!6}   &  & GOMAP & 91.21 & 91.08 & 100.00 & 100.00 & 74,791 & 67,734 & 242,847 & 385,372 & 2 & 2 & 6 & 11\\
 
-\rowcolor{gray!6}   &  & GoldStandard & 3.92 & 0.15 & 0.38 & 4.14 & 1,565 & 65 & 299 & 1,929 & 1 & 0 & 0 & 1\\
+\multirow{-2}{*}{\raggedright\arraybackslash \textit{Vigna unguiculata}} & \multirow{-2}{*}{\raggedleft\arraybackslash 29,773} & Phytozome12 & 13.91 & 45.68 & 34.14 & 53.06 & 5,107 & 19,962 & 12,209 & 37,534 & 0 & 1 & 1 & 2\\
+\cmidrule{1-15}
+\rowcolor{gray!6}   &  & GOMAP & 88.33 & 96.41 & 99.99 & 100.00 & 134,622 & 87,007 & 290,824 & 512,453 & 3 & 2 & 6 & 11\\
 
- &  & Gramene49 & 29.98 & 45.58 & 40.03 & 55.55 & 20,072 & 31,056 & 30,089 & 81,217 & 1 & 1 & 1 & 3\\
+ &  & GoldStandard & 3.89 & 0.15 & 0.38 & 4.10 & 1,554 & 65 & 299 & 1,918 & 1 & 0 & 0 & 1\\
 
-\rowcolor{gray!6}  \multirow{-4}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} & \multirow{-4}{*}{\raggedleft\arraybackslash 39,469} & Phytozome & 11.46 & 34.78 & 28.79 & 40.87 & 4,787 & 19,044 & 13,100 & 36,931 & 0 & 1 & 1 & 2\\
+\rowcolor{gray!6}   &  & Gramene49 & 29.98 & 45.58 & 40.03 & 55.55 & 20,066 & 30,936 & 30,084 & 81,086 & 1 & 1 & 1 & 3\\
+
+\multirow{-4}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} & \multirow{-4}{*}{\raggedleft\arraybackslash 39,469} & Phytozome & 11.46 & 34.77 & 28.79 & 40.87 & 4,787 & 18,966 & 13,100 & 36,853 & 0 & 1 & 1 & 2\\
 \cmidrule{1-15}
- &  & GOMAP & 93.37 & 94.95 & 100.00 & 100.00 & 88,827 & 82,251 & 278,719 & 449,797 & 2 & 2 & 6 & 10\\
+\rowcolor{gray!6}   &  & GOMAP & 93.16 & 94.92 & 100.00 & 100.00 & 87,648 & 81,665 & 278,305 & 447,618 & 2 & 2 & 6 & 10\\
 
-\rowcolor{gray!6}   &  & GoldStandard & 21.23 & 25.60 & 30.82 & 38.07 & 11,510 & 15,019 & 25,737 & 52,428 & 1 & 1 & 1 & 3\\
+ &  & GoldStandard & 21.23 & 25.60 & 30.82 & 38.07 & 11,505 & 14,986 & 25,732 & 52,385 & 1 & 1 & 1 & 3\\
 
-\multirow{-3}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} & \multirow{-3}{*}{\raggedleft\arraybackslash 39,324} & Gramene61-IEA & 37.57 & 56.11 & 60.94 & 74.13 & 20,265 & 47,657 & 58,110 & 126,525 & 1 & 1 & 2 & 3\\
+\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} & \multirow{-3}{*}{\raggedleft\arraybackslash 39,324} & Gramene61-IEA & 37.12 & 55.97 & 60.94 & 74.11 & 19,870 & 47,547 & 58,093 & 126,003 & 1 & 1 & 2 & 3\\
 \cmidrule{1-15}
-\rowcolor{gray!6}  \textit{Zea mays} Mo17 & 38,620 & GOMAP & 87.05 & 90.90 & 100.00 & 100.00 & 87,567 & 79,214 & 277,787 & 444,568 & 2 & 2 & 6 & 10\\
+ &  & GOMAP & 86.98 & 90.87 & 100.00 & 100.00 & 86,074 & 78,650 & 277,395 & 442,119 & 2 & 2 & 6 & 10\\
+
+\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Zea mays} Mo17} & \multirow{-2}{*}{\raggedleft\arraybackslash 38,620} & GoldStandard & 3.22 & 0.14 & 0.35 & 3.42 & 1,266 & 64 & 277 & 1,607 & 1 & 0 & 0 & 1\\
 \cmidrule{1-15}
-\textit{Zea mays} PH207 & 40,557 & GOMAP & 86.72 & 90.64 & 100.00 & 100.00 & 90,617 & 85,500 & 288,677 & 464,794 & 2 & 2 & 6 & 10\\
+ &  & GOMAP & 86.55 & 90.61 & 100.00 & 100.00 & 88,962 & 84,910 & 288,208 & 462,080 & 2 & 2 & 6 & 10\\
+
+\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Zea mays} PH207} & \multirow{-2}{*}{\raggedleft\arraybackslash 40,557} & GoldStandard & 3.15 & 0.14 & 0.33 & 3.34 & 1,302 & 63 & 266 & 1,631 & 1 & 0 & 0 & 1\\
 \cmidrule{1-15}
-\rowcolor{gray!6}  \textit{Zea mays} W22 & 40,690 & GOMAP & 90.90 & 92.61 & 100.00 & 100.00 & 95,390 & 85,039 & 289,780 & 470,209 & 2 & 2 & 6 & 10\\
+ &  & GOMAP & 90.77 & 92.58 & 100.00 & 100.00 & 93,622 & 84,450 & 289,364 & 467,436 & 2 & 2 & 6 & 10\\
+
+\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Zea mays} W22} & \multirow{-2}{*}{\raggedleft\arraybackslash 40,690} & GoldStandard & 2.92 & 0.13 & 0.29 & 3.08 & 1,205 & 59 & 241 & 1,505 & 1 & 0 & 0 & 1\\
 \bottomrule
@@
 \item \href{https://raw.githubusercontent.com/Dill-PICL/GOMAP-Paper-2019.1/master/analyses/quantity/results/quantity_table.csv}{Download this table (CSV)}
-\item[a] How many genes in the genome have at least one GO term from the CC, BF, MP aspect annotated to them?
+\item[a] How many genes in the genome have at least one GO term from the CC, MF, BP aspect annotated to them?
 A = How many at least one from any aspect?
-($\textrm{A} = \textrm{CC} \cup \textrm{BF} \cup \textrm{MP}$)
-\item[b] How many annotations in the CC, BF, and MP aspect does this dataset contain? A = How many in total? $\textrm{A} = \textrm{CC} + \textrm{BF} + \textrm{MP}$
+($\textrm{A} = \textrm{CC} \cup \textrm{MF} \cup \textrm{BP}$)
+\item[b] How many annotations in the CC, MF, and BP aspect does this dataset contain? A = How many in total? $\textrm{A} = \textrm{CC} + \textrm{MF} + \textrm{BP}$
 \item[c] Take a typical gene that is present in the annotation set.
@@
 A = How many in total?
-Please note that $\textrm{A} \neq \textrm{CC} + \textrm{BF} +\textrm{MP}$
+Please note that $\textrm{A} \neq \textrm{CC} + \textrm{MF} +\textrm{BP}$
 \end{tablenotes}
@@
 \centering
+\resizebox{\linewidth}{!}{
 \begin{threeparttable}
-\begin{tabular}{llrr}
+\begin{tabular}{llrr>{}r|rr>{}r|rrr}
 \toprule
-Genome & Dataset & SimGIC2 score & TC AUCPCR score\\
+\multicolumn{2}{c}{ } & \multicolumn{3}{c}{SimGIC2} & \multicolumn{3}{c}{TC-AUCPCR} & \multicolumn{3}{c}{Fmax} \\
+\cmidrule(l{3pt}r{3pt}){3-5} \cmidrule(l{3pt}r{3pt}){6-8} \cmidrule(l{3pt}r{3pt}){9-11}
+Genome & Dataset & CC & MF & BP & CC & MF & BP & CC & MF & BP\\
 \midrule
-\rowcolor{gray!6}  \textit{Hordeum vulgarum} & GOMAP & 0.158996 & 0.000477\\
-\cmidrule{1-4}
- & GOMAP & 0.253680 & 0.204084\\
+\rowcolor{gray!6}   & GOMAP & 0.406628 & 0.462970 & 0.223544 & 0.233442 & 0.230701 & 0.118526 & 0.741361 & 0.740897 & 0.526881\\
 
-\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & Gramene61-IEA & 0.330437 & 0.193740\\
-\cmidrule{1-4}
- & GOMAP & 0.218996 & 0.010039\\
+ & Gramene63-IEA & 0.319117 & 0.419453 & 0.348390 & 0.129163 & 0.192507 & 0.111361 & 0.691016 & 0.738542 & 0.650325\\
 
-\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Triticum aestivum}} & Gramene61-IEA & 0.175564 & 0.005397\\
-\cmidrule{1-4}
- & GOMAP & 0.052182 & 0.012709\\
+\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash \textit{Brachypodium distachyon}} & Phytozome12 & 0.370139 & 0.369241 & 0.350490 & 0.112582 & 0.136832 & 0.085628 & 0.717759 & 0.697076 & 0.660603\\
+\cmidrule{1-11}
+\textit{Hordeum vulgare} & GOMAP & 0.402560 & 0.468542 & 0.237800 & 0.237231 & 0.261399 & 0.130784 & 0.745272 & 0.750213 & 0.560096\\
+\cmidrule{1-11}
+\rowcolor{gray!6}   & GOMAP & 0.374182 & 0.450364 & 0.213045 & 0.272809 & 0.282650 & 0.139032 & 0.730838 & 0.726991 & 0.531406\\
 
-\rowcolor{gray!6}   & Gramene49 & 0.091475 & 0.019127\\
+ & Gramene63-IEA & 0.332022 & 0.435677 & 0.342645 & 0.176497 & 0.265887 & 0.133503 & 0.701093 & 0.749900 & 0.654297\\
 
-\multirow{-3}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} & Phytozome & 0.028721 & 0.004498\\
-\cmidrule{1-4}
-\rowcolor{gray!6}   & GOMAP & 0.257543 & 0.196845\\
+\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash \textit{Medicago truncatula} A17} & Phytozome12 & 0.360232 & 0.365060 & 0.361115 & 0.144247 & 0.170863 & 0.110386 & 0.717307 & 0.698429 & 0.661233\\
+\cmidrule{1-11}
+ & GOMAP & 0.411480 & 0.481120 & 0.247901 & 0.298502 & 0.303384 & 0.159724 & 0.751121 & 0.757181 & 0.559221\\
 
-\multirow{-2}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} & Gramene61-IEA & 0.328777 & 0.188584\\
+\rowcolor{gray!6}   & Gramene63-IEA & 0.330644 & 0.422021 & 0.340339 & 0.167619 & 0.265410 & 0.135451 & 0.711309 & 0.738732 & 0.643827\\
+
+\multirow{-3}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & Phytozome12 & 0.051658 & 0.042817 & 0.043681 & 0.000003 & 0.000003 & 0.000002 & 0.470134 & 0.266628 & 0.239256\\
+\cmidrule{1-11}
+\rowcolor{gray!6}   & GOMAP & 0.407231 & 0.465732 & 0.223938 & 0.316873 & 0.337380 & 0.169883 & 0.746540 & 0.742001 & 0.534258\\
+
+ & Gramene63-IEA & 0.324897 & 0.398742 & 0.352589 & 0.177038 & 0.260198 & 0.154157 & 0.711107 & 0.712170 & 0.653591\\
+
+\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash \textit{Sorghum bicolor}} & Phytozome12 & 0.357286 & 0.347189 & 0.338641 & 0.151947 & 0.177579 & 0.110483 & 0.715714 & 0.675147 & 0.641535\\
+\cmidrule{1-11}
+ & GOMAP & 0.412782 & 0.488887 & 0.228871 & 0.050762 & 0.030610 & 0.019360 & 0.736476 & 0.762420 & 0.533897\\
+
+\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Triticum aestivum}} & Gramene63-IEA & 0.364607 & 0.475901 & 0.394219 & 0.040992 & 0.043701 & 0.027872 & 0.737769 & 0.762059 & 0.670953\\
+\cmidrule{1-11}
+ & GOMAP & 0.198179 & 0.359422 & 0.094640 & 0.034380 & 0.001644 & 0.001021 & 0.648177 & 0.645357 & 0.323390\\
+
+\rowcolor{gray!6}   & Gramene49 & 0.252350 & 0.365922 & 0.163637 & 0.049989 & 0.003238 & 0.001972 & 0.729851 & 0.708819 & 0.441927\\
+
+\multirow{-3}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} & Phytozome & 0.152410 & 0.355794 & 0.100792 & 0.013784 & 0.003064 & 0.000539 & 0.538830 & 0.674668 & 0.324333\\
+\cmidrule{1-11}
+\rowcolor{gray!6}   & GOMAP & 0.486568 & 0.440989 & 0.213537 & 0.283686 & 0.247096 & 0.135719 & 0.779115 & 0.722084 & 0.467588\\
+
+\multirow{-2}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} & Gramene61-IEA & 0.349744 & 0.416108 & 0.324970 & 0.157917 & 0.230439 & 0.131515 & 0.681992 & 0.723220 & 0.569086\\
+\cmidrule{1-11}
+\rowcolor{gray!6}  \textit{Zea mays} Mo17 & GOMAP & 0.232016 & 0.292290 & 0.104776 & 0.040932 & 0.001932 & 0.000895 & 0.692584 & 0.629293 & 0.317094\\
+\cmidrule{1-11}
+\textit{Zea mays} PH207 & GOMAP & 0.234422 & 0.272876 & 0.096926 & 0.037857 & 0.001743 & 0.000813 & 0.694819 & 0.608583 & 0.307465\\
+\cmidrule{1-11}
+\rowcolor{gray!6}  \textit{Zea mays} W22 & GOMAP & 0.235595 & 0.276437 & 0.103866 & 0.038546 & 0.001730 & 0.000868 & 0.695096 & 0.604579 & 0.306371\\
 \bottomrule

### 2021-02-15 analyses/cleanup/convert_obo.py

@@ -16,6 +16,14 @@
 #   "GO:93743":"Something else",
 #   ...
 # }
+#
+# The GO_aspects.json file looks like this:
+# {
+#   "GO:43334":"P",
+#   "GO:93743":"F",
+#   ...
+# }
+
 
 import obo_parser
 import json
@@ -25,6 +33,12 @@ parents = {}
 main_id = {}
 obsolete = []
 go_names = {}
+go_aspects = {}
+go_aspect_mapping = {
+    "biological_process": "P",
+    "molecular_function": "F",
+    "cellular_component": "C"
+}
 with gzip.open("data/go.obo.gz") as obofile:
   parser = obo_parser.Parser(obofile)
   for stanza in parser:
@@ -47,8 +61,14 @@ with gzip.open("data/go.obo.gz") as obofile:
     else:
       go_names[go_id] = stanza.tags['name'][0]
 
+    # Also save obsolete aspects bc they are used on non-cleaned annotations
+    go_aspects[go_id] = go_aspect_mapping[stanza.tags['namespace'][0]]
+
 with open('analyses/cleanup/results/GO.json', 'w') as f:
   f.write(json.dumps({"parents":parents,"main_id":main_id,"obsolete":obsolete},indent=2))
 
 with open('analyses/cleanup/results/GO_names.json', 'w') as f:
   f.write(json.dumps(go_names,indent=2))
+
+with open('analyses/cleanup/results/GO_aspects.json', 'w') as f:
+  f.write(json.dumps(go_aspects,indent=2))

### 2021-02-15 data/go_annotation_sets/gramene2gaf.sh

@@ -2,9 +2,9 @@
 
 # This file converts the TSV files downloaded from Gramene to the GAF 2 format
 # Usage:
-# biomart2gaf.sh <TSV file> <db column string> <taxon id>
+# gramene2gaf.sh <TSV file> <db column string> <taxon id>
 # Example:
-#  biomart2gaf.sh Oryza_sativa/Gramene61_IEA "Gramene/Plant_Genes_61/IRGSP-1.0" 4530 > Oryza_sativa/Gramene61_IEA.gaf
+#  gramene2gaf.sh Oryza_sativa/Gramene61_IEA "Gramene/Plant_Genes_61/IRGSP-1.0" 4530 > Oryza_sativa/Gramene61_IEA.gaf
 
 # Print GAF headers
 echo "!gaf-version:2.0"

### 2021-02-15 data/go_annotation_sets/phytozome2gaf.rb

@@ -1,0 +1,21 @@
+# This file converts the TSV files downloaded from Gramene to the GAF 2 format
+# Usage:
+#  ruby phytozome2gaf.rb <TSV file> <db column string> <taxon id> <go aspect json>
+# Example:
+#  ruby phytozome2gaf.rb Oryza_sativa/Phytozome12.tsv "Phytozome12/Plant_Genomes/Oryza_sativa" 4530 ../../analyses/cleanup/results/GO_aspects.json > Oryza_sativa/Gramene61_IEA.gaf
+
+require "csv"
+require "json"
+
+# Print GAF headers
+puts "!gaf-version:2.0"
+puts "!db	db_object_id	db_object_symbol	qualifier	term_accession	db_reference	evidence_code	with	aspect	db_object_name	db_object_synonym	db_object_type	taxon	date	assigned_by	annotation_extension	gene_product_form_id"
+
+# Load GO aspects
+go_aspects = JSON.parse(File.read(ARGV[3]))
+
+CSV.open(ARGV[0], col_sep:"\t", headers:true).each do |row|
+  if row[1]
+    puts [ARGV[1], row[0], row[0], "", row[1], "", "IEA", "", go_aspects[row[1]], "", "", "protein", "taxon:#{ARGV[2]}", "", "", "", ""].join("\t")
+  end
+end

### 2021-02-28 data/go_annotation_sets/gramene2gaf.sh
delete old maize gold standards, add Gramene-IEA annotations for maize B73 and Hordeum

@@ -4,7 +4,7 @@
 # Usage:
 # gramene2gaf.sh <TSV file> <db column string> <taxon id>
 # Example:
-#  gramene2gaf.sh Oryza_sativa/Gramene61_IEA "Gramene/Plant_Genes_61/IRGSP-1.0" 4530 > Oryza_sativa/Gramene61_IEA.gaf
+#  gramene2gaf.sh Oryza_sativa/Gramene61_IEA.tsv "Gramene/Plant_Genes_61/IRGSP-1.0" 4530 > Oryza_sativa/Gramene61_IEA.gaf
 
 # Print GAF headers
 echo "!gaf-version:2.0"

### 2021-03-02 Paper.tex
update Arabidopsis GOA and finalize quality and quantity tables

--- 2019-11-20 Paper.tex
@@
 \midrule
-\rowcolor{gray!6}  \textit{Arachis hypogaea} & GOMAP & 0 & 0 & 912\\
+\rowcolor{gray!6}  \textit{Arachis hypogaea} & GOMAP & 3437 & 13 & 912\\
 \cmidrule{1-5}
-\textit{Brachypodium distachyon} & GOMAP & 696 & 43 & 789\\
+ & GOMAP & 2512 & 49 & 789\\
+
+\rowcolor{gray!6}   & GoldStandard & 21 & 204 & 0\\
+
+ & Gramene63-IEA & 166 & 114 & 0\\
+
+\rowcolor{gray!6}  \multirow{-4}{*}{\raggedright\arraybackslash \textit{Brachypodium distachyon}} & Phytozome12 & 99 & 18 & 0\\
 \cmidrule{1-5}
-\rowcolor{gray!6}  \textit{Glycine max} & GOMAP & 203 & 0 & 930\\
+\textit{Cannabis sativa} & GOMAP & 1714 & 6 & 757\\
 \cmidrule{1-5}
-\textit{Gossypium raimondii} & GOMAP & 184 & 0 & 822\\
+\rowcolor{gray!6}  \textit{Glycine max} & GOMAP & 3333 & 10 & 930\\
 \cmidrule{1-5}
-\rowcolor{gray!6}   & GOMAP & 101 & 0 & 815\\
+\textit{Gossypium raimondii} & GOMAP & 1781 & 7 & 822\\
+\cmidrule{1-5}
+\rowcolor{gray!6}   & GOMAP & 1877 & 8 & 815\\
 
-\multirow{-2}{*}{\raggedright\arraybackslash \textit{Hordeum vulgarum}} & GoldStandard & 0 & 4 & 0\\
+ & GoldStandard & 1 & 9 & 0\\
+
+\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash \textit{Hordeum vulgare}} & Gramene63-IEA & 282 & 147 & 0\\
 \cmidrule{1-5}
-\rowcolor{gray!6}  \textit{Medicago truncatula} A17 & GOMAP & 0 & 0 & 798\\
+ & GOMAP & 2673 & 10 & 798\\
+
+\rowcolor{gray!6}   & GoldStandard & 2 & 23 & 0\\
+
+ & Gramene62-IEA & 429 & 251 & 0\\
+
+\rowcolor{gray!6}   & Gramene63-IEA & 309 & 243 & 0\\
+
+\multirow{-5}{*}{\raggedright\arraybackslash \textit{Medicago truncatula} A17} & Phytozome12 & 132 & 17 & 0\\
 \cmidrule{1-5}
-\textit{Medicago truncatula} R108 & GOMAP & 0 & 0 & 803\\
+\rowcolor{gray!6}  \textit{Medicago truncatula} R108 & GOMAP & 4168 & 7 & 803\\
 \cmidrule{1-5}
-\rowcolor{gray!6}   & GOMAP & 111 & 2 & 869\\
+ & GOMAP & 1642 & 7 & 869\\
 
- & GoldStandard & 38 & 556 & 0\\
+\rowcolor{gray!6}   & GoldStandard & 37 & 833 & 0\\
 
-\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & Gramene61-IEA & 10 & 14 & 0\\
+ & Gramene61-IEA & 242 & 28 & 0\\
+
+\rowcolor{gray!6}   & Gramene63-IEA & 238 & 64 & 0\\
+
+\multirow{-5}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & Phytozome12 & 119 & 19 & 0\\
 \cmidrule{1-5}
-\textit{Phaseolus vulgaris} & GOMAP & 0 & 0 & 783\\
+\rowcolor{gray!6}  \textit{Phaseolus vulgaris} & GOMAP & 1190 & 6 & 783\\
 \cmidrule{1-5}
-\rowcolor{gray!6}  \textit{Sorghum bicolor} & GOMAP & 690 & 59 & 783\\
+\textit{Pinus lambertiana} & GOMAP & 1839 & 4 & 587\\
 \cmidrule{1-5}
- & GOMAP & 285 & 0 & 1132\\
+\rowcolor{gray!6}   & GOMAP & 2384 & 66 & 783\\
 
-\rowcolor{gray!6}   & GoldStandard & 0 & 10 & 0\\
+ & GoldStandard & 178 & 219 & 0\\
 
-\multirow{-3}{*}{\raggedright\arraybackslash \textit{Triticum aestivum}} & Gramene61-IEA & 47 & 48 & 0\\
+\rowcolor{gray!6}   & Gramene63-IEA & 278 & 198 & 0\\
+
+\multirow{-4}{*}{\raggedright\arraybackslash \textit{Sorghum bicolor}} & Phytozome12 & 131 & 12 & 0\\
 \cmidrule{1-5}
-\rowcolor{gray!6}  \textit{Vigna unguiculata} & GOMAP & 0 & 0 & 811\\
+\rowcolor{gray!6}   & GOMAP & 9624 & 17 & 1132\\
+
+ & GoldStandard & 1 & 5 & 0\\
+
+\rowcolor{gray!6}   & Gramene61-IEA & 706 & 88 & 0\\
+
+\multirow{-4}{*}{\raggedright\arraybackslash \textit{Triticum aestivum}} & Gramene63-IEA & 584 & 319 & 0\\
 \cmidrule{1-5}
- & GOMAP & 1106 & 70 & 709\\
+\rowcolor{gray!6}   & GOMAP & 1269 & 6 & 811\\
 
-\rowcolor{gray!6}   & GoldStandard & 1 & 11 & NA\\
+\multirow{-2}{*}{\raggedright\arraybackslash \textit{Vigna unguiculata}} & Phytozome12 & 122 & 27 & 0\\
+\cmidrule{1-5}
+\rowcolor{gray!6}   & GOMAP & 2077 & 89 & 848\\
 
- & Gramene49 & 94 & 2 & 0\\
+ & GoldStandard & 50 & 633 & 0\\
 
-\rowcolor{gray!6}  \multirow{-4}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} & Phytozome & 54 & 0 & 0\\
+\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} & Gramene63-IEA & 306 & 140 & 0\\
 \cmidrule{1-5}
- & GOMAP & 752 & 83 & 848\\
+ & GOMAP & 2346 & 83 & 823\\
 
-\rowcolor{gray!6}   & GoldStandard & 55 & 174 & 0\\
+\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Zea mays} Mo17} & GoldStandard & 36 & 1489 & 0\\
+\cmidrule{1-5}
+ & GOMAP & 2676 & 82 & 830\\
 
-\multirow{-3}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} & Gramene61-IEA & 99 & 157 & 0\\
+\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Zea mays} PH207} & GoldStandard & 37 & 2702 & 0\\
 \cmidrule{1-5}
-\rowcolor{gray!6}  \textit{Zea mays} Mo17 & GOMAP & 726 & 77 & 823\\
-\cmidrule{1-5}
-\textit{Zea mays} PH207 & GOMAP & 798 & 76 & 830\\
-\cmidrule{1-5}
-\rowcolor{gray!6}  \textit{Zea mays} W22 & GOMAP & 754 & 82 & 840\\
+ & GOMAP & 2681 & 88 & 840\\
+
+\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Zea mays} W22} & GoldStandard & 30 & 499 & 0\\
 \bottomrule
@@
 \cmidrule(l{3pt}r{3pt}){4-7} \cmidrule(l{3pt}r{3pt}){8-11} \cmidrule(l{3pt}r{3pt}){12-15}
-Genome & Genes & Dataset & CC & BF & MP & A & CC & BF & MP & A & CC & BF & MP & A\\
+Genome & Genes & Dataset & CC & MF & BP & A & CC & MF & BP & A & CC & MF & BP & A\\
 \midrule
-\rowcolor{gray!6}  \textit{Arachis hypogaea} & 67,124 & GOMAP & 85.90 & 84.69 & 100.00 & 100.00 & 153,052 & 132,624 & 493,588 & 779,264 & 2 & 2 & 6 & 10\\
+\rowcolor{gray!6}  \textit{Arachis hypogaea} & 67,124 & GOMAP & 85.85 & 84.68 & 100.00 & 100.00 & 150,525 & 132,144 & 493,145 & 775,814 & 2 & 2 & 6 & 10\\
 \cmidrule{1-15}
-\textit{Brachypodium distachyon} & 34,310 & GOMAP & 81.37 & 85.36 & 100.00 & 100.00 & 75,536 & 69,452 & 255,616 & 400,604 & 2 & 2 & 6 & 10\\
+ &  & GOMAP & 81.33 & 85.35 & 100.00 & 100.00 & 74,172 & 69,213 & 255,397 & 398,782 & 2 & 2 & 6 & 10\\
+
+\rowcolor{gray!6}   &  & GoldStandard & 21.54 & 19.53 & 18.20 & 26.66 & 10,985 & 10,436 & 11,120 & 32,673 & 1 & 1 & 1 & 3\\
+
+ &  & Gramene63-IEA & 33.12 & 49.29 & 38.29 & 63.60 & 21,658 & 36,372 & 23,899 & 82,026 & 1 & 1 & 1 & 3\\
+
+\rowcolor{gray!6}  \multirow{-4}{*}{\raggedright\arraybackslash \textit{Brachypodium distachyon}} & \multirow{-4}{*}{\raggedleft\arraybackslash 34,310} & Phytozome12 & 10.25 & 37.21 & 26.86 & 43.11 & 4,186 & 18,597 & 11,070 & 34,060 & 0 & 1 & 1 & 2\\
 \cmidrule{1-15}
-\rowcolor{gray!6}  \textit{Glycine max} & 52,872 & GOMAP & 87.02 & 88.93 & 100.00 & 100.00 & 128,836 & 113,491 & 417,340 & 659,667 & 2 & 2 & 6 & 11\\
+\textit{Cannabis sativa} & 33,677 & GOMAP & 94.22 & 95.48 & 100.00 & 100.00 & 85,755 & 73,614 & 262,741 & 422,110 & 2 & 2 & 6 & 11\\
 \cmidrule{1-15}
-\textit{Gossypium raimondii} & 37,505 & GOMAP & 93.06 & 92.37 & 100.00 & 100.00 & 96,442 & 85,234 & 307,727 & 489,403 & 2 & 2 & 6 & 11\\
+\rowcolor{gray!6}  \textit{Glycine max} & 52,872 & GOMAP & 86.95 & 88.92 & 100.00 & 100.00 & 126,470 & 113,068 & 416,989 & 656,527 & 2 & 2 & 6 & 11\\
 \cmidrule{1-15}
-\rowcolor{gray!6}   &  & GOMAP & 88.67 & 91.77 & 100.00 & 100.00 & 87,780 & 80,015 & 272,625 & 440,420 & 2 & 2 & 5 & 10\\
+\textit{Gossypium raimondii} & 37,505 & GOMAP & 93.00 & 92.37 & 100.00 & 100.00 & 95,419 & 84,910 & 307,470 & 487,799 & 2 & 2 & 6 & 11\\
+\cmidrule{1-15}
+\rowcolor{gray!6}   &  & GOMAP & 88.57 & 91.76 & 100.00 & 100.00 & 86,489 & 79,727 & 272,420 & 438,636 & 2 & 2 & 5 & 10\\
 
-\multirow{-2}{*}{\raggedright\arraybackslash \textit{Hordeum vulgarum}} & \multirow{-2}{*}{\raggedleft\arraybackslash 39,734} & GoldStandard & 0.02 & 0.05 & 0.05 & 0.07 & 7 & 23 & 45 & 75 & 0 & 1 & 1 & 2\\
+ &  & GoldStandard & 28.23 & 26.30 & 23.43 & 35.64 & 15,734 & 15,391 & 15,267 & 46,414 & 1 & 1 & 1 & 3\\
+
+\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash \textit{Hordeum vulgare}} & \multirow{-3}{*}{\raggedleft\arraybackslash 39,734} & Gramene63-IEA & 36.19 & 50.90 & 41.71 & 65.03 & 29,826 & 44,789 & 29,425 & 104,178 & 1 & 1 & 1 & 3\\
 \cmidrule{1-15}
-\rowcolor{gray!6}  \textit{Medicago truncatula} A17 & 50,444 & GOMAP & 83.90 & 86.69 & 100.00 & 100.00 & 107,019 & 99,452 & 363,877 & 570,348 & 2 & 2 & 6 & 10\\
+ &  & GOMAP & 83.79 & 86.69 & 100.00 & 100.00 & 104,902 & 99,155 & 363,608 & 567,665 & 2 & 2 & 6 & 10\\
+
+\rowcolor{gray!6}   &  & GoldStandard & 25.45 & 23.26 & 21.51 & 32.12 & 17,938 & 18,416 & 18,461 & 54,827 & 1 & 1 & 1 & 3\\
+
+ &  & Gramene63-IEA & 34.25 & 50.84 & 40.26 & 66.14 & 32,753 & 63,470 & 40,441 & 137,001 & 1 & 1 & 1 & 3\\
+
+\rowcolor{gray!6}  \multirow{-4}{*}{\raggedright\arraybackslash \textit{Medicago truncatula} A17} & \multirow{-4}{*}{\raggedleft\arraybackslash 50,444} & Phytozome12 & 8.87 & 36.05 & 25.83 & 41.07 & 5,315 & 25,950 & 15,576 & 47,098 & 0 & 1 & 1 & 2\\
 \cmidrule{1-15}
-\textit{Medicago truncatula} R108 & 55,706 & GOMAP & 72.39 & 90.14 & 100.00 & 100.00 & 111,991 & 107,769 & 382,133 & 601,893 & 1 & 2 & 5 & 9\\
+\textit{Medicago truncatula} R108 & 55,706 & GOMAP & 72.10 & 90.14 & 100.00 & 100.00 & 108,388 & 107,499 & 381,831 & 597,718 & 1 & 2 & 5 & 9\\
 \cmidrule{1-15}
-\rowcolor{gray!6}   &  & GOMAP & 79.87 & 83.31 & 100.00 & 100.00 & 72,415 & 64,386 & 248,495 & 385,296 & 2 & 2 & 6 & 9\\
+\rowcolor{gray!6}   &  & GOMAP & 79.78 & 83.31 & 100.00 & 100.00 & 71,306 & 64,150 & 248,304 & 383,760 & 2 & 2 & 6 & 9\\
 
- &  & GoldStandard & 15.98 & 20.61 & 25.21 & 31.79 & 7,730 & 11,060 & 19,378 & 38,176 & 1 & 1 & 1 & 3\\
+ &  & GoldStandard & 29.95 & 27.29 & 25.33 & 37.57 & 15,492 & 15,176 & 16,536 & 47,339 & 1 & 1 & 1 & 3\\
 
-\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & \multirow{-3}{*}{\raggedleft\arraybackslash 35,825} & Gramene61-IEA & 30.07 & 43.37 & 46.63 & 59.86 & 14,633 & 32,787 & 39,105 & 86,529 & 1 & 1 & 1 & 3\\
+\rowcolor{gray!6}   &  & Gramene63-IEA & 32.21 & 45.83 & 36.75 & 60.13 & 21,935 & 37,425 & 24,255 & 83,645 & 1 & 1 & 1 & 3\\
+
+\multirow{-4}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & \multirow{-4}{*}{\raggedleft\arraybackslash 35,825} & Phytozome12 & 10.31 & 40.10 & 29.18 & 46.09 & 4,361 & 20,842 & 12,451 & 37,884 & 0 & 1 & 1 & 2\\
 \cmidrule{1-15}
-\textit{Phaseolus vulgaris} & 27,433 & GOMAP & 94.52 & 93.07 & 100.00 & 100.00 & 71,658 & 64,328 & 229,449 & 365,435 & 2 & 2 & 6 & 11\\
+\rowcolor{gray!6}  \textit{Phaseolus vulgaris} & 27,433 & GOMAP & 94.48 & 93.06 & 100.00 & 100.00 & 70,987 & 64,022 & 229,230 & 364,239 & 2 & 2 & 6 & 11\\
 \cmidrule{1-15}
-\rowcolor{gray!6}  \textit{Sorghum bicolor} & 34,129 & GOMAP & 82.48 & 85.98 & 100.00 & 100.00 & 76,343 & 69,937 & 259,229 & 405,509 & 2 & 2 & 6 & 10\\
+\textit{Pinus lambertiana} & 31,007 & GOMAP & 92.67 & 95.91 & 100.00 & 100.00 & 71,247 & 68,315 & 212,248 & 351,810 & 2 & 2 & 5 & 10\\
 \cmidrule{1-15}
- &  & GOMAP & 88.60 & 90.98 & 100.00 & 100.00 & 267,317 & 218,186 & 785,689 & 1,271,192 & 2 & 2 & 6 & 10\\
+\rowcolor{gray!6}   &  & GOMAP & 82.44 & 85.98 & 100.00 & 100.00 & 75,145 & 69,659 & 259,004 & 403,808 & 2 & 2 & 6 & 10\\
 
-\rowcolor{gray!6}   &  & GoldStandard & 0.89 & 0.57 & 1.54 & 1.73 & 1,590 & 923 & 4,807 & 7,323 & 1 & 0 & 2 & 3\\
+ &  & GoldStandard & 34.48 & 32.91 & 30.90 & 42.84 & 16,837 & 17,614 & 17,850 & 52,593 & 1 & 1 & 1 & 3\\
 
-\multirow{-3}{*}{\raggedright\arraybackslash \textit{Triticum aestivum}} & \multirow{-3}{*}{\raggedleft\arraybackslash 107,891} & Gramene61-IEA & 26.74 & 55.24 & 48.72 & 70.24 & 38,975 & 109,319 & 109,518 & 257,832 & 0 & 1 & 1 & 2\\
+\rowcolor{gray!6}   &  & Gramene63-IEA & 35.91 & 52.11 & 42.36 & 67.41 & 23,608 & 39,418 & 27,074 & 90,313 & 1 & 1 & 1 & 3\\
+
+\multirow{-4}{*}{\raggedright\arraybackslash \textit{Sorghum bicolor}} & \multirow{-4}{*}{\raggedleft\arraybackslash 34,129} & Phytozome12 & 10.54 & 39.19 & 27.90 & 45.10 & 4,246 & 19,724 & 11,432 & 35,599 & 0 & 1 & 1 & 2\\
 \cmidrule{1-15}
-\rowcolor{gray!6}  \textit{Vigna unguiculata} & 29,773 & GOMAP & 91.26 & 91.08 & 100.00 & 100.00 & 75,513 & 68,040 & 243,094 & 386,647 & 2 & 2 & 6 & 11\\
+\rowcolor{gray!6}   &  & GOMAP & 88.53 & 90.98 & 100.00 & 100.00 & 259,318 & 217,467 & 785,051 & 1,261,836 & 2 & 2 & 6 & 10\\
+
+ &  & GoldStandard & 2.98 & 2.78 & 2.56 & 3.82 & 4,727 & 4,512 & 4,793 & 14,035 & 1 & 1 & 1 & 3\\
+
+\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash \textit{Triticum aestivum}} & \multirow{-3}{*}{\raggedleft\arraybackslash 107,891} & Gramene63-IEA & 29.12 & 58.62 & 38.72 & 70.41 & 47,595 & 111,889 & 62,977 & 222,721 & 0 & 1 & 1 & 2\\
 \cmidrule{1-15}
- &  & GOMAP & 88.33 & 96.42 & 99.99 & 100.00 & 134,917 & 87,166 & 291,091 & 513,174 & 3 & 2 & 6 & 11\\
+ &  & GOMAP & 91.21 & 91.08 & 100.00 & 100.00 & 74,791 & 67,734 & 242,847 & 385,372 & 2 & 2 & 6 & 11\\
 
-\rowcolor{gray!6}   &  & GoldStandard & 3.89 & 0.15 & 0.38 & 4.10 & 1,554 & 65 & 299 & 1,918 & 1 & 0 & 0 & 1\\
+\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Vigna unguiculata}} & \multirow{-2}{*}{\raggedleft\arraybackslash 29,773} & Phytozome12 & 13.91 & 45.68 & 34.14 & 53.06 & 5,107 & 19,962 & 12,209 & 37,534 & 0 & 1 & 1 & 2\\
+\cmidrule{1-15}
+ &  & GOMAP & 93.16 & 94.92 & 100.00 & 100.00 & 87,648 & 81,665 & 278,305 & 447,618 & 2 & 2 & 6 & 10\\
 
- &  & Gramene49 & 29.98 & 45.58 & 40.03 & 55.55 & 20,072 & 31,056 & 30,089 & 81,217 & 1 & 1 & 1 & 3\\
+\rowcolor{gray!6}   &  & GoldStandard & 37.92 & 34.78 & 32.67 & 46.85 & 22,531 & 21,292 & 23,153 & 67,285 & 1 & 1 & 1 & 3\\
 
-\rowcolor{gray!6}  \multirow{-4}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} & \multirow{-4}{*}{\raggedleft\arraybackslash 39,469} & Phytozome & 11.46 & 34.78 & 28.79 & 40.87 & 4,787 & 19,044 & 13,100 & 36,931 & 0 & 1 & 1 & 2\\
+\multirow{-3}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} & \multirow{-3}{*}{\raggedleft\arraybackslash 39,324} & Gramene63-IEA & 39.16 & 58.16 & 48.21 & 73.87 & 30,189 & 53,748 & 35,276 & 119,273 & 1 & 1 & 1 & 3\\
 \cmidrule{1-15}
- &  & GOMAP & 93.36 & 94.93 & 100.00 & 100.00 & 88,468 & 81,963 & 278,518 & 448,949 & 2 & 2 & 6 & 10\\
+\rowcolor{gray!6}   &  & GOMAP & 86.98 & 90.87 & 100.00 & 100.00 & 86,074 & 78,650 & 277,395 & 442,119 & 2 & 2 & 6 & 10\\
 
-\rowcolor{gray!6}   &  & GoldStandard & 21.23 & 25.60 & 30.82 & 38.07 & 11,510 & 15,019 & 25,737 & 52,428 & 1 & 1 & 1 & 3\\
+\multirow{-2}{*}{\raggedright\arraybackslash \textit{Zea mays} Mo17} & \multirow{-2}{*}{\raggedleft\arraybackslash 38,620} & GoldStandard & 27.56 & 25.20 & 23.73 & 33.98 & 16,128 & 15,384 & 16,489 & 48,220 & 1 & 1 & 1 & 3\\
+\cmidrule{1-15}
+\rowcolor{gray!6}   &  & GOMAP & 86.55 & 90.61 & 100.00 & 100.00 & 88,962 & 84,910 & 288,208 & 462,080 & 2 & 2 & 6 & 10\\
 
-\multirow{-3}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} & \multirow{-3}{*}{\raggedleft\arraybackslash 39,324} & Gramene61-IEA & 37.57 & 56.11 & 60.94 & 74.13 & 20,265 & 47,657 & 58,110 & 126,525 & 1 & 1 & 2 & 3\\
+\multirow{-2}{*}{\raggedright\arraybackslash \textit{Zea mays} PH207} & \multirow{-2}{*}{\raggedleft\arraybackslash 40,557} & GoldStandard & 28.18 & 25.82 & 24.26 & 34.66 & 17,370 & 16,580 & 17,791 & 51,984 & 1 & 1 & 1 & 3\\
 \cmidrule{1-15}
-\rowcolor{gray!6}  \textit{Zea mays} Mo17 & 38,620 & GOMAP & 87.04 & 90.88 & 100.00 & 100.00 & 87,221 & 78,938 & 277,586 & 443,745 & 2 & 2 & 6 & 10\\
-\cmidrule{1-15}
-\textit{Zea mays} PH207 & 40,557 & GOMAP & 86.71 & 90.62 & 100.00 & 100.00 & 90,267 & 85,223 & 288,474 & 463,964 & 2 & 2 & 6 & 10\\
-\cmidrule{1-15}
-\rowcolor{gray!6}  \textit{Zea mays} W22 & 40,690 & GOMAP & 90.89 & 92.59 & 100.00 & 100.00 & 95,043 & 84,750 & 289,576 & 469,369 & 2 & 2 & 6 & 10\\
+\rowcolor{gray!6}   &  & GOMAP & 90.77 & 92.58 & 100.00 & 100.00 & 93,622 & 84,450 & 289,364 & 467,436 & 2 & 2 & 6 & 10\\
+
+\multirow{-2}{*}{\raggedright\arraybackslash \textit{Zea mays} W22} & \multirow{-2}{*}{\raggedleft\arraybackslash 40,690} & GoldStandard & 25.40 & 23.15 & 21.80 & 31.29 & 15,518 & 14,818 & 15,850 & 46,402 & 1 & 1 & 1 & 3\\
 \bottomrule
@@
 \begin{threeparttable}
-\begin{tabular}{llrr>{}r|rrr}
+\begin{tabular}{llrr>{}r|rr>{}r|rrr}
 \toprule
-\multicolumn{2}{c}{ } & \multicolumn{3}{c}{SimGIC2} & \multicolumn{3}{c}{TC-AUCPCR} \\
-\cmidrule(l{3pt}r{3pt}){3-5} \cmidrule(l{3pt}r{3pt}){6-8}
-Genome & Dataset & CC & BF & MP & CC & BF & MP\\
+\multicolumn{2}{c}{ } & \multicolumn{3}{c}{SimGIC2} & \multicolumn{3}{c}{TC-AUCPCR} & \multicolumn{3}{c}{Fmax} \\
+\cmidrule(l{3pt}r{3pt}){3-5} \cmidrule(l{3pt}r{3pt}){6-8} \cmidrule(l{3pt}r{3pt}){9-11}
+Genome & Dataset & CC & MF & BP & CC & MF & BP & CC & MF & BP\\
 \midrule
-\rowcolor{gray!6}  \textit{Hordeum vulgarum} & GOMAP & 0.309334 & 0.424286 & 0.180110 & NaN & 0.000493 & 0.000388\\
-\cmidrule{1-8}
- & GOMAP & 0.499374 & 0.448762 & 0.213827 & 0.274482 & 0.261767 & 0.142014\\
+\rowcolor{gray!6}   & GOMAP & 0.404149 & 0.464127 & 0.223830 & 0.233442 & 0.230701 & 0.118526 & 0.741361 & 0.740897 & 0.526881\\
 
-\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & Gramene61-IEA & 0.416283 & 0.415342 & 0.324981 & 0.170662 & 0.257685 & 0.126104\\
-\cmidrule{1-8}
- & GOMAP & 0.474972 & 0.418110 & 0.202528 & 0.014568 & 0.005485 & 0.009287\\
+ & Gramene63-IEA & 0.317801 & 0.420859 & 0.349406 & 0.129163 & 0.192507 & 0.111361 & 0.691016 & 0.738542 & 0.650325\\
 
-\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Triticum aestivum}} & Gramene61-IEA & 0.384973 & 0.346840 & 0.191962 & 0.004446 & 0.006115 & 0.004811\\
-\cmidrule{1-8}
- & GOMAP & 0.235407 & 0.348389 & 0.096186 & 0.035907 & 0.001639 & 0.001017\\
+\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash \textit{Brachypodium distachyon}} & Phytozome12 & 0.370264 & 0.370521 & 0.352206 & 0.112582 & 0.136832 & 0.085628 & 0.717759 & 0.697076 & 0.660603\\
+\cmidrule{1-11}
+ & GOMAP & 0.400087 & 0.470012 & 0.238177 & 0.237231 & 0.261399 & 0.130784 & 0.745272 & 0.750213 & 0.560096\\
 
-\rowcolor{gray!6}   & Gramene49 & 0.299075 & 0.359259 & 0.164630 & 0.055498 & 0.003230 & 0.001965\\
+\rowcolor{gray!6}  \multirow{-2}{*}{\raggedright\arraybackslash \textit{Hordeum vulgare}} & Gramene63-IEA & 0.306119 & 0.426601 & 0.381010 & 0.157352 & 0.228797 & 0.136002 & 0.680996 & 0.742638 & 0.665696\\
+\cmidrule{1-11}
+ & GOMAP & 0.371795 & 0.451258 & 0.213407 & 0.272809 & 0.282650 & 0.139032 & 0.730838 & 0.726991 & 0.531406\\
 
-\multirow{-3}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v3} & Phytozome & 0.186238 & 0.347164 & 0.100965 & 0.014873 & 0.003058 & 0.000540\\
-\cmidrule{1-8}
-\rowcolor{gray!6}   & GOMAP & 0.498781 & 0.429594 & 0.212130 & 0.276072 & 0.245183 & 0.133683\\
+\rowcolor{gray!6}   & Gramene63-IEA & 0.329600 & 0.437274 & 0.343561 & 0.176497 & 0.265887 & 0.133503 & 0.701093 & 0.749900 & 0.654297\\
 
-\multirow{-2}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} & Gramene61-IEA & 0.368491 & 0.411399 & 0.323139 & 0.159213 & 0.229186 & 0.130063\\
+\multirow{-3}{*}{\raggedright\arraybackslash \textit{Medicago truncatula} A17} & Phytozome12 & 0.358311 & 0.367257 & 0.363013 & 0.144247 & 0.170863 & 0.110386 & 0.717307 & 0.698429 & 0.661233\\
+\cmidrule{1-11}
+\rowcolor{gray!6}   & GOMAP & 0.408945 & 0.482650 & 0.248207 & 0.298502 & 0.303384 & 0.159724 & 0.751121 & 0.757181 & 0.559221\\
+
+ & Gramene63-IEA & 0.328761 & 0.423191 & 0.341193 & 0.167619 & 0.265410 & 0.135451 & 0.711309 & 0.738732 & 0.643827\\
+
+\rowcolor{gray!6}  \multirow{-3}{*}{\raggedright\arraybackslash \textit{Oryza sativa}} & Phytozome12 & 0.049975 & 0.041007 & 0.044279 & 0.000003 & 0.000003 & 0.000002 & 0.470134 & 0.266628 & 0.239256\\
+\cmidrule{1-11}
+ & GOMAP & 0.404852 & 0.466708 & 0.224011 & 0.316873 & 0.337380 & 0.169883 & 0.746540 & 0.742001 & 0.534258\\
+
+\rowcolor{gray!6}   & Gramene63-IEA & 0.323037 & 0.400241 & 0.353135 & 0.177038 & 0.260198 & 0.154157 & 0.711107 & 0.712170 & 0.653591\\
+
+\multirow{-3}{*}{\raggedright\arraybackslash \textit{Sorghum bicolor}} & Phytozome12 & 0.356091 & 0.348264 & 0.340124 & 0.151947 & 0.177579 & 0.110483 & 0.715714 & 0.675147 & 0.641535\\
+\cmidrule{1-11}
+\rowcolor{gray!6}   & GOMAP & 0.410582 & 0.489881 & 0.229271 & 0.050762 & 0.030610 & 0.019360 & 0.736476 & 0.762420 & 0.533897\\
+
+\multirow{-2}{*}{\raggedright\arraybackslash \textit{Triticum aestivum}} & Gramene63-IEA & 0.362452 & 0.476685 & 0.395112 & 0.040992 & 0.043701 & 0.027872 & 0.737769 & 0.762059 & 0.670953\\
+\cmidrule{1-11}
+\rowcolor{gray!6}   & GOMAP & 0.417455 & 0.467339 & 0.245373 & 0.302761 & 0.290371 & 0.153011 & 0.759504 & 0.746870 & 0.564707\\
+
+\multirow{-2}{*}{\raggedright\arraybackslash \textit{Zea mays} B73.v4} & Gramene63-IEA & 0.303231 & 0.416301 & 0.346308 & 0.175735 & 0.250075 & 0.138275 & 0.662987 & 0.732860 & 0.647725\\
+\cmidrule{1-11}
+\rowcolor{gray!6}  \textit{Zea mays} Mo17 & GOMAP & 0.399521 & 0.464265 & 0.225632 & 0.236209 & 0.239598 & 0.125599 & 0.744360 & 0.743026 & 0.537489\\
+\cmidrule{1-11}
+\textit{Zea mays} PH207 & GOMAP & 0.394481 & 0.436266 & 0.224226 & 0.221709 & 0.221266 & 0.117086 & 0.743111 & 0.718933 & 0.533092\\
+\cmidrule{1-11}
+\rowcolor{gray!6}  \textit{Zea mays} W22 & GOMAP & 0.397602 & 0.463499 & 0.223511 & 0.210198 & 0.217609 & 0.113262 & 0.743783 & 0.742341 & 0.535572\\
 \bottomrule
